### 2021-11-28 rCode/Draft.Rmd
descriptive stats, some fixes

---
title: '\bf Replication Paper'
author: 'Catherine Darin and Zagreb Mukerjee'
date: 'Released: \today'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

## Outline
- Framing story: the trajectory of XYZ county that swung from O to T and suffered big manufacturing layoffs
- Substantive importance: Why did Trump win in 2016? A longstanding debate about relative importance of race and economic factors. Complicated by the interaction of the two. We can tease out 
- Empirical strategy: Differential manuf. exposure across counties allows for identification of the causal effect of deindustrialization on change in Dem vote share. Further differences in racial exposure to mfg layoffs allows for identification of the interaction between race and deindustrialization. 
- Data: census Quarterly Workforce Indicators, which break down employment by industry, race and ethnicity. Compute net change in mfg (long term job loss)

```{r setup, echo=F}
library(tidyverse)
```

## Findings

## Figures
```{r,  echo=F}
regResultList <- readRDS("../regresults.rds")

```

### descriptive statistics

### Example

### Regression summaries

### Counterfactual assessment of election

### example state: Michigan

### 2020

## Future steps

- Disaggregation: Instead of instrumenting by manufacturing share, perhaps we can look at layoffs by industry in each county. While aggregate manufacturing employment may be endogeneous, there's less reason to believe that specific industries would be (cf. Autor, Dorn and Hanson). This may also allow us to get further away from ecological inference problems.
- Trend-cycle estimation: There are techniques from econometrics and other places that could potentially be used to decompose gross layoffs into seasonal and non-seasonal components.

## Appendix

### 2021-11-28 rCode/replicateRegsAndExtend.R

@@ -156,6 +156,41 @@ ourDatasetBase <- censusCountyData %>%
     population = last(population)
   )
 
+
+
+
+datasetClean <- function(electionYear, startYear, aggregateYears){
+  BWDataByCounty %>%  filter(year == 2016) %>%  dplyr::rename(BWLayoffs = mfgLayoffs) %>% 
+    left_join(ourDatasetBase %>% 
+                group_by(wNw, state_fips, county_fips) %>% 
+                filter(year %in% 2012:2015) %>%  
+                arrange(time) %>% 
+                summarize(
+                  layoffCV = sd(mfgEmp, na.rm = T)/mean(mfgEmp, na.rm = T),
+                  totalEmp = mean(totalEmp, na.rm = T), 
+                  mfgEmp = mean(mfgEmp, na.rm = T),
+                  mfgLayoffs = sum(mfgLayoffs, na.rm = T),
+                  mfgLayoffsS = sum(mfgLayoffsS, na.rm = T),
+                  mfgNetChange  = -sum(mfgNetChange, na.rm = T),
+                  population = mean(population, na.rm = T)
+                )) %>%
+    filter(mfgEmp != 0)  %>% 
+    rename(countyPop = population) %>%  filter(is.finite(white_counties_4y), is.finite(msl_service_pc4y))  %>%
+    pivot_wider(names_from = wNw, values_from = c(totalEmp, mfgEmp, mfgLayoffs, mfgLayoffsS, mfgNetChange,layoffCV)) %>% 
+    mutate(mfgLayoffs_total = mfgLayoffs_total/totalEmp_total,
+           mfgNetChange_total = mfgNetChange_total/totalEmp_total,
+           mfgLayoffs_white = mfgLayoffs_white/totalEmp_total,
+           mfgNetChange_white = mfgNetChange_white/totalEmp_total,
+           mfgLayoffs_nonwhite = mfgLayoffs_nonwhite/totalEmp_total,
+           mfgNetChange_nonwhite = mfgNetChange_nonwhite/totalEmp_total)
+  
+  
+}
+
+
+
+
+
 # TODO: take ratios of 2011 employment
 # summarize across years
[…]

### 2021-11-28 rCode/tablesAndFigures.R

@@ -1,0 +1,65 @@
+
+
+
+#########################################
+# Descriptive Statistics
+#########################################
+
+
+censusCountyData  <- readRDS("data/censusDataByCounty.rds")
+
+descDatasetBase <- censusCountyData %>%
+  mutate(year = as.integer(substr(time, 0, 4))) %>% 
+  mutate(wNw = case_when(
+    race == "A0" & ethnicity == "A0" ~ "Total",
+    race == "A1" & ethnicity == "A1" ~ "White",
+    race != "A0" & ethnicity != "A0" ~ "Non-white",
+    TRUE ~ "na"
+  )) %>% 
+  filter(wNw != "na") %>% 
+  group_by(wNw, state_fips, county_fips, year, time) %>% 
+  summarize(
+    totalEmp = sum(totalEmp, na.rm = T),
+    mfgEmp = sum(mfgEmp, na.rm = T), 
+    mfgLayoffs = sum(mfgLayoffs, na.rm = T),
+    mfgLayoffsS = sum(mfgLayoffsS, na.rm = T),
+    mfgNetChange  = sum(mfgNetChange, na.rm = T),
+    population = last(population)
+  )
+
+descDatasetRaw <- descDatasetBase %>% 
+              group_by(wNw, state_fips, county_fips) %>% 
+              filter(year %in% 2012:2015) %>%  
+              arrange(time) %>% 
+              summarize(
+                layoffCV = sd(mfgEmp, na.rm = T)/mean(mfgEmp, na.rm = T),
+                totalEmp = mean(totalEmp, na.rm = T), 
+                mfgEmp = mean(mfgEmp, na.rm = T),
+                mfgLayoffs = sum(mfgLayoffs, na.rm = T),
+                mfgLayoffsS = sum(mfgLayoffsS, na.rm = T),
+                mfgNetChange  = -sum(mfgNetChange, na.rm = T),
+                population = mean(population, na.rm = T)
+              ) %>%
+  filter(mfgEmp != 0)  %>% 
+  rename(countyPop = population)
+
+
+descDatasetRaw %>% 
+  dplyr::select(wNw, state_fips, county_fips, totalEmp, mfgEmp, mfgNetChange) %>% 
+  mutate(wNw = factor(x = wNw, levels = c("Total", "White", "Non-white"))) %>% 
+  rename(
+    `Total Employment` = totalEmp,
+    `Manufacturing Employment` = mfgEmp,
[…]

### 2021-11-28 rCode/replicateRegsAndExtend.R
tweak

@@ -160,8 +160,11 @@ ourDatasetBase <- censusCountyData %>%
 
 
 datasetClean <- function(electionYear, startYear, aggregateYears){
-  BWDataByCounty %>%  filter(year == 2016) %>%  dplyr::rename(BWLayoffs = mfgLayoffs) %>% 
+  BWDataByCounty %>%  filter(year == electionYear) %>%  dplyr::rename(BWLayoffs = mfgLayoffs) %>% 
     left_join(ourDatasetBase %>% 
+                group_by(state_fips, county_fips) %>% 
+                mutate(emp2011_total = mean(totalEmp[year == 2011]),
+                       emp2011_mfg = mean(mfgEmp[year == 2011])) %>% 
                 group_by(wNw, state_fips, county_fips) %>% 
                 filter(year %in% 2012:2015) %>%  
                 arrange(time) %>% 
@@ -183,7 +186,6 @@ datasetClean <- function(electionYear, startYear, aggregateYears){
            mfgNetChange_white = mfgNetChange_white/totalEmp_total,
            mfgLayoffs_nonwhite = mfgLayoffs_nonwhite/totalEmp_total,
            mfgNetChange_nonwhite = mfgNetChange_nonwhite/totalEmp_total)
-  
   
 }
 

### 2021-11-29 rCode/Draft.Rmd
tweak
tables and stats

@@
 author: 'Catherine Darin and Zagreb Mukerjee'
-date: 'Released: \today'
+date: '\today'
 fontsize: 12pt
@@
 ---
+
+\renewcommand{\arraystretch}{1.1}
+\renewcommand{\topfraction}{.85}
+\renewcommand{\bottomfraction}{.7}
+\renewcommand{\textfraction}{.15}
+\renewcommand{\floatpagefraction}{.66}
+\setcounter{topnumber}{3}
+\setcounter{bottomnumber}{3}
+\setcounter{totalnumber}{4}
 
@@
 
-```{r setup, echo=F}
+```{r setup, echo=F, message = F, warning= F}
 library(tidyverse)
+library(stargazer)
+library(sandwich)
+library(lmtest)
+library(knitr)
+library(kableExtra)
+knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
 ```
@@
 
-## Figures
+### Descriptive Statistics
 ```{r,  echo=F}
-regResultList <- readRDS("../regresults.rds")
+descriptiveData <-  readRDS("../tableData.rds")
+
+knitr::kable(descriptiveData$tableOurs,
+             caption = "Manufacturing Job Changes 2012-2015",
+             booktabs = TRUE, digits = 2, format = 'latex')  %>%
+  kable_styling(latex_options = c("hold_position", "scale_down"))
+
+knitr::kable(descriptiveData$table04,
+             caption = "Manufacturing Job Changes 2004-2015",
+             booktabs = TRUE, digits = 2, format = 'latex')  %>%
+  kable_styling(latex_options = c("hold_position", "scale_down"))
 
@@
 
-### descriptive statistics
+## Figures
 
@@
 ### Regression summaries
+
+```{r,  echo=F, message = F, results = "asis"}
+
+regResultList <- readRDS("../regresults.rds")
+
+rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelNetCA$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelNetC$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelWNetCA$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelWNetC$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetCA$coefficients 
+)[rownames(regResultList$secondStageModelWNetCA$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$coefficients
+)[rownames(regResultList$secondStageModelWNetC$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelNetCA$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelNetC$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelWNetCA$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelWNetC$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+names(regResultList$rseNetCA_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseNetC_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseWNetCA_2)[1] <- "White Manufacturing Layoffs"
+names(regResultList$rseWNetC_2)[1] <- "White Manufacturing Layoffs"
+
+names(regResultList$rseWNetCA_2)[names(regResultList$rseWNetCA_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+names(regResultList$rseWNetC_2)[names(regResultList$rseWNetC_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+
+stargazer(regResultList$secondStageModelNetCA,
+          regResultList$secondStageModelNetC,
+          regResultList$secondStageModelWNetCA,
+          regResultList$secondStageModelWNetC,
+          se = list(
+            regResultList$rseNetCA_2,
+            regResultList$rseNetC_2,
+            regResultList$rseWNetCA_2,
+            regResultList$rseWNetC_2
+          ),
+          title = "Effect of Manufacturing Layoffs on Democratic Vote Share",
+          dep.var.labels = "Change in Share (2012-2016)",
+          omit.stat = c("rsq","ser"),
+          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
+          add.lines = list(
+            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
+          ),
+          digits = 2,
+          type = "latex"
+)
+
+```
+
+```{r,  echo=F, message = F, results = "asis"}
+
+rownames(regResultList$secondStageModelNetC04A$coefficients )[rownames(regResultList$secondStageModelNetC04A$coefficients)=="firstStageModelNetC04A$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC04$coefficients )[rownames(regResultList$secondStageModelNetC04$coefficients)=="firstStageModelNetC04$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04A$coefficients )[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="firstStageModelWNetC04A$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$coefficients )[rownames(regResultList$secondStageModelWNetC04$coefficients)=="firstStageModelWNetC04$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetC04A$coefficients
+)[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$coefficients
+)[rownames(regResultList$secondStageModelWNetC04$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelNetC04A$beta )[rownames(regResultList$secondStageModelNetC04A$beta) =="firstStageModelNetC04A$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC04$beta )[rownames(regResultList$secondStageModelNetC04$beta)=="firstStageModelNetC04$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="firstStageModelWNetC04A$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="firstStageModelWNetC04$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+names(regResultList$rseNetC04A_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseNetC04_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseWNetC04A_2)[1] <- "White Manufacturing Layoffs"
+names(regResultList$rseWNetC04_2)[1] <- "White Manufacturing Layoffs"
+
+names(regResultList$rseWNetC04A_2)[names(regResultList$rseWNetC04A_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+names(regResultList$rseWNetC04_2)[names(regResultList$rseWNetC04_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+
+stargazer(regResultList$secondStageModelNetC04A,
+          regResultList$secondStageModelNetC04,
+          regResultList$secondStageModelWNetC04A,
+          regResultList$secondStageModelWNetC04,
+          se = list(
+            regResultList$rseNetC04A_2,
+            regResultList$rseNetC04_2,
+            regResultList$rseWNetC04A_2,
+            regResultList$rseWNetC04_2
+          ),
+          title = "Effect of Manufacturing Layoffs on Democratic Vote Share (since 2004)",
+          dep.var.labels = "Change in Share (2016-2012)",
+          omit.stat = c("rsq","ser"),
+          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
+          add.lines = list(
+            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
+          ),
+          digits = 2,
+          type = "latex"
+)
+
+```
 
@@
 
-## Future steps
+## Potential Future Work
 

### 2021-11-29 rCode/replicateRegsAndExtend.R

@@ -160,165 +160,48 @@ ourDatasetBase <- censusCountyData %>%
 
 
 datasetClean <- function(electionYear, startYear, aggregateYears){
+  
+  tmp <- ourDatasetBase %>% 
+    group_by(state_fips, county_fips) %>% 
+    mutate(emp2011_total = mean(totalEmp[year == startYear]),
+           emp2011_mfg = mean(mfgEmp[year == startYear])) %>% 
+    filter(year %in% aggregateYears) %>%  
+    group_by() %>% 
+    group_by(wNw, state_fips, county_fips, emp2011_total, emp2011_mfg) %>% 
+    arrange(time) %>% 
+    summarize(
+      layoffCV = sd(mfgEmp, na.rm = T)/mean(mfgEmp, na.rm = T),
+      totalEmp = mean(totalEmp, na.rm = T), 
+      mfgEmp = mean(mfgEmp, na.rm = T),
+      mfgLayoffs = sum(mfgLayoffs, na.rm = T),
+      mfgLayoffsS = sum(mfgLayoffsS, na.rm = T),
+      mfgNetChange  = -sum(mfgNetChange, na.rm = T),
+      population = mean(population, na.rm = T)
+    )
+  
   BWDataByCounty %>%  filter(year == electionYear) %>%  dplyr::rename(BWLayoffs = mfgLayoffs) %>% 
-    left_join(ourDatasetBase %>% 
-                group_by(state_fips, county_fips) %>% 
-                mutate(emp2011_total = mean(totalEmp[year == 2011]),
-                       emp2011_mfg = mean(mfgEmp[year == 2011])) %>% 
-                group_by(wNw, state_fips, county_fips) %>% 
-                filter(year %in% 2012:2015) %>%  
-                arrange(time) %>% 
-                summarize(
-                  layoffCV = sd(mfgEmp, na.rm = T)/mean(mfgEmp, na.rm = T),
-                  totalEmp = mean(totalEmp, na.rm = T), 
-                  mfgEmp = mean(mfgEmp, na.rm = T),
-                  mfgLayoffs = sum(mfgLayoffs, na.rm = T),
-                  mfgLayoffsS = sum(mfgLayoffsS, na.rm = T),
-                  mfgNetChange  = -sum(mfgNetChange, na.rm = T),
-                  population = mean(population, na.rm = T)
[…]

### 2021-11-29 rCode/tablesAndFigures.R

@@ -6,60 +6,83 @@
 #########################################
 
 
-censusCountyData  <- readRDS("data/censusDataByCounty.rds")
+datasetList <- readRDS("regData.rds")
 
-descDatasetBase <- censusCountyData %>%
-  mutate(year = as.integer(substr(time, 0, 4))) %>% 
-  mutate(wNw = case_when(
-    race == "A0" & ethnicity == "A0" ~ "Total",
-    race == "A1" & ethnicity == "A1" ~ "White",
-    race != "A0" & ethnicity != "A0" ~ "Non-white",
-    TRUE ~ "na"
-  )) %>% 
-  filter(wNw != "na") %>% 
-  group_by(wNw, state_fips, county_fips, year, time) %>% 
-  summarize(
-    totalEmp = sum(totalEmp, na.rm = T),
-    mfgEmp = sum(mfgEmp, na.rm = T), 
-    mfgLayoffs = sum(mfgLayoffs, na.rm = T),
-    mfgLayoffsS = sum(mfgLayoffsS, na.rm = T),
-    mfgNetChange  = sum(mfgNetChange, na.rm = T),
-    population = last(population)
-  )
-
-descDatasetRaw <- descDatasetBase %>% 
-              group_by(wNw, state_fips, county_fips) %>% 
-              filter(year %in% 2012:2015) %>%  
-              arrange(time) %>% 
-              summarize(
-                layoffCV = sd(mfgEmp, na.rm = T)/mean(mfgEmp, na.rm = T),
-                totalEmp = mean(totalEmp, na.rm = T), 
-                mfgEmp = mean(mfgEmp, na.rm = T),
-                mfgLayoffs = sum(mfgLayoffs, na.rm = T),
-                mfgLayoffsS = sum(mfgLayoffsS, na.rm = T),
-                mfgNetChange  = -sum(mfgNetChange, na.rm = T),
-                population = mean(population, na.rm = T)
-              ) %>%
-  filter(mfgEmp != 0)  %>% 
-  rename(countyPop = population)
-
-
-descDatasetRaw %>% 
-  dplyr::select(wNw, state_fips, county_fips, totalEmp, mfgEmp, mfgNetChange) %>% 
-  mutate(wNw = factor(x = wNw, levels = c("Total", "White", "Non-white"))) %>% 
+tableOurs <- datasetList$datasetOurs %>% 
[…]

### 2021-11-29 rCode/Draft.Rmd
CD adding maps and other visuals

@@
 library(kableExtra)
+library(readxl)
 knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
@@
 ## Findings
+
+```{r}
+# manufacturing layoffs overtime
+
+national_ts <- read_xlsx("../data/National_Data_TS.xlsx")
+
+national_ts <- national_ts %>%
+  rename(year = 1,
+         net_job_change = 2) %>%
+  dplyr::select(year, net_job_change) %>%
+  mutate(net_job_change*4)
+
+ggplot(data = national_ts, aes(x = year, y = net_job_change)) +
+  geom_point()
+
+```
 
@@
 
+```{r,  echo=F, message = F, results = "asis"}
+
+# show map
+model_input <- readRDS("../model_3_input.rds")
+model_results <- readRDS("../model_3_results.rds")
+
+# load voting data
+library(data.table)
+voting <- fread("C:\\Users\\darin\\OneDrive\\Documents\\school\\MPP1 Fall Semester\\GOV 2001\\Replication File\\cd\\voting data.csv")
+
+model_input <- model_input %>%
+  filter(is.finite(bartik_leo5_w2),
+         is.finite(mfgNetChange_white),
+         is.finite(mfgNetChange_nonwhite))
+
+p75 <- quantile(model_input$mfgNetChange_white, (.75))
+
+model_input$P_ddem_1 <- model_results$fitted.values
+
+model_input <- model_input %>%
+  mutate(
+         CF_netchange = p75,
+         CF_d_netchange = CF_netchange - mfgNetChange_white,
+         CF_ddem_change = CF_d_netchange*model_results$coefficients[1],
+         P_ddem_2 = P_ddem_1 + CF_ddem_change) %>%
+  dplyr::select(id, state_fips, state, state_name, county_fips,
+                county, year, dem_votes_pct1, ddem_votes_pct1,
+                P_ddem_1, mfgNetChange_white, mfgNetChange_total,
+                mfgNetChange_nonwhite,
+                CF_netchange,
+                CF_d_netchange,
+                CF_ddem_change,
+                P_ddem_2)
+
+voting <- voting %>%
+  dplyr::select(year, state, county_name, county_fips,
+         party, candidatevotes) %>%
+  filter(party == "DEMOCRAT" | party == "REPUBLICAN") %>%
+  group_by(year, county_fips) %>%
+  summarize(total_dem_rep_votes = sum(candidatevotes),
+         dem_votes = sum(candidatevotes[party == "DEMOCRAT"]),
+         rep_votes = sum(candidatevotes[party == "REPUBLICAN"])) %>%
+  mutate(dem_vote_share = dem_votes/total_dem_rep_votes)
+
+model_input <- model_input %>% mutate(
+  c_fips_long = case_when(
+    str_length(as.character(county_fips)) == 1 ~
+      paste0("00", as.character(county_fips)),
+    str_length(as.character(county_fips)) == 2 ~
+      paste0("0", as.character(county_fips)),
+    TRUE ~ as.character(county_fips)),
+
+  s_fips_long  = case_when(
+    str_length(as.character(state_fips)) == 1 ~
+      paste0("0", as.character(state_fips)),
+    TRUE ~ as.character(state_fips)),
+
+  fips_long = paste0(s_fips_long, c_fips_long),
+  fips_numeric = as.numeric(fips_long))
+
+model_input <- left_join(model_input, voting,
+                          by = c("fips_numeric" = "county_fips",
+                                 "year" = "year"))
+
+model_input <- model_input %>%
+  mutate(CF_dem_votes = dem_votes +
+           CF_ddem_change*total_dem_rep_votes,
+         CF_rep_votes = rep_votes - CF_ddem_change*total_dem_rep_votes)
+
+order = c("-2% or greater", "-1% to -2%", "-0.5% to -1%",
+          "-0.25% to -0.5%", "0% to -0.25%", "0% to +0.25%")
+
+state_summary <- model_input %>%
+  group_by(state_name, state) %>%
+  summarize(actual_trump_votes = sum(rep_votes),
+            actual_dem_votes = sum(dem_votes),
+            CF_trump_votes = sum(CF_rep_votes),
+            CF_dem_votes = sum(CF_dem_votes)) %>%
+
+  mutate(changed_outcome  =
+           ifelse(
+             CF_dem_votes > CF_trump_votes &
+               actual_trump_votes > actual_dem_votes,
+             1, 0),
+    actual_trump_vs =
+      actual_trump_votes/(actual_trump_votes+ actual_dem_votes),
+    CF_trump_vs =
+      CF_trump_votes/(CF_trump_votes+CF_dem_votes),
+    delta_vs = CF_trump_vs - actual_trump_vs) %>%
+  mutate(
+    delta_vs = case_when(delta_vs < -.02 ~ "-2% or greater",
+                         delta_vs < -.01 ~ "-1% to -2%",
+                         delta_vs < -.005 ~ "-0.5% to -1%",
+                         delta_vs < -.0025 ~ "-0.25% to -0.5%",
+                         delta_vs < 0 ~ "0% to -0.25%",
+                         delta_vs < .0025 ~ "0% to +0.25%",
+                         delta_vs < .005 ~ "+0.25% to +0.5%",
+                         delta_vs < .01 ~ "+0.5% to +1%",
+                         TRUE ~ "+1% or greater")) %>%
+  mutate(delta_vs_group = factor(delta_vs, levels = order))
+
+colors =
+   c("-2% or greater" = "#0059ff",
+     "-1% to -2%" = "#4988fc",
+     "-0.5% to -1%" = "#86b0fc",
+     "-0.25% to -0.5%" = "#b8d1ff",
+     "0% to -0.25%" = "#dee9fc",
+     "0% to +0.25%" = "#ffeae8")
+
+# map change in trump vote share
+library(tigris)
+
+# state shapefile
+state_shape <- states(
+  cb = TRUE,
+  resolution = "20m"
+) %>%
+  filter(GEOID != "72") %>%
+  shift_geometry()
+
+mapping <- inner_join(state_shape, state_summary,
+                      by = c("NAME" = "state_name"))
+
+#devtools::install_github("yutannihilation/ggsflabel")
+library(ggsflabel)
+
+mapping_small <- mapping %>% filter(state != "DC")
+
+mapping_small <- mapping_small %>%
+  mutate(changed_outcome = ifelse(changed_outcome == 0,
+                                  "No",
+                                  "Yes"))
+
+#  alt
+flipped <- mapping_small %>% filter(changed_outcome == "Yes")
+ggplot() +
+  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "grey", size = .01) +
+  scale_fill_manual(values = colors) +
+  labs(title = "Figure X:\nManufacturing Layoffs Led Trump to 2016 Victory",
+       subtitle = "Change in Trump Vote Share Assuming Counterfactual Manufacturing Layoffs (25th Percentile)",
+       fill = "Change in Trump Vote Share") +
+  geom_sf(data = flipped, fill = NA, aes(color = changed_outcome), size = 1) +
+  scale_color_manual(values = "#b32ab5", name = "Flipped Election") +
+  labs(color = "Flipped Election") +
+  coord_sf(datum = NA) +
+  theme_minimal() +
+  # geom_sf_text_repel(aes(label = state), data = mapping_small,
+  #                    force = .00001,  seed = 10,
+  #                    size = 2.5) +
+  theme(  axis.title.x=element_blank(),
+          axis.title.y=element_blank())
+
+```
+
 ### example state: Michigan

### 2021-11-29 rCode/cd_test.Rmd
CD adding maps and other visuals

--- 2021-11-28 rCode/Draft.Rmd
@@
 ---
-title: '\bf Replication Paper'
-author: 'Catherine Darin and Zagreb Mukerjee'
-date: 'Released: \today'
-fontsize: 12pt
 output:
   pdf_document: default
-urlcolor: red
-header-includes:
-  - \usepackage{bm}
+  html_document: default
 ---
+```{r,  echo=F, message = F, results = "asis"}
 
-## Outline
-- Framing story: the trajectory of XYZ county that swung from O to T and suffered big manufacturing layoffs
-- Substantive importance: Why did Trump win in 2016? A longstanding debate about relative importance of race and economic factors. Complicated by the interaction of the two. We can tease out 
-- Empirical strategy: Differential manuf.
-exposure across counties allows for identification of the causal effect of deindustrialization on change in Dem vote share.
-Further differences in racial exposure to mfg layoffs allows for identification of the interaction between race and deindustrialization.
-- Data: census Quarterly Workforce Indicators, which break down employment by industry, race and ethnicity. Compute net change in mfg (long term job loss)
+library(tidyverse)
+# show map
+model_input <- readRDS("../model_3_input.rds")
+model_results <- readRDS("../model_3_results.rds")
 
-```{r setup, echo=F}
-library(tidyverse)
-```
+# load voting data
+library(data.table)
+voting <- fread("C:\\Users\\darin\\OneDrive\\Documents\\school\\MPP1 Fall Semester\\GOV 2001\\Replication File\\cd\\voting data.csv")
 
-## Findings
+model_input <- model_input %>%
+  filter(is.finite(bartik_leo5_w2),
+         is.finite(mfgNetChange_white),
+         is.finite(mfgNetChange_nonwhite))
 
-## Figures
-```{r,  echo=F}
-regResultList <- readRDS("../regresults.rds")
+p75 <- quantile(model_input$mfgNetChange_white, (.75))
+
+model_input$P_ddem_1 <- model_results$fitted.values
+
+model_input <- model_input %>%
+  mutate(
+         CF_netchange = p75,
+         CF_d_netchange = CF_netchange - mfgNetChange_white,
+         CF_ddem_change = CF_d_netchange*model_results$coefficients[1],
+         P_ddem_2 = P_ddem_1 + CF_ddem_change) %>%
+  dplyr::select(id, state_fips, state, state_name, county_fips,
+                county, year, dem_votes_pct1, ddem_votes_pct1,
+                P_ddem_1, mfgNetChange_white, mfgNetChange_total,
+                mfgNetChange_nonwhite,
+                CF_netchange,
+                CF_d_netchange,
+                CF_ddem_change,
+                P_ddem_2)
+
+voting <- voting %>%
+  dplyr::select(year, state, county_name, county_fips,
+         party, candidatevotes) %>%
+  filter(party == "DEMOCRAT" | party == "REPUBLICAN") %>%
+  group_by(year, county_fips) %>%
+  summarize(total_dem_rep_votes = sum(candidatevotes),
+         dem_votes = sum(candidatevotes[party == "DEMOCRAT"]),
+         rep_votes = sum(candidatevotes[party == "REPUBLICAN"])) %>%
+  mutate(dem_vote_share = dem_votes/total_dem_rep_votes)
+
+model_input <- model_input %>% mutate(
+  c_fips_long = case_when(
+    str_length(as.character(county_fips)) == 1 ~
+      paste0("00", as.character(county_fips)),
+    str_length(as.character(county_fips)) == 2 ~
+      paste0("0", as.character(county_fips)),
+    TRUE ~ as.character(county_fips)),
+
+  s_fips_long  = case_when(
+    str_length(as.character(state_fips)) == 1 ~
+      paste0("0", as.character(state_fips)),
+    TRUE ~ as.character(state_fips)),
+
+  fips_long = paste0(s_fips_long, c_fips_long),
+  fips_numeric = as.numeric(fips_long))
+
+model_input <- left_join(model_input, voting,
+                          by = c("fips_numeric" = "county_fips",
+                                 "year" = "year"))
+
+model_input <- model_input %>%
+  mutate(CF_dem_votes = dem_votes +
+           CF_ddem_change*total_dem_rep_votes,
+         CF_rep_votes = rep_votes - CF_ddem_change*total_dem_rep_votes)
+
+order = c("-2% or greater", "-1% to -2%", "-0.5% to -1%",
+          "-0.25% to -0.5%", "0% to -0.25%", "0% to +0.25%")
+
+state_summary <- model_input %>%
+  group_by(state_name, state) %>%
+  summarize(actual_trump_votes = sum(rep_votes),
+            actual_dem_votes = sum(dem_votes),
+            CF_trump_votes = sum(CF_rep_votes),
+            CF_dem_votes = sum(CF_dem_votes)) %>%
+
+  mutate(changed_outcome  =
+           ifelse(
+             CF_dem_votes > CF_trump_votes &
+               actual_trump_votes > actual_dem_votes,
+             1, 0),
+    actual_trump_vs =
+      actual_trump_votes/(actual_trump_votes+ actual_dem_votes),
+    CF_trump_vs =
+      CF_trump_votes/(CF_trump_votes+CF_dem_votes),
+    delta_vs = CF_trump_vs - actual_trump_vs) %>%
+  mutate(
+    delta_vs = case_when(delta_vs < -.02 ~ "-2% or greater",
+                         delta_vs < -.01 ~ "-1% to -2%",
+                         delta_vs < -.005 ~ "-0.5% to -1%",
+                         delta_vs < -.0025 ~ "-0.25% to -0.5%",
+                         delta_vs < 0 ~ "0% to -0.25%",
+                         delta_vs < .0025 ~ "0% to +0.25%",
+                         delta_vs < .005 ~ "+0.25% to +0.5%",
+                         delta_vs < .01 ~ "+0.5% to +1%",
+                         TRUE ~ "+1% or greater")) %>%
+  mutate(delta_vs_group = factor(delta_vs, levels = order))
+
+colors =
+   c("-2% or greater" = "#0059ff",
+     "-1% to -2%" = "#4988fc",
+     "-0.5% to -1%" = "#86b0fc",
+     "-0.25% to -0.5%" = "#b8d1ff",
+     "0% to -0.25%" = "#dee9fc",
+     "0% to +0.25%" = "#ffeae8")
+
+# map change in trump vote share
+library(tigris)
+
+# state shapefile
+state_shape <- states(
+  cb = TRUE,
+  resolution = "20m"
+) %>%
+  filter(GEOID != "72") %>%
+  shift_geometry()
+
+mapping <- inner_join(state_shape, state_summary,
+                      by = c("NAME" = "state_name"))
+
+#devtools::install_github("yutannihilation/ggsflabel")
+library(ggsflabel)
+
+mapping_small <- mapping %>% filter(state != "DC")
+
+mapping_small <- mapping_small %>%
+  mutate(changed_outcome = ifelse(changed_outcome == 0,
+                                  "No",
+                                  "Yes"))
+
+#  alt
+flipped <- mapping_small %>% filter(changed_outcome == "Yes")
+ggplot() +
+  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "grey", size = .01) +
+  scale_fill_manual(values = colors) +
+  labs(title = "Figure X:\nManufacturing Layoffs Led Trump to 2016 Victory",
+       subtitle = "Change in Trump Vote Share Assuming Counterfactual Manufacturing Layoffs (25th Percentile)",
+       fill = "Change in Trump Vote Share") +
+  geom_sf(data = flipped, fill = NA, aes(color = changed_outcome), size = 1) +
+  scale_color_manual(values = "#b32ab5", name = "Flipped Election") +
+  labs(color = "Flipped Election") +
+  coord_sf(datum = NA) +
+  theme_minimal() +
+  # geom_sf_text_repel(aes(label = state), data = mapping_small,
+  #                    force = .00001,  seed = 10,
+  #                    size = 2.5) +
+  theme(  axis.title.x=element_blank(),
+          axis.title.y=element_blank())
 
 ```
-
-### descriptive statistics
-
-### Example
-
-### Regression summaries
-
-### Counterfactual assessment of election
-
-### example state: Michigan
-
-### 2020
-
-## Future steps
-
-- Disaggregation: Instead of instrumenting by manufacturing share, perhaps we can look at layoffs by industry in each county.
-While aggregate manufacturing employment may be endogeneous, there's less reason to believe that specific industries would be (cf.
-Autor, Dorn and Hanson).
-This may also allow us to get further away from ecological inference problems.
-- Trend-cycle estimation: There are techniques from econometrics and other places that could potentially be used to decompose gross layoffs into seasonal and non-seasonal components.
-
-## Appendix

### 2021-11-29 rCode/Draft.Rmd
adding short version of regs

--- 2021-11-29 rCode/Draft.Rmd
@@
 library(kableExtra)
+library(readxl)
+library(scales)
 knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
@@
 ## Findings
+
+```{r}
+# manufacturing layoffs overtime
+
+national_ts <- read_xlsx("../data/National_Data_TS.xlsx")
+
+national_ts <- national_ts %>%
+  rename(year = 1,
+         net_job_change = 2) %>%
+  dplyr::select(year, net_job_change) %>%
+  mutate(
+    year = as.numeric(year),
+    net_job_change = net_job_change*4) %>% group_by()
+
+ggplot(data = national_ts %>% filter(year >= 1995), aes(x = year, y = net_job_change)) +
+  geom_col() + scale_x_continuous(breaks=seq(1995,2019,2)) +
+	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6))
+
+```
 
@@
 ### Counterfactual assessment of election
+## (Using 2004-2015 Layoffs)
+
+```{r,  echo=F, message = F, results = "asis"}
+
+# load map
+model_input <- readRDS("../model_5_input.rds")
+model_results <- readRDS("../model_5_results.rds")
+
+# load voting data
+library(data.table)
+voting <- fread("C:\\Users\\darin\\OneDrive\\Documents\\school\\MPP1 Fall Semester\\GOV 2001\\Replication File\\cd\\voting data.csv")
+
+# filter model input based on our regression filtering
+model_input <- model_input %>%
+  filter(is.finite(bartik_leo5_w2),
+         is.finite(mfgNetChange_white),
+         is.finite(mfgNetChange_nonwhite))
+
+# find the 25th percentile in manufacturing layoffs (our measure) across counties
+p25 <- quantile(model_input$mfgNetChange_white, (.25))
+
+# find the predicted democratic vote share
+model_input$P_ddem_1 <- model_results$fitted.values
+
+model_input <- model_input %>%
+  mutate(
+
+    # calculate the counterfactual change in democratic vote share
+    # by multipling our regression coefficient against the difference
+    # between observed manufacturing layoffs (our measure) and the
+    # 25th percentile of layoffs (nationally)
+         CF_netchange = p25,
+         CF_d_netchange = CF_netchange - mfgNetChange_white,
+         CF_ddem_change = CF_d_netchange*model_results$coefficients[1],
+         P_ddem_2 = P_ddem_1 + CF_ddem_change) %>%
+  dplyr::select(id, state_fips, state, state_name, county_fips,
+                county, year, dem_votes_pct1, ddem_votes_pct1,
+                P_ddem_1, mfgNetChange_white, mfgNetChange_total,
+                mfgNetChange_nonwhite,
+                CF_netchange,
+                CF_d_netchange,
+                CF_ddem_change,
+                P_ddem_2)
+
+# clear voting data
+voting <- voting %>%
+  dplyr::select(year, state, county_name, county_fips,
+         party, candidatevotes) %>%
+  filter(party == "DEMOCRAT" | party == "REPUBLICAN") %>%
+  group_by(year, county_fips) %>%
+  summarize(total_dem_rep_votes = sum(candidatevotes),
+         dem_votes = sum(candidatevotes[party == "DEMOCRAT"]),
+         rep_votes = sum(candidatevotes[party == "REPUBLICAN"])) %>%
+  mutate(dem_vote_share = dem_votes/total_dem_rep_votes)
+
+# prep model input data to be merged to voting data
+model_input <- model_input %>% mutate(
+  c_fips_long = case_when(
+    str_length(as.character(county_fips)) == 1 ~
+      paste0("00", as.character(county_fips)),
+    str_length(as.character(county_fips)) == 2 ~
+      paste0("0", as.character(county_fips)),
+    TRUE ~ as.character(county_fips)),
+  s_fips_long  = case_when(
+    str_length(as.character(state_fips)) == 1 ~
+      paste0("0", as.character(state_fips)),
+    TRUE ~ as.character(state_fips)),
+
+  fips_long = paste0(s_fips_long, c_fips_long),
+  fips_numeric = as.numeric(fips_long))
+
+# join model input to observed voting data
+model_input <- left_join(model_input, voting,
+                          by = c("fips_numeric" = "county_fips",
+                                 "year" = "year"))
+
+# calculate the counterfactual dem votes and rep votes
+model_input <- model_input %>%
+  mutate(CF_dem_votes = dem_votes +
+           CF_ddem_change*total_dem_rep_votes,
+         CF_rep_votes = rep_votes - CF_ddem_change*total_dem_rep_votes)
+
+# create mapping categories
+order = c(
+  #"+2% or greater", "+1% to +2%",
+          "+0.5% to +1%",
+          "+0.25% to +0.5%", 
+          "0% to +0.25%", 
+          "0% to -0.25%")
+
+state_summary <- model_input %>%
+  group_by(state_name, state) %>%
+  summarize(actual_trump_votes = sum(rep_votes),
+            actual_dem_votes = sum(dem_votes),
+            CF_trump_votes = sum(CF_rep_votes),
+            CF_dem_votes = sum(CF_dem_votes)) %>%
+
+  mutate(changed_outcome  =
+           ifelse(
+             CF_dem_votes > CF_trump_votes &
+               actual_trump_votes > actual_dem_votes,
+             1, 0),
+    actual_trump_vs =
+      actual_trump_votes/(actual_trump_votes+ actual_dem_votes),
+    CF_trump_vs =
+      CF_trump_votes/(CF_trump_votes+CF_dem_votes),
+    delta_vs = CF_trump_vs - actual_trump_vs) %>%
+  mutate(
+    delta_vs = case_when(delta_vs < -.02 ~ "+2% or greater",
+                         delta_vs < -.01 ~ "+1% to +2%",
+                         delta_vs < -.005 ~ "+0.5% to +1%",
+                         delta_vs < -.0025 ~ "+0.25% to +0.5%",
+                         delta_vs < 0 ~ "0% to +0.25%",
+                         delta_vs < .0025 ~ "0% to -0.25%",
+                         delta_vs < .005 ~ "-0.25% to -0.5%",
+                         delta_vs < .01 ~ "-0.5% to -1%",
+                         TRUE ~ "-1% or greater")) %>%
+  mutate(delta_vs_group = factor(delta_vs, levels = order))
+
+colors =
+   c(
+     #"+2% or greater" = "#0059ff",
+     #"+1% to +2%" = "#4988fc",
+     "+0.5% to +1%" = "#86b0fc",
+     "+0.25% to +0.5%" = "#b8d1ff",
+     "0% to +0.25%" = "#dee9fc",
+     "0% to -0.25%" = "#ffeae8")
+
+# map change in trump vote share
+library(tigris)
+
+# state shapefile
+state_shape <- states(
+  cb = TRUE,
+  resolution = "20m"
+) %>%
+  filter(GEOID != "72") %>%
+  shift_geometry()
+
+mapping <- inner_join(state_shape, state_summary,
+                      by = c("NAME" = "state_name"))
+
+#devtools::install_github("yutannihilation/ggsflabel")
+library(ggsflabel)
+
+mapping_small <- mapping %>% filter(state != "DC")
+
+mapping_small <- mapping_small %>%
+  mutate(changed_outcome = ifelse(changed_outcome == 0,
+                                  "No",
+                                  "Yes"))
+
+#  alt
+flipped <- mapping_small %>% filter(changed_outcome == "Yes")
+ggplot() +
+  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "grey", size = .01) +
+  scale_fill_manual(values = colors) +
+  labs(title = "Figure X:\nWithout Manufacturing Layoffs, Democrats Would Have Won 2016 Election",
+       subtitle = "Change in Democratic Vote Share Assuming Counterfactual Manufacturing Layoffs (25th Percentile)",
+       fill = "Change in Democratic Vote Share") +
+  geom_sf(data = flipped, fill = NA, aes(color = changed_outcome), size = 1) +
+  scale_color_manual(values = "#b32ab5", name = "Flipped Election") +
+  labs(color = "Flipped Election") +
+  coord_sf(datum = NA) +
+  theme_minimal() +
+  # geom_sf_text_repel(aes(label = state), data = mapping_small,
+  #                    force = .00001,  seed = 10,
+  #                    size = 2.5) +
+  theme(  axis.title.x=element_blank(),
+          axis.title.y=element_blank())
+
+```
 

### 2021-11-29 rCode/censusAPIPull.R

@@ -28,7 +28,7 @@ totalData <- bind_rows(lapply(
       vars = c("race", "ethnicity", "Emp"),
       region = "county:*",
       seasonadj = "U",
-      regionin = paste0("state:", str_pad(stateNum, 2, pad = "0")), time = "from 2004 to 2016") %>% 
+      regionin = paste0("state:", str_pad(stateNum, 2, pad = "0")), time = "from 2003 to 2016") %>% 
       rename(totalEmp = Emp) %>% tibble() }
 ))
 
@@ -42,7 +42,7 @@ mfgData <- bind_rows(lapply(
       ownercode = "A05",
       region = "county:*",
       seasonadj = "U",
-      regionin = paste0("state:", str_pad(stateNum, 2, pad = "0")), time = "from 2004 to 2016") %>% 
+      regionin = paste0("state:", str_pad(stateNum, 2, pad = "0")), time = "from 2003 to 2016") %>% 
       rename(mfgEmp = Emp, mfgLayoffs = FrmJbLs, mfgLayoffsS = FrmJbLsS, mfgNetChange = FrmJbC)  %>% tibble()}
 ))
 

### 2021-11-29 rCode/replicateRegsAndExtend_short v2.R

@@ -1,0 +1,532 @@
+
+
+source("rCode/preamble.R")
+BWDataByCounty <- readRDS("data/BWCountyLevel.rds")
+
+#################################################################################
+# First we run our code with their data to replicate 
+# table 2 in Baccini and Weymouth's paper
+#################################################################################
+
+# load B&W data
+BWDataByCounty_16 <- BWDataByCounty %>%  filter(year == 2016)
+
+# model 1
+BW_firstStageModel1 <- felm(
+  data = BWDataByCounty_16,
+  formula = mfgLayoffs ~ bartik_leo5 +
+    LAU_unemp_rate_4y + pers_m_total_share_4y +
+    pers_coll_share_4y | id_state)
+
+BW_secondStageModel1 <- felm(
+  data = BWDataByCounty_16,
+  formula = ddem_votes_pct1 ~ BW_firstStageModel1$fitted.values +
+    LAU_unemp_rate_4y + pers_m_total_share_4y +
+    pers_coll_share_4y | id_state)
+
+rse1_1 <- coeftest(BW_firstStageModel1, vcov = vcovHC(BW_firstStageModel1, type = "HC0"))[,2]
+rse1_2 <- coeftest(BW_secondStageModel1, vcov = vcovHC(BW_secondStageModel1, type = "HC0"))[,2]
+
+# model 2
+BW_firstStageModel2 <- felm(
+  data = BWDataByCounty_16 %>% filter(!is.na(white_counties_4y)),
+  formula = mfgLayoffs ~ bartik_leo5 +
+    LAU_unemp_rate_4y + pers_m_total_share_4y +
+    pers_coll_share_4y + white_counties_4y | id_state)
+
+BW_secondStageModel2 <- felm(
+  data = BWDataByCounty_16 %>% filter(!is.na(white_counties_4y)),
+  formula = ddem_votes_pct1 ~ BW_firstStageModel2$fitted.values +
+    LAU_unemp_rate_4y + pers_m_total_share_4y +
+    pers_coll_share_4y + white_counties_4y | id_state)
+
+rse2_1 <- coeftest(BW_firstStageModel2, vcov = vcovHC(BW_firstStageModel2, type = "HC0"))[,2]
+rse2_2 <- coeftest(BW_secondStageModel2, vcov = vcovHC(BW_secondStageModel2, type = "HC0"))[,2]
+
+# model 3
+BW_firstStageModel3 <- felm(
+  data = BWDataByCounty_16 %>% filter(!is.na(msl_service_pc4y),
[…]

### 2021-11-29 rCode/replicateRegsAndExtend_short v2.R
rename saved data. delete some old code

@@ -178,26 +178,21 @@ datasetClean <- function(electionYear, startYear, aggregateYears){
     group_by(wNw, state_fips, county_fips, emp_base_total, emp_base_mfg) %>% 
     arrange(time) %>% 
     summarize(
-      #layoffCV = sd(mfgEmp, na.rm = T)/mean(mfgEmp, na.rm = T), #not using this variable
       totalEmp = mean(totalEmp, na.rm = T), 
       mfgEmp = mean(mfgEmp, na.rm = T),
       mfgLayoffs = sum(mfgLayoffs, na.rm = T),
-      # mfgLayoffsS = sum(mfgLayoffsS, na.rm = T), #not using this variable
       mfgNetChange  = -sum(mfgNetChange, na.rm = T),
       population = mean(population, na.rm = T)
     )
   
   BWDataByCounty %>%  filter(year == electionYear) %>%  dplyr::rename(BWLayoffs = mfgLayoffs) %>% 
     left_join( tmp)  %>%
-    #filter(mfgEmp != 0)  %>% 
     rename(countyPop = population) %>%  
     filter(is.finite(white_counties_4y), is.finite(msl_service_pc4y))  %>%
     pivot_wider(names_from = wNw, 
                 values_from = c(totalEmp, mfgEmp, 
                                 mfgLayoffs, 
-                                # mfgLayoffsS, # not using this variable for now
-                                mfgNetChange,
-                                #layoffCV  # not using this variable
+                                mfgNetChange
                                 )) %>% 
     mutate(mfgLayoffs_total = mfgLayoffs_total/emp_base_total,
            mfgNetChange_total = mfgNetChange_total/emp_base_total,
@@ -223,7 +218,6 @@ datasetOurs1204 <- datasetClean(electionYear = 2012, startYear = 2004, aggregate
 # our layoff measure, for B&W's models 2, 3, 5 and 6
 ################################################################
 
-# check to see how much it matters how you normalize employment
 
 # model 2
 firstStageModelOurs_2 <- felm(
[…]

### 2021-11-29 rCode/Draft.Rmd
adding voting data

@@
 	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6))
+
+```
+
+### Geographic Concentration of Layoffs
+
+```{r,  echo=F, message = F, results = "asis"}
+
+# load map
+model_input <- readRDS("../model_5_input.rds")
+
+library(tigris)
+
+# state shapefile
+county_shape <- counties(
+  cb = TRUE,
+  resolution = "20m"
+) %>%
+  shift_geometry() %>%
+  mutate(STATEFP = as.numeric(STATEFP),
+         COUNTYFP = as.numeric(COUNTYFP))
+
+# group counties into sextiles 
+model_input <- model_input %>%
+  group_by() %>%
+  mutate(ntile_mfg = as.character(ntile(mfgNetChange_total , 6)))
+
+# find cutoffs
+
+sum <- model_input %>%
+  group_by(ntile_mfg) %>%
+  summarize(min = min(mfgNetChange_total),
+            max = max(mfgNetChange_total))
+
+labels = c(
+  "1" = "Less than -1% (Gain in Mfg. Emp)",
+  "2" = "-1% to 0% (Gain in Mfg. Emp)",
+  "3" = ".001"
+)
+
+mapping_county <- inner_join(county_shape, model_input,
+                      by = c("STATEFP" = "state_fips",
+                             "COUNTYFP" = "county_fips"))
+
+ggplot() +
+  geom_sf(data = mapping_county, aes(fill = mfgNetChange_total), color = NA, size = .01) +
+  scale_fill_viridis_c() +
+  coord_sf(datum = NA) +
+  theme_minimal() +
+  # geom_sf_text_repel(aes(label = state), data = mapping_small,
+  #                    force = .00001,  seed = 10,
+  #                    size = 2.5) +
+  theme(  axis.title.x=element_blank(),
+          axis.title.y=element_blank())
 
@@
 
-#  alt
+#  make map
+
 flipped <- mapping_small %>% filter(changed_outcome == "Yes")
+
 ggplot() +

### 2021-11-29 rCode/Draft.Rmd
updates and text

--- 2021-11-29 rCode/Draft.Rmd
@@
 ---
-title: '\bf Replication Paper'
+title: '\bf Brother, can you spare a manufacturing job? White Voters\' reaction to Deindustrialization'
 author: 'Catherine Darin and Zagreb Mukerjee'
-date: '\today'
+date: '11/29/2021'
 fontsize: 12pt
@@
 
+## Introduction
+
+What led to Donald Trump's surprising 2016 election victory?
+This paper examines the potential contribution of deindustrialization.
+Counties differ by exposure to manufacturing, which we use in an instrumental-variable approach to identify the effect of manufacturing job loss on change in Democratic vote share.
+We find that Democratic vote share falls in counties with high manufacturing job loss since 2004.
+Disaggregating this result by race shows that the vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
+This suggests a racial component to how voters process economic hardship.
+
+Base paper: Baccini and Weymouth 2021, "Gone For Good: Deindustrialization, White Voter Backlash, and US Presidential Voting." *APSR*.
+
 ## Outline
-- Framing story: the trajectory of XYZ county that swung from O to T and suffered big manufacturing layoffs
-- Substantive importance: Why did Trump win in 2016? A longstanding debate about relative importance of race and economic factors. Complicated by the interaction of the two. We can tease out 
-- Empirical strategy: Differential manuf.
-exposure across counties allows for identification of the causal effect of deindustrialization on change in Dem vote share.
+
+#### Framing story
+To do: Qualitative description of the trajectory of XYZ county that swung from O to T and suffered big manufacturing layoffs.
+This will establish the stakes and connect this to the broader conversation.
+
+### Substantive importance
+
+Why did Trump win in 2016?
+A longstanding debate about relative importance of race and economic factors.
+Complicated by the interaction of the two.
+We hope to identify the importance of manufacturing job losses, both in aggregate and for different racial groups.
+
+### Empirical strategy
+
+Differential manufacturing exposure across counties allows for identification of the causal effect of deindustrialization on change in Dem vote share.
 Further differences in racial exposure to mfg layoffs allows for identification of the interaction between race and deindustrialization.
-- Data: census Quarterly Workforce Indicators, which break down employment by industry, race and ethnicity. Compute net change in mfg (long term job loss)
+
+### Data and methods
+
+Data is Census Quarterly Workforce Indicators, which break down county employment by industry, race and ethnicity. Augmented with public data on vote shares, employment, etc.
+
+We look at manufacturing employment (NAICS 31-33, see extensions below). Then  compute net change in mfg jobs (long term job loss) from 2004 to 2015, relative to employment in 2004.
+
+We might be worried about endogeneity for manufacturing job losses.
+So we use a shift-share instrument: we predict job losses per worker with county-level manufacturing as a share of total employment, plus controls.
+
+Controls: unemployment in 2015, college educated share of population, male share of population, layoffs in service sector, white share of population (to control for demographic trends).
+We want to know if there's something singular about manufacturing jobs.
 
@@
 
-knitr::kable(descriptiveData$tableOurs,
-             caption = "Manufacturing Job Changes 2012-2015",
+knitr::kable(descriptiveData$table04,
+             caption = "Manufacturing Job Changes 2004-2015",
              booktabs = TRUE, digits = 2, format = 'latex')  %>%
@@
 
-knitr::kable(descriptiveData$table04,
-             caption = "Manufacturing Job Changes 2004-2015",
+knitr::kable(descriptiveData$tableOurs,
+             caption = "Manufacturing Job Changes 2012-2015",
              booktabs = TRUE, digits = 2, format = 'latex')  %>%
@@
 
+- Temporal: Finding a better way to characterize the potentially lagged effect of manufacturing job losses on Democratic votes. Incorporating study of the 2008, 2012, 2020 elections. 
 - Disaggregation: Instead of instrumenting by manufacturing share, perhaps we can look at layoffs by industry in each county.
@@
 - Trend-cycle estimation: There are techniques from econometrics and other places that could potentially be used to decompose gross layoffs into seasonal and non-seasonal components. 
+- Mechanisms: survey work to examine where the racial difference in economic voting behavior comes from. Is it expressive? Is it because information is transmitted along racially segregated networks?
 

### 2021-11-30 rCode/Draft.Rmd
more text
Adding updatrs to Draft

--- 2021-11-29 rCode/Draft.Rmd
@@
 
+state_shape <- states(
+  cb = TRUE,
+  resolution = "20m"
+) %>%
+  filter(GEOID != "72") %>%
+  shift_geometry()
+
 # group counties into sextiles 
@@
 labels = c(
-  "1" = "Less than -1% (Gain in Mfg. Emp)",
-  "2" = "-1% to 0% (Gain in Mfg. Emp)",
-  "3" = ".001"
-)
+  "1" = "1% or Greater Gain in Mfg. Emp",
+  "2" = "0% to 1% Gain in Mfg. Emp",
+  "3" = "0% to 1% Loss in Mfg. Emp",
+  "4" = "1% to 3% Loss in Mfg. Emp",
+  "5" = "3% to 6% Loss in Mfg. Emp",
+  "6" = "6% or Greater Loss in Mfg. Emp")
 
+colors <- c("1" = "#778868",
+            "2" = "#b5b991",
+            "3" = "#f6edbd",
+            "4" = "#edbb8a",
+            "5" = "#de8a5a",
+            "6" = "#ca562c")
+
+#3d5941,#778868,#b5b991,#f6edbd,#edbb8a,#de8a5a,#ca562c
 mapping_county <- inner_join(county_shape, model_input,
@@
 ggplot() +
-  geom_sf(data = mapping_county, aes(fill = mfgNetChange_total), color = NA, size = .01) +
-  scale_fill_viridis_c() +
+  geom_sf(data = mapping_county, aes(fill = ntile_mfg), 
+          color = NA, size = .01) +
+  scale_fill_manual(values = colors,
+                    labels = labels) +
+  # add state lines
+  geom_sf(data = state_shape, fill = NA, color = "black", size = .1) +
   coord_sf(datum = NA) +
@@
   theme(  axis.title.x=element_blank(),
-          axis.title.y=element_blank())
+          axis.title.y=element_blank(),
+          text = element_text(size = 8)) + 
+  labs(title = "Figure X:\nNet Change in Manufacturing Employment from 2004 to 2015",
+       subtitle = "Normalized by 2004 Overall Employment Levels",
+       fill = "Cumulative Change in Manufacturing\nEmployment (2004-2015) per\n2004 Worker")
 
@@
 library(data.table)
-voting <- fread("C:\\Users\\darin\\OneDrive\\Documents\\school\\MPP1 Fall Semester\\GOV 2001\\Replication File\\cd\\voting data.csv")
+voting <- fread("..\\data\\voting data.csv")
 

### 2021-11-30 rCode/Draft.Rmd

--- 2021-11-29 rCode/Draft.Rmd
@@
 
+## Findings
+
+We find that, in aggregate, manufacturing job losses are a driver of change in Democratic vote share.
+
+Breaking it down by race, we see that
+
 ```{r setup, echo=F, message = F, warning= F}
@@
 	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6))
+
+```
+
+### Geographic Concentration of Layoffs
+
+```{r,  echo=F, message = F, results = "asis"}
+
+# load map
+model_input <- readRDS("../model_5_input.rds")
+
+library(tigris)
+
+# state shapefile
+county_shape <- counties(
+  cb = TRUE,
+  resolution = "20m"
+) %>%
+  shift_geometry() %>%
+  mutate(STATEFP = as.numeric(STATEFP),
+         COUNTYFP = as.numeric(COUNTYFP))
+
+state_shape <- states(
+  cb = TRUE,
+  resolution = "20m"
+) %>%
+  filter(GEOID != "72") %>%
+  shift_geometry()
+
+# group counties into sextiles 
+model_input <- model_input %>%
+  group_by() %>%
+  mutate(ntile_mfg = as.character(ntile(mfgNetChange_total , 6)))
+
+# find cutoffs
+
+sum <- model_input %>%
+  group_by(ntile_mfg) %>%
+  summarize(min = min(mfgNetChange_total),
+            max = max(mfgNetChange_total))
+
+labels = c(
+  "1" = "1% or Greater Gain in Mfg. Emp",
+  "2" = "0% to 1% Gain in Mfg. Emp",
+  "3" = "0% to 1% Loss in Mfg. Emp",
+  "4" = "1% to 3% Loss in Mfg. Emp",
+  "5" = "3% to 6% Loss in Mfg. Emp",
+  "6" = "6% or Greater Loss in Mfg. Emp")
+
+colors <- c("1" = "#778868",
+            "2" = "#b5b991",
+            "3" = "#f6edbd",
+            "4" = "#edbb8a",
+            "5" = "#de8a5a",
+            "6" = "#ca562c")
+
+#3d5941,#778868,#b5b991,#f6edbd,#edbb8a,#de8a5a,#ca562c
+mapping_county <- inner_join(county_shape, model_input,
+                      by = c("STATEFP" = "state_fips",
+                             "COUNTYFP" = "county_fips"))
+
+ggplot() +
+  geom_sf(data = mapping_county, aes(fill = ntile_mfg), 
+          color = NA, size = .01) +
+  scale_fill_manual(values = colors,
+                    labels = labels) +
+  # add state lines
+  geom_sf(data = state_shape, fill = NA, color = "black", size = .1) +
+  coord_sf(datum = NA) +
+  theme_minimal() +
+  # geom_sf_text_repel(aes(label = state), data = mapping_small,
+  #                    force = .00001,  seed = 10,
+  #                    size = 2.5) +
+  theme(  axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          text = element_text(size = 8)) + 
+  labs(title = "Figure X:\nNet Change in Manufacturing Employment from 2004 to 2015",
+       subtitle = "Normalized by 2004 Overall Employment Levels",
+       fill = "Cumulative Change in Manufacturing\nEmployment (2004-2015) per\n2004 Worker")
 
@@
 - Mechanisms: survey work to examine where the racial difference in economic voting behavior comes from. Is it expressive? Is it because information is transmitted along racially segregated networks?
-
-## Appendix

### 2021-11-30 rCode/Draft.Rmd
moving datsets

@@
 ---
-title: '\bf Brother, can you spare a manufacturing job? White Voters\' reaction to Deindustrialization'
+title: 'bf Brother, can you spare a manufacturing job? White Voters reaction to Deindustrialization'
 author: 'Catherine Darin and Zagreb Mukerjee'
@@
 
-national_ts <- read_xlsx("../data/National_Data_TS.xlsx")
+national_ts <- read_xlsx("../National_Data_TS.xlsx")
 
@@
 library(data.table)
-voting <- fread("..\\data\\voting data.csv")
+voting <- fread("..\\voting data.csv")
 

### 2021-11-30 rCode/Draft.Rmd
small change

@@
 We find that Democratic vote share falls in counties with high manufacturing job loss since 2004.
-Disaggregating this result by race shows that the vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
+Disaggregating this result by race shows that the democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
 This suggests a racial component to how voters process economic hardship.
@@
 #devtools::install_github("yutannihilation/ggsflabel")
-library(ggsflabel)
+#library(ggsflabel)
 

### 2021-11-30 rCode/Draft.Rmd
small change

@@
 ---
-title: 'bf Brother, can you spare a manufacturing job? White Voters reaction to Deindustrialization'
+title: "Brother, can you spare a manufacturing job? White Voters' reaction to Deindustrialization"
 author: 'Catherine Darin and Zagreb Mukerjee'
@@
 
-We look at manufacturing employment (NAICS 31-33, see extensions below). Then  compute net change in mfg jobs (long term job loss) from 2004 to 2015, relative to employment in 2004.
+We look at total employment and manufacturing employment (NAICS 31-33, see extensions below).
+We then  compute net change in mfg jobs (long term job loss) from 2004 to 2015, relative to employment in 2004.
 
 We might be worried about endogeneity for manufacturing job losses.
-So we use a shift-share instrument: we predict job losses per worker with county-level manufacturing as a share of total employment, plus controls.
+So we use a shift-share instrument: we predict net job losses per worker with county-level manufacturing as a share of total employment, plus controls.
 
@@
 We want to know if there's something singular about manufacturing jobs.
+
+## Extension Relative to
 
@@
 library(scales)
+library(tigris)
+
 knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
@@
 model_input <- readRDS("../model_5_input.rds")
-
-library(tigris)
 

### 2021-11-30 rCode/Draft.Rmd
draft.rmd

--- 2021-11-30 rCode/Draft.Rmd
@@
 ---
-title: 'bf Brother, can you spare a manufacturing job? White Voters reaction to Deindustrialization'
+title: '\bf Brother, Can You Spare a Manufacturing Job? White Voter Reactions to Deindustrialization'
 author: 'Catherine Darin and Zagreb Mukerjee'
@@
 knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
+knitr::opts_chunk$set(echo = FALSE, message = FALSE)
 ```
@@
   cb = TRUE,
-  resolution = "20m"
+  resolution = "20m",
+  progress_bar = F
 ) %>%
@@
     # calculate the counterfactual change in democratic vote share
-    # by multipling our regression coefficient against the difference
+    # by multiplying our regression coefficient against the difference
     # between observed manufacturing layoffs (our measure) and the
@@
 
-#devtools::install_github("yutannihilation/ggsflabel")
+# devtools::install_github("yutannihilation/ggsflabel")
 library(ggsflabel)
@@
 
-### example state: Michigan
-
-### 2020
-
 ## Potential Future Work

### 2021-11-30 rCode/Draft.Rmd
message

@@
           digits = 2,
+          header = F,
           type = "latex"

### 2021-11-30 rCode/Draft.Rmd
add extension section

@@
 ---
-title: '\bf Brother, Can You Spare a Manufacturing Job? White Voter Reactions to Deindustrialization'
+title: "Brother, can you spare a manufacturing job? White Voters' reaction to Deindustrialization"
 author: 'Catherine Darin and Zagreb Mukerjee'
@@
 
-## Findings
+### Extension Relative to Baccini and Weymoth (2021)
+
+In their main model, Baccini and Weymouth looked at the effect on gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
+
+We believe that the correct quantity of internet is not gross manufacturing job losses, but net manufacturing job losses.
+E.g., if a county losses 400 manufacturing jobs and gain 400 manufacturing jobs in the same quarter, that should be considered a 0 net change in manufacturing employment, rather than a job loss of 400.
+
+Using net manufacturing job loss as our outcome measure, we replicate Baccini and Weymouth's main model, which uses 2012-2015 manufacturing  (gross) layoffs to explain the change in democratic 2016 vote share.
+We find totally opposite results (as shown in Table X) - that a *net* increase in white manufacturing jobs (from 2012 to 2015) *increased* democratic vote share, while a **net** increase in non-white manufacturing jobs decreased democratic vote share.
+
+However, if we expand measure of job changes to include the 2004 to 2011 period - which is when the U.S.
+manufacturing economy was hit most intensley (see figure 1) -- we get a result that is consisent with Baccini and Weymouth's overall conclusion.
+That is, that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job lossess increased Democratic vote share.
+
+But while our substantive takeway is consistent with Baccini and Weymouth's story, it is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
+Whereas Baccini and Weymouth's analyis suggests that economic changes lead to immediate political consequences, our analysis shows that economic changes can have lagged and variable effects on political outcomes.
+In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in democratic vote share in other elections (2012 and 2020).
+
+## Key Findings
 
@@
 
-# devtools::install_github("yutannihilation/ggsflabel")
-library(ggsflabel)
+#devtools::install_github("yutannihilation/ggsflabel")
+#library(ggsflabel)
 

### 2021-11-30 rCode/Draft.Rmd
add text changes

@@
 
-We believe that the correct quantity of internet is not gross manufacturing job losses, but net manufacturing job losses.
-E.g., if a county losses 400 manufacturing jobs and gain 400 manufacturing jobs in the same quarter, that should be considered a 0 net change in manufacturing employment, rather than a job loss of 400.
+Our key extension of Baccini and Weymouth's analysis is changing the quantity of interest from **gross** manufacturing job losses to **net** manufacturing job losses.
+For example, in Baccini and Weymouth's model, if a county lost 400 manufacturing jobs from 2012-2015 and also gained 400 manufacturing jobs over the same period, they would count 400 overall layoffs.
+Using our measure of *net* manufacturing job lossess, we would consider this example a 0 net change in manufacturing employment.
+Given that job descruction and creation is a natural dynamic within the economy (i.e., creative destruction), we think that *net* job lossess is a more meaningful measure.
 
-Using net manufacturing job loss as our outcome measure, we replicate Baccini and Weymouth's main model, which uses 2012-2015 manufacturing  (gross) layoffs to explain the change in democratic 2016 vote share.
-We find totally opposite results (as shown in Table X) - that a *net* increase in white manufacturing jobs (from 2012 to 2015) *increased* democratic vote share, while a **net** increase in non-white manufacturing jobs decreased democratic vote share.
+Using *net* manufacturing job losses as our outcome, we replicate Baccini and Weymouth's main model, which uses 2012-2015 manufacturing (gross) job losses to explain the change in democratic vote share in 2016.
+Using their specifications, we find totally opposite results - that a *net* increase in white manufacturing jobs *increased* democratic vote share, while a *net* increase in non-white manufacturing jobs *decreased* democratic vote share.
+(See Tavble X)
 
-However, if we expand measure of job changes to include the 2004 to 2011 period - which is when the U.S.
+However, we do not trust the result of this specification, because, from 2012 to 2015, the national economy experienced a net increase in manufacturing jobs following the 2008 recession (see Figure 1).
+During this time of recovery, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery.
+Therefore, because manufacturing job losses pre-2012 are likely negatively correlated with manufacturing job gains from 2012-2015, it is misleading to segment the analysis data to just include job losses from 2012 to 2015.
+[To DO: Empirically show negative correlation describe here]
+
+If we expand our measure of net manufacturing job losses to include the 2004 to 2011 period - which covers most of the period when the U.S.
 manufacturing economy was hit most intensley (see figure 1) -- we get a result that is consisent with Baccini and Weymouth's overall conclusion.
-That is, that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job lossess increased Democratic vote share.
+That is, we find that net white manufacturing job losses decreased democratic vote share, while net non-white manufacturing job lossess increased democratic vote share.
 
-But while our substantive takeway is consistent with Baccini and Weymouth's story, it is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
+While our main takeway is consistent with Baccini and Weymouth's story, it is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
 Whereas Baccini and Weymouth's analyis suggests that economic changes lead to immediate political consequences, our analysis shows that economic changes can have lagged and variable effects on political outcomes.
-In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in democratic vote share in other elections (2012 and 2020).
+
+[Note: to demonstrate our point about **variable** effects, In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in democratic vote share in other elections (2012 and 2020).]
 
@@
 
-We find that, in aggregate, manufacturing job losses are a driver of change in Democratic vote share.
+We find that, in aggregate, manufacturing job losses were a driver of change in Democratic vote share in the 2016 election. Breaking it down by race, we see that
 
-Breaking it down by race, we see that
+Moreover, we find that, given the evolution of the business cycle, considering only recent job losses can paint a misleading picture of the relationship between manufacturing job losses and changes in vote share.
+In fact, we find that net manufacturing job losses from 2004 to 2011 are crucial to explaning Trump's 2016 win.
+This finding suggests that economic changes, like manufacturing layoffs, can have lagged and variable political consequence.
 
@@
   geom_col() + scale_x_continuous(breaks=seq(1995,2019,2)) +
-	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6))
+	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6)) +
+  labs()
 

### 2021-11-30 rCode/Draft.Rmd
text changes

@@
 ---
-title: "Brother, can you spare a manufacturing job? White Voters' reaction to Deindustrialization"
+title: "Brother, can you spare a manufacturing job? White Voters reaction to Deindustrialization"
 author: 'Catherine Darin and Zagreb Mukerjee'
@@
 #### Framing story
+
 To do: Qualitative description of the trajectory of XYZ county that swung from O to T and suffered big manufacturing layoffs.
@@
 For example, in Baccini and Weymouth's model, if a county lost 400 manufacturing jobs from 2012-2015 and also gained 400 manufacturing jobs over the same period, they would count 400 overall layoffs.
-Using our measure of *net* manufacturing job lossess, we would consider this example a 0 net change in manufacturing employment.
-Given that job descruction and creation is a natural dynamic within the economy (i.e., creative destruction), we think that *net* job lossess is a more meaningful measure.
+Using our measure of *net* manufacturing job losses, we would consider this example a 0 net change in manufacturing employment.
+Given that job destruction and creation is a natural dynamic within the economy (i.e., creative destruction), we think that *net* job losses is a more meaningful measure.
 
@@
 Using their specifications, we find totally opposite results - that a *net* increase in white manufacturing jobs *increased* democratic vote share, while a *net* increase in non-white manufacturing jobs *decreased* democratic vote share.
-(See Tavble X)
+(See Table 3)
 
-However, we do not trust the result of this specification, because, from 2012 to 2015, the national economy experienced a net increase in manufacturing jobs following the 2008 recession (see Figure 1).
+However, we do not trust the result of this specification, because, from 2012 to 2015, the national economy experienced a net increase in manufacturing jobs following the 2008 recession (See Figure 1).
 During this time of recovery, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery.
@@
 If we expand our measure of net manufacturing job losses to include the 2004 to 2011 period - which covers most of the period when the U.S.
-manufacturing economy was hit most intensley (see figure 1) -- we get a result that is consisent with Baccini and Weymouth's overall conclusion.
-That is, we find that net white manufacturing job losses decreased democratic vote share, while net non-white manufacturing job lossess increased democratic vote share.
+manufacturing economy was hit most intensely (See figure 1) -- we get a result that is consistent with Baccini and Weymouth's overall conclusion (See Table 4).
+That is, we find that net white manufacturing job losses decreased democratic vote share, while net non-white manufacturing job losses increased democratic vote share.
 
-While our main takeway is consistent with Baccini and Weymouth's story, it is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
-Whereas Baccini and Weymouth's analyis suggests that economic changes lead to immediate political consequences, our analysis shows that economic changes can have lagged and variable effects on political outcomes.
+While our main takeaway is consistent with Baccini and Weymouth's story, it is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
+Whereas Baccini and Weymouth's analysis suggests that economic changes lead to immediate political consequences, our analysis shows that economic changes can have lagged and variable effects on political outcomes.
 
@@
 
-## Key Findings
+### Key Findings
 
@@
 Moreover, we find that, given the evolution of the business cycle, considering only recent job losses can paint a misleading picture of the relationship between manufacturing job losses and changes in vote share.
-In fact, we find that net manufacturing job losses from 2004 to 2011 are crucial to explaning Trump's 2016 win.
+In fact, we find that net manufacturing job losses from 2004 to 2011 are crucial to explaining Trump's 2016 win.
 This finding suggests that economic changes, like manufacturing layoffs, can have lagged and variable political consequence.
+
+### Potential Future Work
+
+- Temporal: Finding a better way to characterize the potentially lagged effect of manufacturing job losses on Democratic votes. Incorporating study of the 2008, 2012, 2020 elections. 
+- Disaggregation: Instead of instrumenting by manufacturing share, perhaps we can look at layoffs by industry in each county.
+While aggregate manufacturing employment may be endogenous, there's less reason to believe that specific industries would be (cf.
+Autor, Dorn and Hanson).
+This may also allow us to get further away from ecological inference problems.
+- Trend-cycle estimation: There are techniques from econometrics and other places that could potentially be used to decompose gross layoffs into seasonal and non-seasonal components. 
+- Mechanisms: survey work to examine where the racial difference in economic voting behavior comes from. Is it expressive? Is it because information is transmitted along racially segregated networks?
+
+## Tables and Figures
 
@@
 
-## Findings
+### Manufacturing Layoffs Overtime
 
@@
 ```
-
-## Potential Future Work
-
-- Temporal: Finding a better way to characterize the potentially lagged effect of manufacturing job losses on Democratic votes. Incorporating study of the 2008, 2012, 2020 elections. 
-- Disaggregation: Instead of instrumenting by manufacturing share, perhaps we can look at layoffs by industry in each county.
-While aggregate manufacturing employment may be endogeneous, there's less reason to believe that specific industries would be (cf.
-Autor, Dorn and Hanson).
-This may also allow us to get further away from ecological inference problems.
-- Trend-cycle estimation: There are techniques from econometrics and other places that could potentially be used to decompose gross layoffs into seasonal and non-seasonal components. 
-- Mechanisms: survey work to examine where the racial difference in economic voting behavior comes from. Is it expressive? Is it because information is transmitted along racially segregated networks?

### 2021-11-30 rCode/Draft.Rmd
tweaks

@@
 ---
-title: "Brother, can you spare a manufacturing job? White Voters reaction to Deindustrialization"
+title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
 author: 'Catherine Darin and Zagreb Mukerjee'
@@
 We find that Democratic vote share falls in counties with high manufacturing job loss since 2004.
-Disaggregating this result by race shows that the democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
+Disaggregating this result by race shows that the Democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
 This suggests a racial component to how voters process economic hardship.
@@
 
-To do: Qualitative description of the trajectory of XYZ county that swung from O to T and suffered big manufacturing layoffs.
+To do: Qualitative description of the trajectory of XYZ county that swung from Obama to Trump and suffered big manufacturing layoffs.
 This will establish the stakes and connect this to the broader conversation.
@@
 Why did Trump win in 2016?
-A longstanding debate about relative importance of race and economic factors.
+There is a longstanding debate about relative importance of race and economic factors.
 Complicated by the interaction of the two.
 We hope to identify the importance of manufacturing job losses, both in aggregate and for different racial groups.
+Eventually we think that people should stop asking "race or economics" when the answer is likely both.
 
@@
 
-In their main model, Baccini and Weymouth looked at the effect on gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
+In their main model, Baccini and Weymouth looked at the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
 
@@
 Using our measure of *net* manufacturing job losses, we would consider this example a 0 net change in manufacturing employment.
-Given that job destruction and creation is a natural dynamic within the economy (i.e., creative destruction), we think that *net* job losses is a more meaningful measure.
+Given that job destruction and creation is a natural dynamic within the economy (i.e.
+seasonal employment, creative destruction), we think that *net* job losses is a more meaningful measure.
 
-Using *net* manufacturing job losses as our outcome, we replicate Baccini and Weymouth's main model, which uses 2012-2015 manufacturing (gross) job losses to explain the change in democratic vote share in 2016.
-Using their specifications, we find totally opposite results - that a *net* increase in white manufacturing jobs *increased* democratic vote share, while a *net* increase in non-white manufacturing jobs *decreased* democratic vote share.
+Using *net* manufacturing job losses as our outcome, we replicate Baccini and Weymouth's main model, which uses 2012-2015 manufacturing (gross) job losses to explain the change in Democratic vote share in 2016.
+Using their specifications, we find totally opposite results - that a *net* increase in white manufacturing jobs *increased* Democratic vote share, while a *net* increase in non-white manufacturing jobs *decreased* Democratic vote share.
 (See Table 3)
 
-However, we do not trust the result of this specification, because, from 2012 to 2015, the national economy experienced a net increase in manufacturing jobs following the 2008 recession (See Figure 1).
+However, we don't think this is capturing the important dynamic at play.
+From 2012 to 2015, the national economy experienced a net increase in manufacturing jobs following the 2008 recession (See Figure 1).
 During this time of recovery, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery.
-Therefore, because manufacturing job losses pre-2012 are likely negatively correlated with manufacturing job gains from 2012-2015, it is misleading to segment the analysis data to just include job losses from 2012 to 2015.
-[To DO: Empirically show negative correlation describe here]
+Because of this v-shaped recovery, focusing only on 2012-2015 job losses/gains paints a distorted picture.
+[To DO: Empirically show negative correlation described here]
 
 If we expand our measure of net manufacturing job losses to include the 2004 to 2011 period - which covers most of the period when the U.S.
-manufacturing economy was hit most intensely (See figure 1) -- we get a result that is consistent with Baccini and Weymouth's overall conclusion (See Table 4).
-That is, we find that net white manufacturing job losses decreased democratic vote share, while net non-white manufacturing job losses increased democratic vote share.
+manufacturing economy was hit most intensely (See Figure 1) -- we get a result that corroborates the core intuition of Baccini and Weymouth (See Table 4).
+That is, we find that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased democratic vote share.
 
-While our main takeaway is consistent with Baccini and Weymouth's story, it is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
+It is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
 Whereas Baccini and Weymouth's analysis suggests that economic changes lead to immediate political consequences, our analysis shows that economic changes can have lagged and variable effects on political outcomes.
+The mechanisms of these lagged effects merit further study.
 
@@
 
-We find that, in aggregate, manufacturing job losses were a driver of change in Democratic vote share in the 2016 election. Breaking it down by race, we see that
-
-Moreover, we find that, given the evolution of the business cycle, considering only recent job losses can paint a misleading picture of the relationship between manufacturing job losses and changes in vote share.
-In fact, we find that net manufacturing job losses from 2004 to 2011 are crucial to explaining Trump's 2016 win.
-This finding suggests that economic changes, like manufacturing layoffs, can have lagged and variable political consequence.
+We find that, in aggregate, manufacturing job losses were associated with loss of Democratic vote share in the 2016 election.
+10 manufacturing job losses per worker in a county since 2004 corresponded to a 3.8 \% loss in vote share, plus or minus 3.3 \%.
+Breaking it down by race, we see that white
 
@@
 
-### Manufacturing Layoffs Overtime
+### Nationwide Manufacturing Layoffs Per Worker, 1995-2019
 
-```{r}
-# manufacturing layoffs overtime
+```{r, message = F}
+# manufacturing layoffs over time
 
@@
   dplyr::select(year, net_job_change) %>%
+  rename(Year = year, `Job Change per Worker` = net_job_change) %>% 
   mutate(
-    year = as.numeric(year),
-    net_job_change = net_job_change*4) %>% group_by()
+    Year = as.numeric(Year),
+    `Job Change per Worker` = `Job Change per Worker`*4) %>% group_by()
 
-ggplot(data = national_ts %>% filter(year >= 1995), aes(x = year, y = net_job_change)) +
+ggplot(data = national_ts %>% filter(Year >= 1995), aes(x = Year, y = `Job Change per Worker`)) +
   geom_col() + scale_x_continuous(breaks=seq(1995,2019,2)) +
@@
 
-### Example
-
 ### Regression summaries
@@
 
-rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelNetCA$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelNetC$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelWNetCA$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelWNetC$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC04A$coefficients )[rownames(regResultList$secondStageModelNetC04A$coefficients)=="firstStageModelOurs04_2$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC04$coefficients )[rownames(regResultList$secondStageModelNetC04$coefficients)=="firstStageModelOurs04_3$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04A$coefficients )[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="firstStageModelOurs04_5$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$coefficients )[rownames(regResultList$secondStageModelWNetC04$coefficients)=="firstStageModelOurs04_6$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetC04A$coefficients
+)[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$coefficients
+)[rownames(regResultList$secondStageModelWNetC04$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelNetC04A$beta )[rownames(regResultList$secondStageModelNetC04A$beta) =="firstStageModelOurs04_2$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC04$beta )[rownames(regResultList$secondStageModelNetC04$beta)=="firstStageModelOurs04_3$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="firstStageModelOurs04_5$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="firstStageModelOurs04_6$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+names(regResultList$rseNetC04A_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseNetC04_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseWNetC04A_2)[1] <- "White Manufacturing Layoffs"
+names(regResultList$rseWNetC04_2)[1] <- "White Manufacturing Layoffs"
+
+names(regResultList$rseWNetC04A_2)[names(regResultList$rseWNetC04A_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+names(regResultList$rseWNetC04_2)[names(regResultList$rseWNetC04_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+
+stargazer(regResultList$secondStageModelNetC04A,
+          regResultList$secondStageModelNetC04,
+          regResultList$secondStageModelWNetC04A,
+          regResultList$secondStageModelWNetC04,
+          se = list(
+            regResultList$rseNetC04A_2,
+            regResultList$rseNetC04_2,
+            regResultList$rseWNetC04A_2,
+            regResultList$rseWNetC04_2
+          ),
+          title = "Effect of Manufacturing Layoffs on Democratic Vote Share (since 2004)",
+          dep.var.labels = "Change in Share (2016-2012)",
+          omit.stat = c("rsq","ser"),
+          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
+          add.lines = list(
+            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
+          ),
+          digits = 2,
+          header = F,
+          type = "latex"
+)
+
+```
+
+```{r,  echo=F, message = F, results = "asis"}
+
+rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"
 
@@
 
-rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelNetCA$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelNetC$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelWNetCA$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelWNetC$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"
 
@@
           dep.var.labels = "Change in Share (2012-2016)",
-          omit.stat = c("rsq","ser"),
-          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
-          add.lines = list(
-            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
-          ),
-          digits = 2,
-          header = F,
-          type = "latex"
-)
-
-```
-
-```{r,  echo=F, message = F, results = "asis"}
-
-rownames(regResultList$secondStageModelNetC04A$coefficients )[rownames(regResultList$secondStageModelNetC04A$coefficients)=="firstStageModelNetC04A$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC04$coefficients )[rownames(regResultList$secondStageModelNetC04$coefficients)=="firstStageModelNetC04$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04A$coefficients )[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="firstStageModelWNetC04A$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$coefficients )[rownames(regResultList$secondStageModelWNetC04$coefficients)=="firstStageModelWNetC04$fitted.values"] <-  "White Manufacturing Layoffs"
-
-rownames(regResultList$secondStageModelWNetC04A$coefficients
-)[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$coefficients
-)[rownames(regResultList$secondStageModelWNetC04$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-
-rownames(regResultList$secondStageModelNetC04A$beta )[rownames(regResultList$secondStageModelNetC04A$beta) =="firstStageModelNetC04A$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC04$beta )[rownames(regResultList$secondStageModelNetC04$beta)=="firstStageModelNetC04$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="firstStageModelWNetC04A$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="firstStageModelWNetC04$fitted.values"] <-  "White Manufacturing Layoffs"
-
-rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-
-names(regResultList$rseNetC04A_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseNetC04_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseWNetC04A_2)[1] <- "White Manufacturing Layoffs"
-names(regResultList$rseWNetC04_2)[1] <- "White Manufacturing Layoffs"
-
-names(regResultList$rseWNetC04A_2)[names(regResultList$rseWNetC04A_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
-names(regResultList$rseWNetC04_2)[names(regResultList$rseWNetC04_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
-
-stargazer(regResultList$secondStageModelNetC04A,
-          regResultList$secondStageModelNetC04,
-          regResultList$secondStageModelWNetC04A,
-          regResultList$secondStageModelWNetC04,
-          se = list(
-            regResultList$rseNetC04A_2,
-            regResultList$rseNetC04_2,
-            regResultList$rseWNetC04A_2,
-            regResultList$rseWNetC04_2
-          ),
-          title = "Effect of Manufacturing Layoffs on Democratic Vote Share (since 2004)",
-          dep.var.labels = "Change in Share (2016-2012)",
           omit.stat = c("rsq","ser"),

### 2021-11-30 rCode/Draft.Rmd
more minor changes

--- 2021-11-30 rCode/Draft.Rmd
@@
 
-We find that, in aggregate, manufacturing job losses were a driver of change in Democratic vote share in the 2016 election. Breaking it down by race, we see that
+We find that, in aggregate, manufacturing job losses were a driver of change in Democratic vote share in the 2016 election.
+Breaking it down by race, we see that [TO DO: complete thought].
+Using our main results from regression 3 in Table 4, we simulate a counterfactual scenario to demonstrate the practical signifcance of our estimates.
+Specifically, we generate a counterfactual democratic vote share assuming that all counties experienced manufacturing job losses equivalent to the county at the 25th national percentile.
+In Figure 3, we show the difference between the counterfactual democratic vote share and the model-predicted democratic vote share.
+We highlight states in purple if the difference between the counterfactual and model-predicted democratic vote shares exceeded Trump's vote share margin.
+Figure 3 shows that the effect sizes from our analysis suggest that, but for manufacturing layoffs from 2004-2015, Trump may not have one the 2016 presidential election.
 
-Moreover, we find that, given the evolution of the business cycle, considering only recent job losses can paint a misleading picture of the relationship between manufacturing job losses and changes in vote share.
+Additionally, we find that, given the evolution of the business cycle, considering only recent job losses can paint a misleading picture of the relationship between manufacturing job losses and changes in vote share.
 In fact, we find that net manufacturing job losses from 2004 to 2011 are crucial to explaining Trump's 2016 win.
@@
 
-### Manufacturing Layoffs Overtime
+### 1. Figure 1: Manufacturing Layoffs Over Time
 
@@
     # 25th percentile of layoffs (nationally)
+
+    # counterfactual net change in manufacturing job losses     
     CF_netchange = p25,
+
+    # difference between counterfactual and actual net manufacturing job losses 
     CF_d_netchange = CF_netchange - mfgNetChange_white,
+
+    # effect size -> coeff on white manufacturing layoffs times by the dif between CF and actual
     CF_ddem_change = CF_d_netchange*model_results$coefficients[1],
+
+    # counterfactual predicted dem vote share
+
     P_ddem_2 = P_ddem_1 + CF_ddem_change) %>%
+
   dplyr::select(id, state_fips, state, state_name, county_fips,
@@
 model_input <- model_input %>%
-  mutate(CF_dem_votes = dem_votes +
-           CF_ddem_change*total_dem_rep_votes,
+  mutate(
+    CF_dem_votes = dem_votes + CF_ddem_change*total_dem_rep_votes,
     CF_rep_votes = rep_votes - CF_ddem_change*total_dem_rep_votes)
@@
 order = c(
-  #"+2% or greater", "+1% to +2%",
+  "+2% or greater", 
+  "+1% to +2%",
           "+0.5% to +1%",
@@
 state_summary <- model_input %>%
-  group_by(state_name, state) %>%
+  group_by(state) %>%
   summarize(actual_trump_votes = sum(rep_votes),
@@
   mutate(
-    delta_vs = case_when(delta_vs < -.02 ~ "+2% or greater",
+    delta_vs_group = case_when(delta_vs < -.02 ~ "+2% or greater",
                          delta_vs < -.01 ~ "+1% to +2%",
@@
                          TRUE ~ "-1% or greater")) %>%
-  mutate(delta_vs_group = factor(delta_vs, levels = order))
+  mutate(delta_vs_group = factor(delta_vs_group, levels = order))
 
@@
    c(
-     #"+2% or greater" = "#0059ff",
-     #"+1% to +2%" = "#4988fc",
+     "+2% or greater" = "#0059ff",
+     "+1% to +2%" = "#4988fc",
      "+0.5% to +1%" = "#86b0fc",
@@
      "0% to -0.25%" = "#ffeae8")
-
-# map change in trump vote share
-library(tigris)
 
@@
 mapping <- inner_join(state_shape, state_summary,
-                      by = c("NAME" = "state_name"))
+                      by = c("STUSPS" = "state"))
 
-#devtools::install_github("yutannihilation/ggsflabel")
-#library(ggsflabel)
-
-mapping_small <- mapping %>% filter(state != "DC")
+mapping_small <- mapping #%>% filter(state != "DC")
 
@@
 
-#  alt
+#  make map
 flipped <- mapping_small %>% filter(changed_outcome == "Yes")

### 2021-11-30 rCode/Draft.Rmd

--- 2021-11-30 rCode/Draft.Rmd
@@
 
+We find that, in aggregate, manufacturing job losses were a driver of change in Democratic vote share in the 2016 election.
+Breaking it down by race, we see that [TO DO: complete thought].
+Using our main results from regression 3 in Table 4, we simulate a counterfactual scenario to demonstrate the practical signifcance of our estimates.
+Specifically, we generate a counterfactual democratic vote share assuming that all counties experienced manufacturing job losses equivalent to the county at the 25th national percentile.
+In Figure 3, we show the difference between the counterfactual democratic vote share and the model-predicted democratic vote share.
+We highlight states in purple if the difference between the counterfactual and model-predicted democratic vote shares exceeded Trump's vote share margin.
+Figure 3 shows that the effect sizes from our analysis suggest that, but for manufacturing layoffs from 2004-2015, Trump may not have one the 2016 presidential election.
+
+Additionally, we find that, given the evolution of the business cycle, considering only recent job losses can paint a misleading picture of the relationship between manufacturing job losses and changes in vote share.
+In fact, we find that net manufacturing job losses from 2004 to 2011 are crucial to explaining Trump's 2016 win.
+This finding suggests that economic changes, like manufacturing layoffs, can have lagged and variable political consequence.
+
 We find that, in aggregate, manufacturing job losses were associated with loss of Democratic vote share in the 2016 election.
@@
 ```
+
+### 1. Figure 1: Manufacturing Layoffs Over Time
 

### 2021-11-30 rCode/Draft.Rmd
last updates

@@
 
-### 1. Figure 1: Manufacturing Layoffs Over Time
-
-### Nationwide Manufacturing Layoffs Per Worker, 1995-2019
+### Manufacturing Layoffs Over Time
 
@@
 
-ggplot(data = national_ts %>% filter(Year >= 1995), aes(x = Year, y = `Job Change per Worker`)) +
-  geom_col() + scale_x_continuous(breaks=seq(1995,2019,2)) +
+ggplot(data = national_ts %>% filter(Year >= 1995), 
+       aes(x = Year, y = `Job Change per Worker`)) +
+  ylab("Millions of Jobs") +
+  ggtitle("Figure 1. Nationwide Change in Manufacturing Employment, 1995-2019") +
+  geom_col(fill = "#4287f5") + scale_x_continuous(breaks=seq(1995,2019,2)) +
 	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6)) +
-  labs()
+  theme_minimal()
 
@@
 
+\newpage
 ### Geographic Concentration of Layoffs
@@
 ) %>%
-  filter(GEOID != "72") %>%
-  shift_geometry()
+  filter(GEOID != "72" & GEOID != "02", GEOID != "15")
 
@@
 labels = c(
-  "1" = "1% or Greater Gain in Mfg. Emp",
-  "2" = "0% to 1% Gain in Mfg. Emp",
-  "3" = "0% to 1% Loss in Mfg. Emp",
-  "4" = "1% to 3% Loss in Mfg. Emp",
-  "5" = "3% to 6% Loss in Mfg. Emp",
-  "6" = "6% or Greater Loss in Mfg. Emp")
+  "1" = "1% or Greater Gain",
+  "2" = "0% to 1% Gain",
+  "3" = "0% to 1% Loss",
+  "4" = "1% to 3% Loss",
+  "5" = "3% to 6% Loss",
+  "6" = "6% or Greater Loss")
 
@@
           text = element_text(size = 8)) + 
-  labs(title = "Figure X:\nNet Change in Manufacturing Employment from 2004 to 2015",
+  labs(title = "Figure 2: Net Change in Manufacturing Employment from 2004 to 2015",
        subtitle = "Normalized by 2004 Overall Employment Levels",
@@
 
+\newpage
 ### Descriptive Statistics
@@
 
-## Figures
-
-### Regression summaries
+\newpage
+### Regression Results (Using 2004-2015 Net Manu Job Change)
 
@@
 
+\newpage
+### Regression Results (Using 2012-2015 Net Manu Job Change)
+
 ```{r,  echo=F, message = F, results = "asis"}
@@
 
-### Counterfactual assessment of election
-## (Using 2004-2015 Layoffs)
+\newpage
+### Counterfactual assessment of election (Using 2004-2015 Layoffs)
 
-```{r,  echo=F, message = F, results = "asis"}
+```{r,  echo=F, message = F}
 
@@
 order = c(
-  "+2% or greater", 
-  "+1% to +2%",
+ # "+2% or greater", 
+  #"+1% to +2%",
           "+0.5% to +1%",
@@
    c(
-     "+2% or greater" = "#0059ff",
-     "+1% to +2%" = "#4988fc",
+    # "+2% or greater" = "#0059ff",
+     #"+1% to +2%" = "#4988fc",
      "+0.5% to +1%" = "#86b0fc",
@@
 ggplot() +
-  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "grey", size = .01) +
+  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "black", size = .1) +
   scale_fill_manual(values = colors) +
-  labs(title = "Figure X:\nWithout Manufacturing Layoffs, Democrats Would Have Won 2016 Election",
-       subtitle = "Change in Democratic Vote Share Assuming Counterfactual Manufacturing Layoffs (25th Percentile)",
+  labs(title = "Figure 3: Impact of Manufacturing Job Lossess on Democratic Vote Share",
+       subtitle = "Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses",
        fill = "Change in Democratic Vote Share") +
-  geom_sf(data = flipped, fill = NA, aes(color = changed_outcome), size = 1) +
+  geom_sf(data = flipped, fill = NA, 
+          aes(color = changed_outcome), 
+          size = 1) +
   scale_color_manual(values = "#b32ab5", name = "Flipped Election") +

### 2021-11-30 rCode/Draft.Rmd
tiny tweaks

@@
 
-### Extension Relative to Baccini and Weymoth (2021)
+### Extension Relative to Baccini and Weymouth (2021)
 
@@
 manufacturing economy was hit most intensely (See Figure 1) -- we get a result that corroborates the core intuition of Baccini and Weymouth (See Table 4).
-That is, we find that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased democratic vote share.
+That is, we find that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased Democratic vote share.
 
@@
 
-[Note: to demonstrate our point about **variable** effects, In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in democratic vote share in other elections (2012 and 2020).]
+[Note: to demonstrate our point about **variable** effects, In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in Democratic vote share in other elections (2012 and 2020).]
 
@@
 
-We find that, in aggregate, manufacturing job losses were a driver of change in Democratic vote share in the 2016 election.
+We find that, in aggregate, manufacturing job losses were associated with loss of Democratic vote share in the 2016 election.
+10 manufacturing job losses per worker in a county since 2004 corresponded to a 3.8 \% loss in vote share, plus or minus 3.3 \%.
 Breaking it down by race, we see that [TO DO: complete thought].
-Using our main results from regression 3 in Table 4, we simulate a counterfactual scenario to demonstrate the practical signifcance of our estimates.
-Specifically, we generate a counterfactual democratic vote share assuming that all counties experienced manufacturing job losses equivalent to the county at the 25th national percentile.
-In Figure 3, we show the difference between the counterfactual democratic vote share and the model-predicted democratic vote share.
-We highlight states in purple if the difference between the counterfactual and model-predicted democratic vote shares exceeded Trump's vote share margin.
-Figure 3 shows that the effect sizes from our analysis suggest that, but for manufacturing layoffs from 2004-2015, Trump may not have one the 2016 presidential election.
+
+Figure 3 demonstrates the practical significance of our estimates.
+Using our main results from regression 3 in Table 4, we simulate a counterfactual 2016 election assuming that all counties experienced white manufacturing job losses equivalent to the county at the 25th national percentile.
+We highlight states in purple if this counterfactual shows a state flipping from Trump to Clinton.
 
@@
 This finding suggests that economic changes, like manufacturing layoffs, can have lagged and variable political consequence.
-
-We find that, in aggregate, manufacturing job losses were associated with loss of Democratic vote share in the 2016 election.
-10 manufacturing job losses per worker in a county since 2004 corresponded to a 3.8 \% loss in vote share, plus or minus 3.3 \%.
-Breaking it down by race, we see that white
 

### 2021-12-03 rCode/fipsCodeLabel.R
Modifications to make code run.

@@ -8,7 +8,7 @@
 # maybe they omit bedford city because their list is post 2013
 
 
-countyLevelRaw <- read_dta("OriginalMaterials/county_level.dta")
+countyLevelRaw <- read_dta(here::here("OriginalMaterials/county_level.dta"))
 
 
 allFIPS <- tidycensus::fips_codes %>%  tibble() %>% 
@@ -41,7 +41,7 @@ countyLevel <- countyLevel0 %>%  left_join(allFIPSBW %>%  dplyr::select(id, coun
 # these are missing in BW as well
 
 
-saveRDS(countyLevel, "data/BWCountyLevel.rds")
+saveRDS(countyLevel, here::here("data/BWCountyLevel.rds"))
 
 
 

### 2021-12-03 rCode/replicateBartikInstrument.R

@@ -1,7 +1,7 @@
 
 ################################################################
-countyLevelData <- readRDS("data/censusDataByCounty.rds")
-natlResult <- readRDS("data/natlResult.rds") 
+countyLevelData <- readRDS(here::here("data/censusDataByCounty.rds"))
+natlResult <- readRDS(here::here("data/natlResult.rds"))
 ################################################################
 
 aggregate <- totalData %>%  left_join(mfgData) %>%

### 2021-12-09 Final Draft/Final-Draft.tex

% AER-Article.tex for AEA last revised 22 June 2011
\documentclass[AER]{AEA}

% The mathtime package uses a Times font instead of Computer Modern.
% Uncomment the line below if you wish to use the mathtime package:
%\usepackage[cmbold]{mathtime}
% Note that miktex, by default, configures the mathtime package to use commercial fonts
% which you may not have. If you would like to use mathtime but you are seeing error
% messages about missing fonts (mtex.pfb, mtsy.pfb, or rmtmi.pfb) then please see
% the technical support document at http://www.aeaweb.org/templates/technical_support.pdf
% for instructions on fixing this problem.

% Note: you may use either harvard or natbib (but not both) to provide a wider
% variety of citation commands than latex supports natively. See below.

% Uncomment the next line to use the natbib package with bibtex
\usepackage{natbib}

% Uncomment the next line to use the harvard package with bibtex
%\usepackage[abbr]{harvard}

% This command determines the leading (vertical space between lines) in draft mode
% with 1.5 corresponding to "double" spacing.
\draftSpacing{1.5}

% For Pandoc highlighting needs

% Pandoc citation processing

\usepackage{hyperref}

\begin{document}

\title{Untitled}
\shortTitle{A shorter title}
% \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
% Surname2: affiliation2, address2, email2. Acknowledgements}}

\author{
  Alice Anonymous\\
  Bob Security\thanks{
  Anonymous: Some Institute of Technology, \href{mailto:alice@example.com}{alice@example.com}.
  Security: Another University, \href{mailto:bob@example.com}{bob@example.com}.
  Acknowledgements
}
}

\date{\today}
\pubMonth{12}
\pubYear{2021}
\pubVolume{1}
\pubIssue{1}
\JEL{A10, A11}
\Keywords{first keyword, second keyword}

\begin{abstract}
Abstract goes here
\end{abstract}

\maketitle

American Economic Review Pointers:

\begin{itemize}
\item Do not use an "Introduction" heading. Begin your introductory material
before the first section heading.

\item Avoid style markup (except sparingly for emphasis).

\item Avoid using explicit vertical or horizontal space.

\item Captions are short and go below figures but above tables.

\item The tablenotes or figurenotes environments may be used below tables
or figures, respectively, as demonstrated below.

\item If you have difficulties with the mathtime package, adjust the package
options appropriately for your platform. If you can't get it to work, just
remove the package or see our technical support document online (please
refer to the author instructions).

\item If you are using an appendix, it goes last, after the bibliography.
Use regular section headings to make the appendix headings.

\item If you are not using an appendix, you may delete the appendix command
and sample appendix section heading.

\item Either the natbib package or the harvard package may be used with bibtex.
To include one of these packages, uncomment the appropriate usepackage command
above. Note: you can't use both packages at once or compile-time errors will result.

\end{itemize}

\section{First Section in Body}

Sample figure:

\begin{figure}
Figure here.

\caption{Caption for figure below.}
\begin{figurenotes}
Figure notes without optional leadin.
\end{figurenotes}
\begin{figurenotes}[Source]
Figure notes with optional leadin (Source, in this case).
\end{figurenotes}
\end{figure}

Sample table:

\begin{table}
\caption{Caption for table above.}

\begin{tabular}{lll}
& Heading 1 & Heading 2 \\
Row 1 & 1 & 2 \\
Row 2 & 3 & 4%
\end{tabular}
\begin{tablenotes}
Table notes environment without optional leadin.
\end{tablenotes}
\begin{tablenotes}[Source]
Table notes environment with optional leadin (Source, in this case).
\end{tablenotes}
\end{table}

References here (manual or bibTeX). If you are using bibTeX, add your
bib file name in place of BibFile in the bibliography command. \% Remove
or comment out the next two lines if you are not using bibtex.

\bibliographystyle{aea}
\bibliography{references}

\% The appendix command is issued once, prior to all appendices, if any.
\appendix

\section{Mathematical Appendix}

\end{document}

### 2021-12-09 rCode/Draft v2.Rmd

--- 2021-11-30 rCode/Draft.Rmd
@@
 ---
-
 \renewcommand{\arraystretch}{1.1}
@@
 \setcounter{totalnumber}{4}
+
+## Replication Instructions
+
+Please find instructions and relevant code to replicate our analysis here: https://github.com/zagrebmukerjee/ReplicationPaper
 
@@
 
+### 04 to 15
+
 ```{r,  echo=F, message = F, results = "asis"}
@@
        fill = "Cumulative Change in Manufacturing\nEmployment (2004-2015) per\n2004 Worker")
+
+```
+
+\newpage
+
+### 12 to 15
+
+```{r,  echo=F, message = F, results = "asis"}
+
+# load map
+model_input <- readRDS("../input_12_16.rds")
+
+# state shapefile
+county_shape <- counties(
+  cb = TRUE,
+  resolution = "20m",
+  progress_bar = F
+) %>%
+  shift_geometry() %>%
+  mutate(STATEFP = as.numeric(STATEFP),
+         COUNTYFP = as.numeric(COUNTYFP))
+
+state_shape <- states(
+  cb = TRUE,
+  resolution = "20m",
+  progress_bar = F
+) %>%
+  filter(GEOID != "72" & GEOID != "02", GEOID != "15")
+
+# group counties into sextiles
+model_input <- model_input %>%
+  group_by() %>%
+  mutate(ntile_mfg = as.character(ntile(mfgNetChange_total , 6)))
+
+# find cutoffs
+
+sum <- model_input %>%
+  group_by(ntile_mfg) %>%
+  summarize(min = min(mfgNetChange_total),
+            max = max(mfgNetChange_total))
+
+labels = c(
+  "1" = "1% or Greater Gain",
+  "2" = "0% to 1% Gain",
+  "3" = "0% to 1% Loss",
+  "4" = "1% to 3% Loss",
+  "5" = "3% to 6% Loss",
+  "6" = "6% or Greater Loss")
+
+colors <- c("1" = "#778868",
+            "2" = "#b5b991",
+            "3" = "#f6edbd",
+            "4" = "#edbb8a",
+            "5" = "#de8a5a",
+            "6" = "#ca562c")
+
+#3d5941,#778868,#b5b991,#f6edbd,#edbb8a,#de8a5a,#ca562c
+mapping_county <- inner_join(county_shape, model_input,
+                      by = c("STATEFP" = "state_fips",
+                             "COUNTYFP" = "county_fips"))
+
+ggplot() +
+  geom_sf(data = mapping_county, aes(fill = ntile_mfg),
+          color = NA, size = .01) +
+  scale_fill_manual(values = colors,
+                    labels = labels) +
+  # add state lines
+  geom_sf(data = state_shape, fill = NA, color = "black", size = .1) +
+  coord_sf(datum = NA) +
+  theme_minimal() +
+  # geom_sf_text_repel(aes(label = state), data = mapping_small,
+  #                    force = .00001,  seed = 10,
+  #                    size = 2.5) +
+  theme(  axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          text = element_text(size = 8)) +
+  labs(title = "Figure 2: Net Change in Manufacturing Employment from 2012 to 2015",
+       subtitle = "Normalized by 2011 Overall Employment Levels",
+       fill = "Cumulative Change in Manufacturing\nEmployment (2012-2015) per\n2011 Worker")
 
@@
 p25 <- quantile(model_input$mfgNetChange_white, (.25))
-
-# find the predicted democratic vote share
-model_input$P_ddem_1 <- model_results$fitted.values
 

### 2021-12-09 rCode/Draft.Rmd
add link

@@
 \setcounter{totalnumber}{4}
+
+# ```{r, include=FALSE}
+# options(tinytex.verbose = TRUE)
+# ```
+
+## Replication Instructions
+
+Please find instructions and relevant code to replicate our analysis here: https://github.com/zagrebmukerjee/ReplicationPaper
 

### 2021-12-09 rCode/Draft.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Brother, Can You Spare a Manufacturing Job? How Voters React to Deindustrialization},
  pdfauthor={Catherine Darin and Zagreb Mukerjee},
  colorlinks=true,
  linkcolor=Maroon,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=red,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{bm}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Brother, Can You Spare a Manufacturing Job? How Voters React to
Deindustrialization}
\author{Catherine Darin and Zagreb Mukerjee}
\date{11/29/2021}

\begin{document}
\maketitle

\renewcommand{\arraystretch}{1.1}
\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{3}
\setcounter{totalnumber}{4}

\hypertarget{r-includefalse-optionstinytex.verbose-true}{%
\section{\texorpdfstring{\texttt{\{r,\ include=FALSE\}\ \#\ options(tinytex.verbose\ =\ TRUE)\ \#}}{\{r, include=FALSE\} \# options(tinytex.verbose = TRUE) \#}}\label{r-includefalse-optionstinytex.verbose-true}}

\hypertarget{replication-instructions}{%
\subsection{Replication Instructions}\label{replication-instructions}}

Please find instructions and relevant code to replicate our analysis
here: \url{https://github.com/zagrebmukerjee/ReplicationPaper}

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

What led to Donald Trump's surprising 2016 election victory? This paper
examines the potential contribution of deindustrialization. Counties
differ by exposure to manufacturing, which we use in an
instrumental-variable approach to identify the effect of manufacturing
job loss on change in Democratic vote share. We find that Democratic
vote share falls in counties with high manufacturing job loss since
2004. Disaggregating this result by race shows that the Democratic vote
share fell where layoffs affected white populations, and rose where
layoffs affected nonwhites. This suggests a racial component to how
voters process economic hardship.

Base paper: Baccini and Weymouth 2021, ``Gone For Good:
Deindustrialization, White Voter Backlash, and US Presidential Voting.''
\emph{APSR}.

\hypertarget{outline}{%
\subsection{Outline}\label{outline}}

\hypertarget{framing-story}{%
\paragraph{Framing story}\label{framing-story}}

To do: Qualitative description of the trajectory of XYZ county that
swung from Obama to Trump and suffered big manufacturing layoffs. This
will establish the stakes and connect this to the broader conversation.

\hypertarget{substantive-importance}{%
\subsubsection{Substantive importance}\label{substantive-importance}}

Why did Trump win in 2016? There is a longstanding debate about relative
importance of race and economic factors. Complicated by the interaction
of the two. We hope to identify the importance of manufacturing job
losses, both in aggregate and for different racial groups. Eventually we
think that people should stop asking ``race or economics'' when the
answer is likely both.

\hypertarget{empirical-strategy}{%
\subsubsection{Empirical strategy}\label{empirical-strategy}}

Differential manufacturing exposure across counties allows for
identification of the causal effect of deindustrialization on change in
Dem vote share. Further differences in racial exposure to mfg layoffs
allows for identification of the interaction between race and
deindustrialization.

\hypertarget{data-and-methods}{%
\subsubsection{Data and methods}\label{data-and-methods}}

Data is Census Quarterly Workforce Indicators, which break down county
employment by industry, race and ethnicity. Augmented with public data
on vote shares, employment, etc.

We look at total employment and manufacturing employment (NAICS 31-33,
see extensions below). We then compute net change in mfg jobs (long term
job loss) from 2004 to 2015, relative to employment in 2004.

We might be worried about endogeneity for manufacturing job losses. So
we use a shift-share instrument: we predict net job losses per worker
with county-level manufacturing as a share of total employment, plus
controls.

Controls: unemployment in 2015, college educated share of population,
male share of population, layoffs in service sector, white share of
population (to control for demographic trends). We want to know if
there's something singular about manufacturing jobs.

\hypertarget{extension-relative-to-baccini-and-weymouth-2021}{%
\subsubsection{Extension Relative to Baccini and Weymouth
(2021)}\label{extension-relative-to-baccini-and-weymouth-2021}}

In their main model, Baccini and Weymouth looked at the effect of gross
manufacturing job losses from 2012 to 2015 on the change in Democratic
vote share in the 2016 presidential election.

Our key extension of Baccini and Weymouth's analysis is changing the
quantity of interest from \textbf{gross} manufacturing job losses to
\textbf{net} manufacturing job losses. For example, in Baccini and
Weymouth's model, if a county lost 400 manufacturing jobs from 2012-2015
and also gained 400 manufacturing jobs over the same period, they would
count 400 overall layoffs. Using our measure of \emph{net} manufacturing
job losses, we would consider this example a 0 net change in
manufacturing employment. Given that job destruction and creation is a
natural dynamic within the economy (i.e.~seasonal employment, creative
destruction), we think that \emph{net} job losses is a more meaningful
measure.

Using \emph{net} manufacturing job losses as our outcome, we replicate
Baccini and Weymouth's main model, which uses 2012-2015 manufacturing
(gross) job losses to explain the change in Democratic vote share in
2016. Using their specifications, we find totally opposite results -
that a \emph{net} increase in white manufacturing jobs \emph{increased}
Democratic vote share, while a \emph{net} increase in non-white
manufacturing jobs \emph{decreased} Democratic vote share. (See Table 3)

However, we don't think this is capturing the important dynamic at play.
From 2012 to 2015, the national economy experienced a net increase in
manufacturing jobs following the 2008 recession (See Figure 1). During
this time of recovery, counties that experienced the most pronounced
manufacturing job losses in prior years were also likely to experience
the most pronounced recovery. Because of this v-shaped recovery,
focusing only on 2012-2015 job losses/gains paints a distorted picture.
{[}To DO: Empirically show negative correlation described here{]}

If we expand our measure of net manufacturing job losses to include the
2004 to 2011 period - which covers most of the period when the U.S.
manufacturing economy was hit most intensely (See Figure 1) -- we get a
result that corroborates the core intuition of Baccini and Weymouth (See
Table 4). That is, we find that net white manufacturing job losses
decreased Democratic vote share, while net non-white manufacturing job
losses increased Democratic vote share.

It is important to highlight the substantive importance of the
\emph{timing} of manufacturing layoffs on political outcomes. Whereas
Baccini and Weymouth's analysis suggests that economic changes lead to
immediate political consequences, our analysis shows that economic
changes can have lagged and variable effects on political outcomes. The
mechanisms of these lagged effects merit further study.

{[}Note: to demonstrate our point about \textbf{variable} effects, In
our next iteration of the analysis, we will show that manufacturing job
losses had little explanatory effect on changes in Democratic vote share
in other elections (2012 and 2020).{]}

\hypertarget{key-findings}{%
\subsubsection{Key Findings}\label{key-findings}}

We find that, in aggregate, manufacturing job losses were associated
with loss of Democratic vote share in the 2016 election. 10
manufacturing job losses per worker in a county since 2004 corresponded
to a 3.8 \% loss in vote share, plus or minus 3.3 \%. Breaking it down
by race, we see that {[}TO DO: complete thought{]}.

Figure 3 demonstrates the practical significance of our estimates. Using
our main results from regression 3 in Table 4, we simulate a
counterfactual 2016 election assuming that all counties experienced
white manufacturing job losses equivalent to the county at the 25th
national percentile. We highlight states in purple if this
counterfactual shows a state flipping from Trump to Clinton.

Additionally, we find that, given the evolution of the business cycle,
considering only recent job losses can paint a misleading picture of the
relationship between manufacturing job losses and changes in vote share.
In fact, we find that net manufacturing job losses from 2004 to 2011 are
crucial to explaining Trump's 2016 win. This finding suggests that
economic changes, like manufacturing layoffs, can have lagged and
variable political consequence.

\hypertarget{potential-future-work}{%
\subsubsection{Potential Future Work}\label{potential-future-work}}

\begin{itemize}
\tightlist
\item
  Temporal: Finding a better way to characterize the potentially lagged
  effect of manufacturing job losses on Democratic votes. Incorporating
  study of the 2008, 2012, 2020 elections.
\item
  Disaggregation: Instead of instrumenting by manufacturing share,
  perhaps we can look at layoffs by industry in each county. While
  aggregate manufacturing employment may be endogenous, there's less
  reason to believe that specific industries would be (cf.~Autor, Dorn
  and Hanson). This may also allow us to get further away from
  ecological inference problems.
\item
  Trend-cycle estimation: There are techniques from econometrics and
  other places that could potentially be used to decompose gross layoffs
  into seasonal and non-seasonal components.
\item
  Mechanisms: survey work to examine where the racial difference in
  economic voting behavior comes from. Is it expressive? Is it because
  information is transmitted along racially segregated networks?
\end{itemize}

\hypertarget{tables-and-figures}{%
\subsection{Tables and Figures}\label{tables-and-figures}}

\hypertarget{manufacturing-layoffs-over-time}{%
\subsubsection{Manufacturing Layoffs Over
Time}\label{manufacturing-layoffs-over-time}}

\begin{verbatim}
## Warning: Removed 2 rows containing missing values (position_stack).
\end{verbatim}

\includegraphics{Draft_files/figure-latex/unnamed-chunk-1-1}

\newpage

\hypertarget{geographic-concentration-of-layoffs}{%
\subsubsection{Geographic Concentration of
Layoffs}\label{geographic-concentration-of-layoffs}}

\hypertarget{to-15}{%
\subsubsection{04 to 15}\label{to-15}}

\includegraphics{Draft_files/figure-latex/unnamed-chunk-2-1}

\newpage

\hypertarget{to-15-1}{%
\subsubsection{12 to 15}\label{to-15-1}}

\includegraphics{Draft_files/figure-latex/unnamed-chunk-3-1}

\newpage

\hypertarget{descriptive-statistics}{%
\subsubsection{Descriptive Statistics}\label{descriptive-statistics}}

\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-4}Manufacturing Job Changes 2004-2015}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrr}
\toprule
  & Mean & Std Dev & 25th Pctile & Median & 75th Pctile\\
\midrule
Mfg Share of Emp & 0.20 & 0.15 & 0.09 & 0.17 & 0.29\\
Mfg Share of Emp (White) & 0.16 & 0.13 & 0.06 & 0.13 & 0.22\\
Mfg Share of Emp (Nonwhite) & 0.05 & 0.07 & 0.01 & 0.02 & 0.06\\
Change in Mfg Jobs/ Worker & 0.04 & 0.09 & -0.01 & 0.02 & 0.06\\
Change in Mfg Jobs/ Worker (W) & 0.03 & 0.07 & 0.00 & 0.02 & 0.06\\
\addlinespace
Change in Mfg Jobs/ Worker (NW) & 0.00 & 0.04 & -0.01 & 0.00 & 0.01\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-4}Manufacturing Job Changes 2012-2015}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrr}
\toprule
  & Mean & Std Dev & 25th Pctile & Median & 75th Pctile\\
\midrule
Change in Dem Vote Share & -0.06 & 0.05 & -0.10 & -0.05 & -0.03\\
Mfg Share of Emp & 0.20 & 0.16 & 0.08 & 0.16 & 0.28\\
Mfg Share of Emp (White) & 0.15 & 0.13 & 0.06 & 0.12 & 0.22\\
Mfg Share of Emp (Nonwhite) & 0.05 & 0.07 & 0.01 & 0.03 & 0.06\\
Change in Mfg Jobs/ Worker & -0.01 & 0.05 & -0.02 & 0.00 & 0.01\\
\addlinespace
Change in Mfg Jobs/ Worker (W) & 0.00 & 0.03 & -0.01 & 0.00 & 0.01\\
Change in Mfg Jobs/ Worker (NW) & 0.00 & 0.02 & -0.01 & 0.00 & 0.00\\
\bottomrule
\end{tabular}}
\end{table}

\newpage

\hypertarget{regression-results-using-2004-2015-net-manu-job-change}{%
\subsubsection{Regression Results (Using 2004-2015 Net Manu Job
Change)}\label{regression-results-using-2004-2015-net-manu-job-change}}

\begin{table}[!htbp] \centering 
  \caption{Effect of Manufacturing Layoffs on Democratic Vote Share (since 2004)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{Change in Share (2016-2012)} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Manufacturing Layoffs & $-$0.34$^{**}$ & $-$0.38$^{**}$ &  &  \\ 
  & (0.14) & (0.17) &  &  \\ 
  & & & & \\ 
 White Manufacturing Layoffs &  &  & $-$0.23$^{***}$ & $-$0.32$^{***}$ \\ 
  &  &  & (0.08) & (0.10) \\ 
  & & & & \\ 
 Nonwhite Manufacturing Layoffs &  &  & 0.15$^{***}$ & 0.20$^{***}$ \\ 
  &  &  & (0.05) & (0.06) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Controls For White Share/Service Layoffs & No & Yes & No & Yes \\ 
Observations & 3,049 & 3,049 & 2,750 & 2,750 \\ 
Adjusted R$^{2}$ & 0.72 & 0.72 & 0.75 & 0.75 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\newpage

\hypertarget{regression-results-using-2012-2015-net-manu-job-change}{%
\subsubsection{Regression Results (Using 2012-2015 Net Manu Job
Change)}\label{regression-results-using-2012-2015-net-manu-job-change}}

\begin{table}[!htbp] \centering 
  \caption{Effect of Manufacturing Layoffs on Democratic Vote Share} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{Change in Share (2012-2016)} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Manufacturing Layoffs & 0.43$^{**}$ & 0.37$^{**}$ &  &  \\ 
  & (0.17) & (0.17) &  &  \\ 
  & & & & \\ 
 White Manufacturing Layoffs &  &  & 6.50$^{***}$ & 2.33$^{***}$ \\ 
  &  &  & (2.20) & (0.76) \\ 
  & & & & \\ 
 Nonwhite Manufacturing Layoffs &  &  & $-$3.99$^{***}$ & $-$1.42$^{***}$ \\ 
  &  &  & (1.36) & (0.47) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Controls For White Share/Service Layoffs & No & Yes & No & Yes \\ 
Observations & 3,064 & 3,064 & 2,765 & 2,765 \\ 
Adjusted R$^{2}$ & 0.73 & 0.73 & 0.75 & 0.75 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\newpage

\hypertarget{counterfactual-assessment-of-election-using-2004-2015-layoffs}{%
\subsubsection{Counterfactual assessment of election (Using 2004-2015
Layoffs)}\label{counterfactual-assessment-of-election-using-2004-2015-layoffs}}

\includegraphics{Draft_files/figure-latex/unnamed-chunk-7-1}

\end{document}

### 2021-12-09 test.Rmd

--- 2021-12-09 rCode/Draft v2.Rmd
@@
 ```
-
-\newpage
-### Descriptive Statistics
-```{r,  echo=F}
-descriptiveData <-  readRDS("../tableData.rds")
-
-knitr::kable(descriptiveData$table04,
-             caption = "Manufacturing Job Changes 2004-2015",
-             booktabs = TRUE, digits = 2, format = 'latex')  %>%
-  kable_styling(latex_options = c("hold_position", "scale_down"))
-
-knitr::kable(descriptiveData$tableOurs,
-             caption = "Manufacturing Job Changes 2012-2015",
-             booktabs = TRUE, digits = 2, format = 'latex')  %>%
-  kable_styling(latex_options = c("hold_position", "scale_down"))
-
-```
-
-\newpage
-### Regression Results (Using 2004-2015 Net Manu Job Change)
-
-```{r,  echo=F, message = F, results = "asis"}
-
-regResultList <- readRDS("../regresults.rds")
-
-rownames(regResultList$secondStageModelNetC04A$coefficients )[rownames(regResultList$secondStageModelNetC04A$coefficients)=="firstStageModelOurs04_2$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC04$coefficients )[rownames(regResultList$secondStageModelNetC04$coefficients)=="firstStageModelOurs04_3$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04A$coefficients )[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="firstStageModelOurs04_5$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$coefficients )[rownames(regResultList$secondStageModelWNetC04$coefficients)=="firstStageModelOurs04_6$fitted.values"] <-  "White Manufacturing Layoffs"
-
-rownames(regResultList$secondStageModelWNetC04A$coefficients
-)[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$coefficients
-)[rownames(regResultList$secondStageModelWNetC04$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-
-rownames(regResultList$secondStageModelNetC04A$beta )[rownames(regResultList$secondStageModelNetC04A$beta) =="firstStageModelOurs04_2$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC04$beta )[rownames(regResultList$secondStageModelNetC04$beta)=="firstStageModelOurs04_3$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="firstStageModelOurs04_5$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="firstStageModelOurs04_6$fitted.values"] <-  "White Manufacturing Layoffs"
-
-rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-
-names(regResultList$rseNetC04A_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseNetC04_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseWNetC04A_2)[1] <- "White Manufacturing Layoffs"
-names(regResultList$rseWNetC04_2)[1] <- "White Manufacturing Layoffs"
-
-names(regResultList$rseWNetC04A_2)[names(regResultList$rseWNetC04A_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
-names(regResultList$rseWNetC04_2)[names(regResultList$rseWNetC04_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
-
-stargazer(regResultList$secondStageModelNetC04A,
-          regResultList$secondStageModelNetC04,
-          regResultList$secondStageModelWNetC04A,
-          regResultList$secondStageModelWNetC04,
-          se = list(
-            regResultList$rseNetC04A_2,
-            regResultList$rseNetC04_2,
-            regResultList$rseWNetC04A_2,
-            regResultList$rseWNetC04_2
-          ),
-          title = "Effect of Manufacturing Layoffs on Democratic Vote Share (since 2004)",
-          dep.var.labels = "Change in Share (2016-2012)",
-          omit.stat = c("rsq","ser"),
-          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
-          add.lines = list(
-            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
-          ),
-          digits = 2,
-          header = F,
-          type = "latex"
-)
-
-```
-
-\newpage
-### Regression Results (Using 2012-2015 Net Manu Job Change)
-
-```{r,  echo=F, message = F, results = "asis"}
-
-rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"
-
-rownames(regResultList$secondStageModelWNetCA$coefficients 
-)[rownames(regResultList$secondStageModelWNetCA$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC$coefficients
-)[rownames(regResultList$secondStageModelWNetC$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-
-rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"
-
-rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-
-names(regResultList$rseNetCA_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseNetC_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseWNetCA_2)[1] <- "White Manufacturing Layoffs"
-names(regResultList$rseWNetC_2)[1] <- "White Manufacturing Layoffs"
-
-names(regResultList$rseWNetCA_2)[names(regResultList$rseWNetCA_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
-names(regResultList$rseWNetC_2)[names(regResultList$rseWNetC_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
-
-stargazer(regResultList$secondStageModelNetCA,
-          regResultList$secondStageModelNetC,
-          regResultList$secondStageModelWNetCA,
-          regResultList$secondStageModelWNetC,
-          se = list(
-            regResultList$rseNetCA_2,
-            regResultList$rseNetC_2,
-            regResultList$rseWNetCA_2,
-            regResultList$rseWNetC_2
-          ),
-          title = "Effect of Manufacturing Layoffs on Democratic Vote Share",
-          dep.var.labels = "Change in Share (2012-2016)",
-          omit.stat = c("rsq","ser"),
-          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
-          add.lines = list(
-            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
-          ),
-          digits = 2,
-          header = F,
-          type = "latex"
-)
-
-```
-
-\newpage
-### Counterfactual assessment of election (Using 2004-2015 Layoffs)
-
-```{r,  echo=F, message = F}
-
-# load map
-model_input <- readRDS("../model_5_input.rds")
-model_results <- readRDS("../model_5_results.rds")
-
-# load voting data
-library(data.table)
-voting <- fread("..\\voting data.csv")
-
-# filter model input based on our regression filtering
-model_input <- model_input %>%
-  filter(is.finite(bartik_leo5_w2),
-         is.finite(mfgNetChange_white),
-         is.finite(mfgNetChange_nonwhite))
-
-# find the 25th percentile in manufacturing layoffs (our measure) across counties
-p25 <- quantile(model_input$mfgNetChange_white, (.25))
-
-model_input <- model_input %>%
-  mutate(
-
-    # calculate the counterfactual change in democratic vote share
-    # by multiplying our regression coefficient against the difference
-    # between observed manufacturing layoffs (our measure) and the
-    # 25th percentile of layoffs (nationally)
-
-    # counterfactual net change in manufacturing job losses     
-    CF_netchange = p25,
-
-    # difference between counterfactual and actual net manufacturing job losses 
-    CF_d_netchange = CF_netchange - mfgNetChange_white,
-
-    # effect size -> coeff on white manufacturing layoffs times by the dif between CF and actual
-    CF_ddem_change = CF_d_netchange*model_results$coefficients[1],
-
-    # counterfactual predicted dem vote share
-
-    P_ddem_2 = P_ddem_1 + CF_ddem_change) %>%
-
-  dplyr::select(id, state_fips, state, state_name, county_fips,
-                county, year, dem_votes_pct1, ddem_votes_pct1,
-                P_ddem_1, mfgNetChange_white, mfgNetChange_total,
-                mfgNetChange_nonwhite,
-                CF_netchange,
-                CF_d_netchange,
-                CF_ddem_change,
-                P_ddem_2)
-
-# clear voting data
-voting <- voting %>%
-  dplyr::select(year, state, county_name, county_fips,
-         party, candidatevotes) %>%
-  filter(party == "DEMOCRAT" | party == "REPUBLICAN") %>%
-  group_by(year, county_fips) %>%
-  summarize(total_dem_rep_votes = sum(candidatevotes),
-         dem_votes = sum(candidatevotes[party == "DEMOCRAT"]),
-         rep_votes = sum(candidatevotes[party == "REPUBLICAN"])) %>%
-  mutate(dem_vote_share = dem_votes/total_dem_rep_votes)
-
-# prep model input data to be merged to voting data
-model_input <- model_input %>% mutate(
-  c_fips_long = case_when(
-    str_length(as.character(county_fips)) == 1 ~
-      paste0("00", as.character(county_fips)),
-    str_length(as.character(county_fips)) == 2 ~
-      paste0("0", as.character(county_fips)),
-    TRUE ~ as.character(county_fips)),
-  s_fips_long  = case_when(
-    str_length(as.character(state_fips)) == 1 ~
-      paste0("0", as.character(state_fips)),
-    TRUE ~ as.character(state_fips)),
-
-  fips_long = paste0(s_fips_long, c_fips_long),
-  fips_numeric = as.numeric(fips_long))
-
-# join model input to observed voting data
-model_input <- left_join(model_input, voting,
-                          by = c("fips_numeric" = "county_fips",
-                                 "year" = "year"))
-
-# calculate the counterfactual dem votes and rep votes
-model_input <- model_input %>%
-  mutate(
-    CF_dem_votes = dem_votes + CF_ddem_change*total_dem_rep_votes,
-    CF_rep_votes = rep_votes - CF_ddem_change*total_dem_rep_votes)
-
-# create mapping categories
-order = c(
- # "+2% or greater", 
-  #"+1% to +2%",
-          "+0.5% to +1%",
-          "+0.25% to +0.5%", 
-          "0% to +0.25%", 
-          "0% to -0.25%")
-
-state_summary <- model_input %>%
-  group_by(state) %>%
-  summarize(actual_trump_votes = sum(rep_votes),
-            actual_dem_votes = sum(dem_votes),
-            CF_trump_votes = sum(CF_rep_votes),
-            CF_dem_votes = sum(CF_dem_votes)) %>%
-
-  mutate(changed_outcome  =
-           ifelse(
-             CF_dem_votes > CF_trump_votes &
-               actual_trump_votes > actual_dem_votes,
-             1, 0),
-    actual_trump_vs =
-      actual_trump_votes/(actual_trump_votes+ actual_dem_votes),
-    CF_trump_vs =
-      CF_trump_votes/(CF_trump_votes+CF_dem_votes),
-    delta_vs = CF_trump_vs - actual_trump_vs) %>%
-  mutate(
-    delta_vs_group = case_when(delta_vs < -.02 ~ "+2% or greater",
-                         delta_vs < -.01 ~ "+1% to +2%",
-                         delta_vs < -.005 ~ "+0.5% to +1%",
-                         delta_vs < -.0025 ~ "+0.25% to +0.5%",
-                         delta_vs < 0 ~ "0% to +0.25%",
-                         delta_vs < .0025 ~ "0% to -0.25%",
-                         delta_vs < .005 ~ "-0.25% to -0.5%",
-                         delta_vs < .01 ~ "-0.5% to -1%",
-                         TRUE ~ "-1% or greater")) %>%
-  mutate(delta_vs_group = factor(delta_vs_group, levels = order))
-
-colors =
-   c(
-    # "+2% or greater" = "#0059ff",
-     #"+1% to +2%" = "#4988fc",
-     "+0.5% to +1%" = "#86b0fc",
-     "+0.25% to +0.5%" = "#b8d1ff",
-     "0% to +0.25%" = "#dee9fc",
-     "0% to -0.25%" = "#ffeae8")
-
-# state shapefile
-state_shape <- states(
-  cb = TRUE,
-  resolution = "20m",
-  progress_bar = F
-) %>%
-  filter(GEOID != "72") %>%
-  shift_geometry()
-
-mapping <- inner_join(state_shape, state_summary,
-                      by = c("STUSPS" = "state"))
-
-mapping_small <- mapping #%>% filter(state != "DC")
-
-mapping_small <- mapping_small %>%
-  mutate(changed_outcome = ifelse(changed_outcome == 0,
-                                  "No",
-                                  "Yes"))
-
-#  make map
-flipped <- mapping_small %>% filter(changed_outcome == "Yes")
-ggplot() +
-  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "black", size = .1) +
-  scale_fill_manual(values = colors) +
-  labs(title = "Figure 3: Impact of Manufacturing Job Lossess on Democratic Vote Share",
-       subtitle = "Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses",
-       fill = "Change in Democratic Vote Share") +
-  geom_sf(data = flipped, fill = NA, 
-          aes(color = changed_outcome), 
-          size = 1) +
-  scale_color_manual(values = "#b32ab5", name = "Flipped Election") +
-  labs(color = "Flipped Election") +
-  coord_sf(datum = NA) +
-  theme_minimal() +
-  # geom_sf_text_repel(aes(label = state), data = mapping_small,
-  #                    force = .00001,  seed = 10,
-  #                    size = 2.5) +
-  theme(  axis.title.x=element_blank(),
-          axis.title.y=element_blank())
-
-```

### 2021-12-09 Final Draft/Final Draft.Rmd
updates

--- 2021-12-09 Final Draft/Final-Draft.tex
@@
-% AER-Article.tex for AEA last revised 22 June 2011
-\documentclass[AER]{AEA}
+---
+title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
+short: ""
+journal: "" # AER, AEJ, PP, JEL
+month: "`r format(Sys.Date(), '%m')`"
+year: "`r format(Sys.Date(), '%Y')`"
+vol: 1
+issue: 1
+jel:
+  - 
+  -
+keywords:
+  - 
+  - 
+author:
+  - name: Catherine Darin
+    firstname: Catherine
+    surname: Darin
+    email: cdarin@hks.harvard.edu
+    affiliation: Harvard University
+  - name: Zagreb Mukerjee
+    firstname: Zagreb
+    surname: Mukergee
+    email: zagrebmukerjee@fas.harvard.edu
+    affiliation: Harvard University
+acknowledgements: 
+abstract: |
+  What led to Donald Trump's surprising 2016 election victory?
+This paper examines the potential contribution of deindustrialization.
+Counties differ by exposure to manufacturing, which we use in an instrumental-variable approach to identify the effect of manufacturing job loss on change in Democratic vote share.
+We find that Democratic vote share falls in counties with high manufacturing job loss since 2004.
+Disaggregating this result by race shows that the Democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
+This suggests a racial component to how voters process economic hardship.
+output: rticles::aea_article
+---
 
-% The mathtime package uses a Times font instead of Computer Modern.
-% Uncomment the line below if you wish to use the mathtime package:
-%\usepackage[cmbold]{mathtime}
-% Note that miktex, by default, configures the mathtime package to use commercial fonts
-% which you may not have. If you would like to use mathtime but you are seeing error
-% messages about missing fonts (mtex.pfb, mtsy.pfb, or rmtmi.pfb) then please see
-% the technical support document at http://www.aeaweb.org/templates/technical_support.pdf
-% for instructions on fixing this problem.
+\section{First Section in Body}
 
-% Note: you may use either harvard or natbib (but not both) to provide a wider
-% variety of citation commands than latex supports natively. See below.
-
-% Uncomment the next line to use the natbib package with bibtex
-\usepackage{natbib}
-
-% Uncomment the next line to use the harvard package with bibtex
-%\usepackage[abbr]{harvard}
-
-% This command determines the leading (vertical space between lines) in draft mode
-% with 1.5 corresponding to "double" spacing.
-\draftSpacing{1.5}
-
-% For Pandoc highlighting needs
-
-% Pandoc citation processing
-
-\usepackage{hyperref}
-
-\begin{document}
-
-\title{Untitled}
-\shortTitle{A shorter title}
-% \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
-% Surname2: affiliation2, address2, email2. Acknowledgements}}
-
-\author{
-  Alice Anonymous\\
-  Bob Security\thanks{
-  Anonymous: Some Institute of Technology, \href{mailto:alice@example.com}{alice@example.com}.
-  Security: Another University, \href{mailto:bob@example.com}{bob@example.com}.
-  Acknowledgements
-}
-}
-
-\date{\today}
-\pubMonth{12}
-\pubYear{2021}
-\pubVolume{1}
-\pubIssue{1}
-\JEL{A10, A11}
-\Keywords{first keyword, second keyword}
-
-\begin{abstract}
-Abstract goes here
-\end{abstract}
-
-\maketitle
+Sample figure:
 
@@
 
-References here (manual or bibTeX). If you are using bibTeX, add your
-bib file name in place of BibFile in the bibliography command. \% Remove
-or comment out the next two lines if you are not using bibtex.
-
+References here (manual or bibTeX). If you are using bibTeX, add your bib file
+name in place of BibFile in the bibliography command.
+% Remove or comment out the next two lines if you are not using bibtex.
 \bibliographystyle{aea}
@@
 
-\% The appendix command is issued once, prior to all appendices, if any.
+% The appendix command is issued once, prior to all appendices, if any.
 \appendix
@@
 \section{Mathematical Appendix}
-
-\end{document}

### 2021-12-09 Final Draft/Final-Draft.tex
updates

@@
 % AER-Article.tex for AEA last revised 22 June 2011
-\documentclass[AER]{AEA}
+\documentclass[]{AEA}
 
@@
 
-\title{Untitled}
-\shortTitle{A shorter title}
+\title{Brother, Can You Spare a Manufacturing Job? How Voters React to
+Deindustrialization}
+
 % \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
@@
 \author{
-  Alice Anonymous\\
-  Bob Security\thanks{
-  Anonymous: Some Institute of Technology, \href{mailto:alice@example.com}{alice@example.com}.
-  Security: Another University, \href{mailto:bob@example.com}{bob@example.com}.
-  Acknowledgements
+  Catherine Darin\\
+  Zagreb Mukerjee\thanks{
+  Darin: Harvard University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
+  Mukergee: Harvard University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
 }
@@
 \pubIssue{1}
-\JEL{A10, A11}
-\Keywords{first keyword, second keyword}
+\JEL{, }
+\Keywords{, }
 
 \begin{abstract}
-Abstract goes here
+What led to Donald Trump's surprising 2016 election victory? This paper
+examines the potential contribution of deindustrialization. Counties
+differ by exposure to manufacturing, which we use in an
+instrumental-variable approach to identify the effect of manufacturing
+job loss on change in Democratic vote share. We find that Democratic
+vote share falls in counties with high manufacturing job loss since
+2004. Disaggregating this result by race shows that the Democratic vote
+share fell where layoffs affected white populations, and rose where
+layoffs affected nonwhites. This suggests a racial component to how
+voters process economic hardship.
 \end{abstract}
@@
 \maketitle
+
+\section{First Section in Body}
+
+Sample figure:
 

### 2021-12-10 Final Draft/Final Draft.Rmd
doc changes

@@
 
+```{r}
+library(tidyverse)
+library(stargazer)
+library(sandwich)
+library(lmtest)
+library(knitr)
+library(kableExtra)
+library(readxl)
+library(scales)
+library(tigris)
+
+#knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
+#knitr::opts_chunk$set(echo = FALSE, message = FALSE)
+```
+
+\section{Introduction}
+
+We replicate Baccini and Wemouth (2021), which analyzes the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
+
+We extend Baccini and Weymouth's analysis by changing the quantity of interest from **gross** manufacturing job losses to **net** manufacturing job losses.
+For example, in Baccini and Weymouth's model, if a county lost 400 manufacturing jobs from 2012-2015 and also gained 400 manufacturing jobs over the same period, they would count 400 overall layoffs.
+Using our measure of *net* manufacturing job losses, we would consider this example a 0 net change in manufacturing employment.
+Given that job destruction and creation is a natural dynamic within the economy (i.e.
+seasonal employment, creative destruction), we think that *net* job losses is a more meaningful measure.
+
+Using *net* manufacturing job losses as our outcome, we replicate Baccini and Weymouth's main model, which uses 2012-2015 manufacturing (gross) job losses to explain the change in Democratic vote share in 2016.
+Using their specifications, we find totally opposite results - that a *net* increase in white manufacturing jobs *increased* Democratic vote share, while a *net* increase in non-white manufacturing jobs *decreased* Democratic vote share.
+
+However, we don't think this is capturing the important dynamic at play.
+From 2012 to 2015, the national economy experienced a net increase in manufacturing jobs following the 2008 recession (See Figure 1).
+During this time of recovery, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery.
+Because of this v-shaped recovery, focusing only on 2012-2015 job losses/gains paints a distorted picture.
+
 \section{First Section in Body}
+
+Sample figure:
+
+  \begin{figure}
+
+```{r}
+
+```
+
+\caption{Caption for figure below.}
+\begin{figurenotes}
+Figure notes without optional leadin.
+\end{figurenotes}
+\begin{figurenotes}[Source]
+Figure notes with optional leadin (Source, in this case).
+\end{figurenotes}
+\end{figure}
+
+If we expand our measure of net manufacturing job losses to include the 2004 to 2011 period - which covers most of the period when the U.S.
+manufacturing economy was hit most intensely (See Figure 1) -- we get a result that corroborates the core intuition of Baccini and Weymouth (See Table 4).
+That is, we find that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased Democratic vote share.
+
+It is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
+Whereas Baccini and Weymouth's analysis suggests that economic changes lead to immediate political consequences, our analysis shows that economic changes can have lagged and variable effects on political outcomes.
+The mechanisms of these lagged effects merit further study.
+
+[Note: to demonstrate our point about **variable** effects, In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in Democratic vote share in other elections (2012 and 2020).]
 

### 2021-12-10 Final Draft/Final-Draft.tex
doc changes

@@
 
+\section{Introduction}
+
+We replicate Baccini and Wemouth (2021), which analyzes the effect of
+gross manufacturing job losses from 2012 to 2015 on the change in
+Democratic vote share in the 2016 presidential election.
+
+We extend Baccini and Weymouth's analysis by changing the quantity of
+interest from \textbf{gross} manufacturing job losses to \textbf{net}
+manufacturing job losses. For example, in Baccini and Weymouth's model,
+if a county lost 400 manufacturing jobs from 2012-2015 and also gained
+400 manufacturing jobs over the same period, they would count 400
+overall layoffs. Using our measure of \emph{net} manufacturing job
+losses, we would consider this example a 0 net change in manufacturing
+employment. Given that job destruction and creation is a natural dynamic
+within the economy (i.e.~seasonal employment, creative destruction), we
+think that \emph{net} job losses is a more meaningful measure.
+
+Using \emph{net} manufacturing job losses as our outcome, we replicate
+Baccini and Weymouth's main model, which uses 2012-2015 manufacturing
+(gross) job losses to explain the change in Democratic vote share in
+2016. Using their specifications, we find totally opposite results -
+that a \emph{net} increase in white manufacturing jobs \emph{increased}
+Democratic vote share, while a \emph{net} increase in non-white
+manufacturing jobs \emph{decreased} Democratic vote share.
+
+However, we don't think this is capturing the important dynamic at play.
+From 2012 to 2015, the national economy experienced a net increase in
+manufacturing jobs following the 2008 recession (See Figure 1). During
+this time of recovery, counties that experienced the most pronounced
+manufacturing job losses in prior years were also likely to experience
+the most pronounced recovery. Because of this v-shaped recovery,
+focusing only on 2012-2015 job losses/gains paints a distorted picture.
+
 \section{First Section in Body}
+
+Sample figure:
+
+\begin{figure}
+
+\caption{Caption for figure below.}
+\begin{figurenotes}
+Figure notes without optional leadin.
+\end{figurenotes}
+\begin{figurenotes}[Source]
+Figure notes with optional leadin (Source, in this case).
+\end{figurenotes}
+\end{figure}
+
+If we expand our measure of net manufacturing job losses to include the
+2004 to 2011 period - which covers most of the period when the U.S.
+manufacturing economy was hit most intensely (See Figure 1) -- we get a
+result that corroborates the core intuition of Baccini and Weymouth (See
+Table 4). That is, we find that net white manufacturing job losses
+decreased Democratic vote share, while net non-white manufacturing job
+losses increased Democratic vote share.
+
+It is important to highlight the substantive importance of the
+\emph{timing} of manufacturing layoffs on political outcomes. Whereas
+Baccini and Weymouth's analysis suggests that economic changes lead to
+immediate political consequences, our analysis shows that economic
+changes can have lagged and variable effects on political outcomes. The
+mechanisms of these lagged effects merit further study.
+
+{[}Note: to demonstrate our point about \textbf{variable} effects, In
+our next iteration of the analysis, we will show that manufacturing job
+losses had little explanatory effect on changes in Democratic vote share
+in other elections (2012 and 2020).{]}
 

### 2021-12-10 test.Rmd
doc changes

@@
 title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
-author: 'Catherine Darin and Zagreb Mukerjee'
-date: '11/29/2021'
-fontsize: 12pt
+author:
+- affiliation: Harvard University
+  email: cdarin@hks.harvard.edu
+  firstname: Catherine
+  name: Catherine Darin
+  surname: Darin
+- affiliation: Harvard University
+  email: zagrebmukerjee@fas.harvard.edu
+  firstname: Zagreb
+  name: Zagreb Mukerjee
+  surname: Mukergee
+acknowledgements: null
 output:
   pdf_document: default
-urlcolor: red
-header-includes:
-  - \usepackage{bm}
----
-\renewcommand{\arraystretch}{1.1}
-\renewcommand{\topfraction}{.85}
-\renewcommand{\bottomfraction}{.7}
-\renewcommand{\textfraction}{.15}
-\renewcommand{\floatpagefraction}{.66}
-\setcounter{topnumber}{3}
-\setcounter{bottomnumber}{3}
-\setcounter{totalnumber}{4}
-
-## Replication Instructions
-
-Please find instructions and relevant code to replicate our analysis here: https://github.com/zagrebmukerjee/ReplicationPaper
-
-## Introduction
-
+  rticles::aea_article: default
+jel:
+- ~
+- ~
+journal: ''
+keywords:
+- ~
+- ~
+month: `r format(Sys.Date(), '%m')`
+issue: 1
+short: ''
+abstract: |
   What led to Donald Trump's surprising 2016 election victory?
@@
 This suggests a racial component to how voters process economic hardship.
+vol: 1
+year: `r format(Sys.Date(), '%Y')`
+---
 
-Base paper: Baccini and Weymouth 2021, "Gone For Good: Deindustrialization, White Voter Backlash, and US Presidential Voting." *APSR*.
+\section{Introduction}
 
-## Outline
+We replicate Baccini and Wemouth (2021), which analyzes the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
 
-#### Framing story
-
-To do: Qualitative description of the trajectory of XYZ county that swung from Obama to Trump and suffered big manufacturing layoffs.
-This will establish the stakes and connect this to the broader conversation.
-
-### Substantive importance
-
-Why did Trump win in 2016?
-There is a longstanding debate about relative importance of race and economic factors.
-Complicated by the interaction of the two.
-We hope to identify the importance of manufacturing job losses, both in aggregate and for different racial groups.
-Eventually we think that people should stop asking "race or economics" when the answer is likely both.
-
-### Empirical strategy
-
-Differential manufacturing exposure across counties allows for identification of the causal effect of deindustrialization on change in Dem vote share.
-Further differences in racial exposure to mfg layoffs allows for identification of the interaction between race and deindustrialization.
-
-### Data and methods
-
-Data is Census Quarterly Workforce Indicators, which break down county employment by industry, race and ethnicity. Augmented with public data on vote shares, employment, etc.
-
-We look at total employment and manufacturing employment (NAICS 31-33, see extensions below).
-We then  compute net change in mfg jobs (long term job loss) from 2004 to 2015, relative to employment in 2004.
-
-We might be worried about endogeneity for manufacturing job losses.
-So we use a shift-share instrument: we predict net job losses per worker with county-level manufacturing as a share of total employment, plus controls.
-
-Controls: unemployment in 2015, college educated share of population, male share of population, layoffs in service sector, white share of population (to control for demographic trends).
-We want to know if there's something singular about manufacturing jobs.
-
-### Extension Relative to Baccini and Weymouth (2021)
-
-In their main model, Baccini and Weymouth looked at the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
-
-Our key extension of Baccini and Weymouth's analysis is changing the quantity of interest from **gross** manufacturing job losses to **net** manufacturing job losses.
+We extend Baccini and Weymouth's analysis by changing the quantity of interest from **gross** manufacturing job losses to **net** manufacturing job losses.
 For example, in Baccini and Weymouth's model, if a county lost 400 manufacturing jobs from 2012-2015 and also gained 400 manufacturing jobs over the same period, they would count 400 overall layoffs.
@@
 Using their specifications, we find totally opposite results - that a *net* increase in white manufacturing jobs *increased* Democratic vote share, while a *net* increase in non-white manufacturing jobs *decreased* Democratic vote share.
-(See Table 3)
 
@@
 Because of this v-shaped recovery, focusing only on 2012-2015 job losses/gains paints a distorted picture.
-[To DO: Empirically show negative correlation described here]
-
-If we expand our measure of net manufacturing job losses to include the 2004 to 2011 period - which covers most of the period when the U.S.
-manufacturing economy was hit most intensely (See Figure 1) -- we get a result that corroborates the core intuition of Baccini and Weymouth (See Table 4).
-That is, we find that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased Democratic vote share.
-
-It is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
-Whereas Baccini and Weymouth's analysis suggests that economic changes lead to immediate political consequences, our analysis shows that economic changes can have lagged and variable effects on political outcomes.
-The mechanisms of these lagged effects merit further study.
-
-[Note: to demonstrate our point about **variable** effects, In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in Democratic vote share in other elections (2012 and 2020).]
-
-### Key Findings
-
-We find that, in aggregate, manufacturing job losses were associated with loss of Democratic vote share in the 2016 election.
-10 manufacturing job losses per worker in a county since 2004 corresponded to a 3.8 \% loss in vote share, plus or minus 3.3 \%.
-Breaking it down by race, we see that [TO DO: complete thought].
-
-Figure 3 demonstrates the practical significance of our estimates.
-Using our main results from regression 3 in Table 4, we simulate a counterfactual 2016 election assuming that all counties experienced white manufacturing job losses equivalent to the county at the 25th national percentile.
-We highlight states in purple if this counterfactual shows a state flipping from Trump to Clinton.
-
-Additionally, we find that, given the evolution of the business cycle, considering only recent job losses can paint a misleading picture of the relationship between manufacturing job losses and changes in vote share.
-In fact, we find that net manufacturing job losses from 2004 to 2011 are crucial to explaining Trump's 2016 win.
-This finding suggests that economic changes, like manufacturing layoffs, can have lagged and variable political consequence.
-
-### Potential Future Work
-
-- Temporal: Finding a better way to characterize the potentially lagged effect of manufacturing job losses on Democratic votes. Incorporating study of the 2008, 2012, 2020 elections. 
-- Disaggregation: Instead of instrumenting by manufacturing share, perhaps we can look at layoffs by industry in each county.
-While aggregate manufacturing employment may be endogenous, there's less reason to believe that specific industries would be (cf.
-Autor, Dorn and Hanson).
-This may also allow us to get further away from ecological inference problems.
-- Trend-cycle estimation: There are techniques from econometrics and other places that could potentially be used to decompose gross layoffs into seasonal and non-seasonal components. 
-- Mechanisms: survey work to examine where the racial difference in economic voting behavior comes from. Is it expressive? Is it because information is transmitted along racially segregated networks?
-
-## Tables and Figures
-
-```{r setup, echo=F, message = F, warning= F}
-library(tidyverse)
-library(stargazer)
-library(sandwich)
-library(lmtest)
-library(knitr)
-library(kableExtra)
-library(readxl)
-library(scales)
-library(tigris)
-
-knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
-knitr::opts_chunk$set(echo = FALSE, message = FALSE)
-```
-
-### Manufacturing Layoffs Over Time
-
-```{r, message = F}
-# manufacturing layoffs over time
-
-national_ts <- read_xlsx("../National_Data_TS.xlsx")
-
-national_ts <- national_ts %>%
-  rename(year = 1,
-         net_job_change = 2) %>%
-  dplyr::select(year, net_job_change) %>%
-  rename(Year = year, `Job Change per Worker` = net_job_change) %>%
-  mutate(
-    Year = as.numeric(Year),
-    `Job Change per Worker` = `Job Change per Worker`*4) %>% group_by()
-
-ggplot(data = national_ts %>% filter(Year >= 1995),
-       aes(x = Year, y = `Job Change per Worker`)) +
-  ylab("Millions of Jobs") +
-  ggtitle("Figure 1. Nationwide Change in Manufacturing Employment, 1995-2019") +
-  geom_col(fill = "#4287f5") + scale_x_continuous(breaks=seq(1995,2019,2)) +
-	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6)) +
-  theme_minimal()
-
-```
-
-\newpage
-### Geographic Concentration of Layoffs
-
-### 04 to 15
-
-```{r,  echo=F, message = F, results = "asis"}
-
-# load map
-model_input <- readRDS("../model_5_input.rds")
-
-# state shapefile
-county_shape <- counties(
-  cb = TRUE,
-  resolution = "20m",
-  progress_bar = F
-) %>%
-  shift_geometry() %>%
-  mutate(STATEFP = as.numeric(STATEFP),
-         COUNTYFP = as.numeric(COUNTYFP))
-
-state_shape <- states(
-  cb = TRUE,
-  resolution = "20m",
-  progress_bar = F
-) %>%
-  filter(GEOID != "72" & GEOID != "02", GEOID != "15")
-
-# group counties into sextiles
-model_input <- model_input %>%
-  group_by() %>%
-  mutate(ntile_mfg = as.character(ntile(mfgNetChange_total , 6)))
-
-# find cutoffs
-
-sum <- model_input %>%
-  group_by(ntile_mfg) %>%
-  summarize(min = min(mfgNetChange_total),
-            max = max(mfgNetChange_total))
-
-labels = c(
-  "1" = "1% or Greater Gain",
-  "2" = "0% to 1% Gain",
-  "3" = "0% to 1% Loss",
-  "4" = "1% to 3% Loss",
-  "5" = "3% to 6% Loss",
-  "6" = "6% or Greater Loss")
-
-colors <- c("1" = "#778868",
-            "2" = "#b5b991",
-            "3" = "#f6edbd",
-            "4" = "#edbb8a",
-            "5" = "#de8a5a",
-            "6" = "#ca562c")
-
-#3d5941,#778868,#b5b991,#f6edbd,#edbb8a,#de8a5a,#ca562c
-mapping_county <- inner_join(county_shape, model_input,
-                      by = c("STATEFP" = "state_fips",
-                             "COUNTYFP" = "county_fips"))
-
-ggplot() +
-  geom_sf(data = mapping_county, aes(fill = ntile_mfg),
-          color = NA, size = .01) +
-  scale_fill_manual(values = colors,
-                    labels = labels) +
-  # add state lines
-  geom_sf(data = state_shape, fill = NA, color = "black", size = .1) +
-  coord_sf(datum = NA) +
-  theme_minimal() +
-  # geom_sf_text_repel(aes(label = state), data = mapping_small,
-  #                    force = .00001,  seed = 10,
-  #                    size = 2.5) +
-  theme(  axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          text = element_text(size = 8)) +
-  labs(title = "Figure 2: Net Change in Manufacturing Employment from 2004 to 2015",
-       subtitle = "Normalized by 2004 Overall Employment Levels",
-       fill = "Cumulative Change in Manufacturing\nEmployment (2004-2015) per\n2004 Worker")
-
-```
-
-\newpage
-
-### 12 to 15
-
-```{r,  echo=F, message = F, results = "asis"}
-
-# load map
-model_input <- readRDS("../input_12_16.rds")
-
-# state shapefile
-county_shape <- counties(
-  cb = TRUE,
-  resolution = "20m",
-  progress_bar = F
-) %>%
-  shift_geometry() %>%
-  mutate(STATEFP = as.numeric(STATEFP),
-         COUNTYFP = as.numeric(COUNTYFP))
-
-state_shape <- states(
-  cb = TRUE,
-  resolution = "20m",
-  progress_bar = F
-) %>%
-  filter(GEOID != "72" & GEOID != "02", GEOID != "15")
-
-# group counties into sextiles
-model_input <- model_input %>%
-  group_by() %>%
-  mutate(ntile_mfg = as.character(ntile(mfgNetChange_total , 6)))
-
-# find cutoffs
-
-sum <- model_input %>%
-  group_by(ntile_mfg) %>%
-  summarize(min = min(mfgNetChange_total),
-            max = max(mfgNetChange_total))
-
-labels = c(
-  "1" = "1% or Greater Gain",
-  "2" = "0% to 1% Gain",
-  "3" = "0% to 1% Loss",
-  "4" = "1% to 3% Loss",
-  "5" = "3% to 6% Loss",
-  "6" = "6% or Greater Loss")
-
-colors <- c("1" = "#778868",
-            "2" = "#b5b991",
-            "3" = "#f6edbd",
-            "4" = "#edbb8a",
-            "5" = "#de8a5a",
-            "6" = "#ca562c")
-
-#3d5941,#778868,#b5b991,#f6edbd,#edbb8a,#de8a5a,#ca562c
-mapping_county <- inner_join(county_shape, model_input,
-                      by = c("STATEFP" = "state_fips",
-                             "COUNTYFP" = "county_fips"))
-
-ggplot() +
-  geom_sf(data = mapping_county, aes(fill = ntile_mfg),
-          color = NA, size = .01) +
-  scale_fill_manual(values = colors,
-                    labels = labels) +
-  # add state lines
-  geom_sf(data = state_shape, fill = NA, color = "black", size = .1) +
-  coord_sf(datum = NA) +
-  theme_minimal() +
-  # geom_sf_text_repel(aes(label = state), data = mapping_small,
-  #                    force = .00001,  seed = 10,
-  #                    size = 2.5) +
-  theme(  axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          text = element_text(size = 8)) +
-  labs(title = "Figure 2: Net Change in Manufacturing Employment from 2012 to 2015",
-       subtitle = "Normalized by 2011 Overall Employment Levels",
-       fill = "Cumulative Change in Manufacturing\nEmployment (2012-2015) per\n2011 Worker")
-
-```

### 2021-12-10 Final Draft/Final Draft.Rmd
some writing

--- 2021-12-09 Final Draft/Final Draft.Rmd
@@
 issue: 1
-jel:
-  - 
-  -
-keywords:
-  - 
-  - 
 author:
@@
     firstname: Zagreb
-    surname: Mukergee
+    surname: Mukerjee
     email: zagrebmukerjee@fas.harvard.edu
@@
 
-\section{First Section in Body}
+\section{Data and Methods}
 
-Sample figure:
+\subsection{Data}
+
+Following \cite{BW}, our unit of analysis is the county.
+This allows us to capture not only the direct effects of deindustrialization on laid-off manufacturing workers, but also on the local economy.
+The primary outcome variable is the county's change in Democratic vote share between 2012 and 2016.
+We obtain this from XXXXXXXXX
+
+We want to measure the causal relationship between deindustrialization and the change in vote share.
+As a measure of deindustrialization, we use the destruction of manufacturing jobs, as a share of the total manufacturing
 

### 2021-12-10 rCode/Scratch/cbpsScratch.R
cbps

@@ -1,0 +1,305 @@
+library(CBPS)
+
+
+data("lalonde")
+
+fit <- CBPS(treat ~ age + educ + re75 + re74 +
+              I(re75==0) + I(re74==0),
+            data = LaLonde, ATT = TRUE)
+balance(fit)
+
+
+
+
+
+datasetOurs04Limited <- datasetOurs04 %>%  
+  filter(is.finite(mfgNetChange_total), is.finite(mfgNetChange_white ), is.finite(mfgNetChange_nonwhite ), is.finite(bartik_leo5_w2))
+
+
+
+plot(datasetOurs04Limited$ddem_votes_pct1, datasetOurs04Limited$mfgNetChange_total)
+
+plot(datasetOurs04Limited$mfgNetChange_white, datasetOurs04Limited$msl_educ_prop)
+
+fit04 <- CBPS(mfgNetChange_total ~ LAU_unemp_rate_4y + pers_m_total_share_4y +
+                pers_coll_share_4y + white_counties_4y + msl_service_pc4y + mfgShare_total + totalEmp_total, data = datasetOurs04Limited, method = "exact")
+
+fit04_white <- CBPS(mfgNetChange_white ~ LAU_unemp_rate_4y + pers_m_total_share_4y +
+                pers_coll_share_4y + white_counties_4y + msl_service_pc4y + mfgShare_white + totalEmp_white, data = datasetOurs04Limited, method = "exact")
+
+plot(fit04)
+plot(fit04_white)
+
+balance(fit04)
+balance(fit04_white)
+
+
+###############################################################
+# Test to make sure my listwise deletion didn't do too much
+################################################################
+
+# model 2
+firstStageModelOurs04L_2 <- felm(
+  data = datasetOurs04Limited,
+  formula = mfgNetChange_total ~ bartik_leo5  +
+    LAU_unemp_rate_4y + pers_m_total_share_4y +
+    pers_coll_share_4y + white_counties_4y   | id_state)
+
+secondStageModelOurs04L_2 <- felm(
+  data = datasetOurs04Limited,
+  formula = ddem_votes_pct1 ~ firstStageModelOurs04L_2$fitted.values +
+    LAU_unemp_rate_4y + pers_m_total_share_4y +
+    pers_coll_share_4y + white_counties_4y  | id_state)
+
[…]

### 2021-12-10 Final Draft/Final Draft.Rmd
cbps

--- 2021-12-10 Final Draft/Final Draft.Rmd
@@
 
-\section{First Section in Body}
+\section{Data and Methods}
 
-Sample figure:
+\subsection{Data}
 
-  \begin{figure}
+Following \cite{BW}, our unit of analysis is the county.
+This allows us to capture not only the direct effects of deindustrialization on laid-off manufacturing workers, but also on the local economy.
+The primary outcome variable is the county's change in Democratic vote share between 2012 and 2016.
+We obtain this from XXXXXXXXX
 
-```{r}
-
-```
-
-\caption{Caption for figure below.}
-\begin{figurenotes}
-Figure notes without optional leadin.
-\end{figurenotes}
-\begin{figurenotes}[Source]
-Figure notes with optional leadin (Source, in this case).
-\end{figurenotes}
-\end{figure}
+We want to measure the causal relationship between deindustrialization and the change in vote share.
+As a measure of deindustrialization, we use the destruction of manufacturing jobs, as a share of the total employment in each county.
 
@@
 \begin{figure}
-Figure here.
 

### 2021-12-10 Final Draft/Final-Draft.tex
some writing

@@
 % For Pandoc highlighting needs
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 
 % Pandoc citation processing
+
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
@@
   Zagreb Mukerjee\thanks{
-  Darin: Harvard University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
-  Mukergee: Harvard University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
+  Darin: Harvard
+University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
+  Mukerjee: Harvard
+University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
 }
@@
 \pubIssue{1}
-\JEL{, }
-\Keywords{, }
+\JEL{}
+\Keywords{}
 
@@
 \maketitle
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(tidyverse)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## -- Attaching packages --------------------------------------- tidyverse 1.3.1 --
+\end{verbatim}
+
+\begin{verbatim}
+## v ggplot2 3.3.5     v purrr   0.3.4
+## v tibble  3.1.4     v dplyr   1.0.5
+## v tidyr   1.1.3     v stringr 1.4.0
+## v readr   1.4.0     v forcats 0.5.1
+\end{verbatim}
+
+\begin{verbatim}
+## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
+## x dplyr::filter() masks stats::filter()
+## x dplyr::lag()    masks stats::lag()
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(stargazer)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## Please cite as:
+\end{verbatim}
+
+\begin{verbatim}
+##  Hlavac, Marek (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables.
+\end{verbatim}
+
+\begin{verbatim}
+##  R package version 5.2.2. https://CRAN.R-project.org/package=stargazer
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(sandwich)}
+\FunctionTok{library}\NormalTok{(lmtest)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Loading required package: zoo
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Attaching package: 'zoo'
+\end{verbatim}
+
+\begin{verbatim}
+## The following objects are masked from 'package:base':
+## 
+##     as.Date, as.Date.numeric
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(knitr)}
+\FunctionTok{library}\NormalTok{(kableExtra)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## Attaching package: 'kableExtra'
+\end{verbatim}
+
+\begin{verbatim}
+## The following object is masked from 'package:dplyr':
+## 
+##     group_rows
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(readxl)}
+\FunctionTok{library}\NormalTok{(scales)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## Attaching package: 'scales'
+\end{verbatim}
+
+\begin{verbatim}
+## The following object is masked from 'package:purrr':
+## 
+##     discard
+\end{verbatim}
+
+\begin{verbatim}
+## The following object is masked from 'package:readr':
+## 
+##     col_factor
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(tigris)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## To enable 
+## caching of data, set `options(tigris_use_cache = TRUE)` in your R script or .Rprofile.
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\#knitr::opts\_chunk$set(fig.pos = "!H", out.extra = "")}
+\CommentTok{\#knitr::opts\_chunk$set(echo = FALSE, message = FALSE)}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-\section{First Section in Body}
+\section{Data and Methods}
 
-Sample figure:
+\subsection{Data}
+
+Following \cite{BW}, our unit of analysis is the county. This allows us
+to capture not only the direct effects of deindustrialization on
+laid-off manufacturing workers, but also on the local economy. The
+primary outcome variable is the county's change in Democratic vote share
+between 2012 and 2016. We obtain this from XXXXXXXXX
+
+We want to measure the causal relationship between deindustrialization
+and the change in vote share. As a measure of deindustrialization, we
+use the destruction of manufacturing jobs, as a share of the total
+employment in each county.
 

### 2021-12-10 Final Draft/Final Draft.Rmd
more writing

@@
 title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
-short: ""
+short: "Brother, Can You Spare a Manufacturing Job? "
 journal: "" # AER, AEJ, PP, JEL
@@
 
-```{r}
-library(tidyverse)
-library(stargazer)
-library(sandwich)
-library(lmtest)
-library(knitr)
-library(kableExtra)
-library(readxl)
-library(scales)
-library(tigris)
-
-#knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
-#knitr::opts_chunk$set(echo = FALSE, message = FALSE)
-```
-
 \section{Introduction}
 
-We replicate Baccini and Wemouth (2021), which analyzes the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
+We replicate \cite{BW21}, which analyzes the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
 
@@
 
-Following \cite{BW}, our unit of analysis is the county.
+Following \cite{BW21}, our unit of analysis is the county.
 This allows us to capture not only the direct effects of deindustrialization on laid-off manufacturing workers, but also on the local economy.
@@
 We want to measure the causal relationship between deindustrialization and the change in vote share.
-As a measure of deindustrialization, we use the destruction of manufacturing jobs, as a share of the total employment in each county.
+As a measure of deindustrialization, we use the loss of manufacturing jobs as a share of the total beginning-of-period employment in each county.
+Suppose at the beginning of our period there were $2000$ manufacturing workers in a county, and $8000$ non-manufacturing workers.
+At the end there are only $1500$ manufacturing workers.
+This is a loss of $500/10000 = 5\%.$
+
+In this choice we diverge from \cite{BW21}, which uses **gross** manufacturing job losses.
+For example, if a county lost $450$ manufacturing jobs from 2012-2015 and also gained $400$ manufacturing jobs over the same period, this would be $450$ **gross** job losses, but only $50$ **net** job losses.
+The **gross** measure captures several dynamics unrelated to deindustrialization - for example, seasonal unemployment in a food-manufacturing region, or workers moving between jobs.
+Thus we believe the **net** job losses over a period are the more accurate measure.
+
+Data on job gains and losses are obtained, using an API, from the Census Bureau's Quarterly Workforce Indicators (\cite{QWI}), which contains (among other things) information about employment by industry and county.
+These statistics are further disaggregated by race and ethnicity.
+The Census Bureau obtains this data from a combination of sources, such as administrative tax data and the U.S.
+Census.
+
+XXXXXXXXXXXXXXXX sources of other data
+
+\subsection{Methods}
+
+We conduct two related tests of our hypothesis.
+Our first test involves an instrumental-variable approach.
+A regression of change in Democratic vote share on manufacturing job losses risks endogeneity, in case counties with manufacturing job losses were otherwise predisposed to turn towards Trump (a singular candidate, after all).
+To mitigate these risks, \cite{BW21} uses a Bartik instrument, which we adapt.
+This instrument essentially uses the cross-county distribution of manufacturing employment as a source of exogenous variation.
+
+$$
+\begin{aligned}
+b_{j,c} &=& \frac{\text{Manufacturing Employment}_{j,c} \text{ at } t_0}{\text{Total Employment}_c \text{ at }t_0}  \\
+&&  * \frac{\text{National Manufacturing Job Change}_{j,c} }{\text{Total National Employment at }t_0} \\
+\end{aligned}
+$$
 

### 2021-12-10 Final Draft/Final-Draft.tex
more writing

--- 2021-12-10 Final Draft/Final-Draft.tex
@@
 
-We replicate Baccini and Wemouth (2021), which analyzes the effect of
-gross manufacturing job losses from 2012 to 2015 on the change in
-Democratic vote share in the 2016 presidential election.
+We replicate \cite{BW21}, which analyzes the effect of gross
+manufacturing job losses from 2012 to 2015 on the change in Democratic
+vote share in the 2016 presidential election.
 
@@
 
-\section{First Section in Body}
+\section{Data and Methods}
 
-Sample figure:
+\subsection{Data}
 
-\begin{figure}
+Following \cite{BW21}, our unit of analysis is the county. This allows
+us to capture not only the direct effects of deindustrialization on
+laid-off manufacturing workers, but also on the local economy. The
+primary outcome variable is the county's change in Democratic vote share
+between 2012 and 2016. We obtain this from XXXXXXXXX
 
-\caption{Caption for figure below.}
-\begin{figurenotes}
-Figure notes without optional leadin.
-\end{figurenotes}
-\begin{figurenotes}[Source]
-Figure notes with optional leadin (Source, in this case).
-\end{figurenotes}
-\end{figure}
+We want to measure the causal relationship between deindustrialization
+and the change in vote share. As a measure of deindustrialization, we
+use the loss of manufacturing jobs as a share of the total
+beginning-of-period employment in each county. Suppose at the beginning
+of our period there were \(2000\) manufacturing workers in a county, and
+\(8000\) non-manufacturing workers. At the end there are only \(1500\)
+manufacturing workers. This is a loss of \(500/10000 = 5\%.\)
+
+In this choice we diverge from \cite{BW21}, which uses \textbf{gross}
+manufacturing job losses. For example, if a county lost \(450\)
+manufacturing jobs from 2012-2015 and also gained \(400\) manufacturing
+jobs over the same period, this would be \(450\) \textbf{gross} job
+losses, but only \(50\) \textbf{net} job losses. The \textbf{gross}
+measure captures several dynamics unrelated to deindustrialization - for
+example, seasonal unemployment in a food-manufacturing region, or
+workers moving between jobs. Thus we believe the \textbf{net} job losses
+over a period are the more accurate measure.
+
+Data on job gains and losses are obtained, using an API, from the Census
+Bureau's Quarterly Workforce Indicators (\cite{QWI}), which contains
+(among other things) information about employment by industry and
+county. These statistics are further disaggregated by race and
+ethnicity. The Census Bureau obtains this data from a combination of
+sources, such as administrative tax data and the U.S. Census.
+
+XXXXXXXXXXXXXXXX sources of other data
+
+\subsection{Methods}
+
+We conduct two related tests of our hypothesis. Our first test involves
+an instrumental-variable approach. A regression of change in Democratic
+vote share on manufacturing job losses risks endogeneity, in case
+counties with manufacturing job losses were otherwise predisposed to
+turn towards Trump (a singular candidate, after all). To mitigate these
+risks, \cite{BW21} uses a Bartik instrument, which we adapt. This
+instrument essentially uses the cross-county distribution of
+manufacturing employment as a source of exogenous variation.
+
+\[
+\begin{aligned}
+b_{j,c} &=& \frac{\text{Manufacturing Employment}_{j,c} \text{ at } t_0}{\text{Total Employment}_c \text{ at }t_0}  \\
+&&  * \frac{\text{National Manufacturing Job Change}_{j,c} }{\text{Total National Employment at }t_0} \\
+\end{aligned}
+\]
 

### 2021-12-10 Final Draft/Final Draft.Rmd
text and cites

@@
 
-We replicate \cite{BW21}, which analyzes the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
+We replicate \cite{Baccini21}, which analyzes the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
 
@@
 
-Following \cite{BW21}, our unit of analysis is the county.
+Following \cite{Baccini21}, our unit of analysis is the county.
 This allows us to capture not only the direct effects of deindustrialization on laid-off manufacturing workers, but also on the local economy.
@@
 
-In this choice we diverge from \cite{BW21}, which uses **gross** manufacturing job losses.
+In this choice we diverge from \cite{Baccini21}, which uses **gross** manufacturing job losses.
 For example, if a county lost $450$ manufacturing jobs from 2012-2015 and also gained $400$ manufacturing jobs over the same period, this would be $450$ **gross** job losses, but only $50$ **net** job losses.
@@
 A regression of change in Democratic vote share on manufacturing job losses risks endogeneity, in case counties with manufacturing job losses were otherwise predisposed to turn towards Trump (a singular candidate, after all).
-To mitigate these risks, \cite{BW21} uses a Bartik instrument, which we adapt.
+To mitigate these risks, \cite{Baccini21} uses a Bartik instrument, which we adapt (see \cite{Bartik91}).
 This instrument essentially uses the cross-county distribution of manufacturing employment as a source of exogenous variation.
@@
 $$
+
+Using this instrument, we then conduct a two stage regression. First we estimate manufacturing job loss with the Bartik Instrument
 
@@
 \bibliography{references}
-
-% The appendix command is issued once, prior to all appendices, if any.
-\appendix
-
-\section{Mathematical Appendix}

### 2021-12-10 Final Draft/Final-Draft.tex
text and cites

@@
 Deindustrialization}
-
+\shortTitle{Brother, Can You Spare a Manufacturing Job?}
 % \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
@@
 
-We replicate \cite{BW21}, which analyzes the effect of gross
+We replicate \cite{Baccini21}, which analyzes the effect of gross
 manufacturing job losses from 2012 to 2015 on the change in Democratic
@@
 
-Following \cite{BW21}, our unit of analysis is the county. This allows
-us to capture not only the direct effects of deindustrialization on
-laid-off manufacturing workers, but also on the local economy. The
+Following \cite{Baccini21}, our unit of analysis is the county. This
+allows us to capture not only the direct effects of deindustrialization
+on laid-off manufacturing workers, but also on the local economy. The
 primary outcome variable is the county's change in Democratic vote share
@@
 
-In this choice we diverge from \cite{BW21}, which uses \textbf{gross}
-manufacturing job losses. For example, if a county lost \(450\)
-manufacturing jobs from 2012-2015 and also gained \(400\) manufacturing
-jobs over the same period, this would be \(450\) \textbf{gross} job
-losses, but only \(50\) \textbf{net} job losses. The \textbf{gross}
-measure captures several dynamics unrelated to deindustrialization - for
-example, seasonal unemployment in a food-manufacturing region, or
-workers moving between jobs. Thus we believe the \textbf{net} job losses
-over a period are the more accurate measure.
+In this choice we diverge from \cite{Baccini21}, which uses
+\textbf{gross} manufacturing job losses. For example, if a county lost
+\(450\) manufacturing jobs from 2012-2015 and also gained \(400\)
+manufacturing jobs over the same period, this would be \(450\)
+\textbf{gross} job losses, but only \(50\) \textbf{net} job losses. The
+\textbf{gross} measure captures several dynamics unrelated to
+deindustrialization - for example, seasonal unemployment in a
+food-manufacturing region, or workers moving between jobs. Thus we
+believe the \textbf{net} job losses over a period are the more accurate
+measure.
 
@@
 turn towards Trump (a singular candidate, after all). To mitigate these
-risks, \cite{BW21} uses a Bartik instrument, which we adapt. This
+risks, \cite{Baccini21} uses a Bartik instrument, which we adapt. This
 instrument essentially uses the cross-county distribution of
@@
 \]
+
+Using this instrument, we then conduct a two stage regression. First we
+estimate manufacturing job loss with the Bartik Instrument
 

### 2021-12-10 Final Draft/Final Draft.Rmd
more text

@@
 This paper examines the potential contribution of deindustrialization.
-Counties differ by exposure to manufacturing, which we use in an instrumental-variable approach to identify the effect of manufacturing job loss on change in Democratic vote share.
+We use an instrumental-variable approach and a covariate-balancing approach to identify the effect of manufacturing job loss on change in Democratic vote share.
 We find that Democratic vote share falls in counties with high manufacturing job loss since 2004.
@@
 
-\section{Introduction}
+This paper analyzes the relationship between deindustrialization, race, and the election of Donald Trump in 2016.
+Previous analysis has frequently focused on racial animus, trade, or the conjunction of the two (\cite{Autor20}; \cite{che16}; \cite{BR21}).
+We extend the analysis of \cite{Baccini21}, one of the first papers to examine the effects of deindustrialization in a localized way.
+Deindustrialization - the transition of the U.S.
+economy away from manufacturing - has led to widespread job loss and created knock-on adverse effects in many formerly industrial areas.
+Along with \cite{Baccini21}, we find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites.
+However, we find that the related effects in the 2016 election are not associated with recent manufacturing job loss; rather, the opposite.
+Counties with manufacturing job losses from 2012-2015 tended to become more Democratic.
+We extend the analysis to the 2004-2015 period, to capture the long-term effects of deindustrialization on a region.
+Doing so, we find that regions experiencing more manufacturing job loss swung towards Donald Trump in 2016, and that this occurred more when those losing jobs were white.
 
-We replicate \cite{Baccini21}, which analyzes the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
-
-We extend Baccini and Weymouth's analysis by changing the quantity of interest from **gross** manufacturing job losses to **net** manufacturing job losses.
-For example, in Baccini and Weymouth's model, if a county lost 400 manufacturing jobs from 2012-2015 and also gained 400 manufacturing jobs over the same period, they would count 400 overall layoffs.
-Using our measure of *net* manufacturing job losses, we would consider this example a 0 net change in manufacturing employment.
-Given that job destruction and creation is a natural dynamic within the economy (i.e.
-seasonal employment, creative destruction), we think that *net* job losses is a more meaningful measure.
-
-Using *net* manufacturing job losses as our outcome, we replicate Baccini and Weymouth's main model, which uses 2012-2015 manufacturing (gross) job losses to explain the change in Democratic vote share in 2016.
-Using their specifications, we find totally opposite results - that a *net* increase in white manufacturing jobs *increased* Democratic vote share, while a *net* increase in non-white manufacturing jobs *decreased* Democratic vote share.
-
-However, we don't think this is capturing the important dynamic at play.
-From 2012 to 2015, the national economy experienced a net increase in manufacturing jobs following the 2008 recession (See Figure 1).
-During this time of recovery, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery.
+Our analysis extends \cite{Baccini21} in several ways.
+First, we change focus from a measure of gross losses in manufacturing jobs to net losses.
+As discussed in \ref{datasec}, we believe this to be a more accurate measure of deindustrialization.
+Second, we change the temporal focus.
+Rather than focusing on manufacturing job loss in 2012-2015, we extend our analysis back to 2004.
+This is an important change.
+As shown XXXXXXXXXXXXXX FIGURE XXXXXXXXXXXXXXX, the bulk of U.S.
+manufacturing job loss took place prior to 2012; in fact, the 2012-2015 period was characterized by a slight rebound in manufacturing jobs.
+During this rebound, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery XXXXXXXXXXXXXXX FIGURE XXXXXXXXXXXXX.
 Because of this v-shaped recovery, focusing only on 2012-2015 job losses/gains paints a distorted picture.
+Finally, we augment the instrumental-variable approach with one based on covariate balancing, which produces similar results.
 
 \section{Data and Methods} 
+\label{datamethods}
 
 \subsection{Data} 
+\label{datasec}
 
@@
 \subsection{Methods} 
+\label{methodssec}
 
@@
 
-Using this instrument, we then conduct a two stage regression. First we estimate manufacturing job loss with the Bartik Instrument
+Using this instrument, we then conduct a two stage regression.
+First we estimate manufacturing job loss with the Bartik Instrument and a set of county-level controls; then we use the estimated values of job losses to predict Democratic vote share.
+In these regressions we control for unemployment, service layoffs, the share of college-educated voters, and the share of male voters.
+For some estimates, we also control for the white share of the population.
+These controls are similar to those of \cite{Baccini21}.
+
+Our second approach involves attempting to balance the covariates of the deindustrialization treatment.
+We use the same covariates as are used in controls above, as well as manufacturing as share of the population and total population.
+We apply the method of Covariate Balancing Propensity Scores, as developed by \cite{Imai14}; this method generates weights to reduce the correlation between covariates and treatment, while addressing several of the issues with propensity score weights.
+Given covariate-balancing weights, we then conduct a single-stage weighted regression of change in Democratic vote share on manufacturing job loss, using the same controls as above.
+
+XXXXXXXXXXXXXXX BALANCE FIGURE??? XXXXXXXXXXXXXXXXXXXXXXXXXXX
+
+\subsection{Results}
 
@@
 [Note: to demonstrate our point about **variable** effects, In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in Democratic vote share in other elections (2012 and 2020).]
+
+\subsection{Conclusion}
 

### 2021-12-10 Final Draft/Final-Draft.tex
more text

@@
 What led to Donald Trump's surprising 2016 election victory? This paper
-examines the potential contribution of deindustrialization. Counties
-differ by exposure to manufacturing, which we use in an
-instrumental-variable approach to identify the effect of manufacturing
-job loss on change in Democratic vote share. We find that Democratic
-vote share falls in counties with high manufacturing job loss since
-2004. Disaggregating this result by race shows that the Democratic vote
-share fell where layoffs affected white populations, and rose where
-layoffs affected nonwhites. This suggests a racial component to how
-voters process economic hardship.
+examines the potential contribution of deindustrialization. We use an
+instrumental-variable approach and a covariate-balancing approach to
+identify the effect of manufacturing job loss on change in Democratic
+vote share. We find that Democratic vote share falls in counties with
+high manufacturing job loss since 2004. Disaggregating this result by
+race shows that the Democratic vote share fell where layoffs affected
+white populations, and rose where layoffs affected nonwhites. This
+suggests a racial component to how voters process economic hardship.
 \end{abstract}
@@
 
-\section{Introduction}
+This paper analyzes the relationship between deindustrialization, race,
+and the election of Donald Trump in 2016. Previous analysis has
+frequently focused on racial animus, trade, or the conjunction of the
+two (\cite{Autor20}; \cite{che16}; \cite{BR21}). We extend the analysis
+of \cite{Baccini21}, one of the first papers to examine the effects of
+deindustrialization in a localized way. Deindustrialization - the
+transition of the U.S. economy away from manufacturing - has led to
+widespread job loss and created knock-on adverse effects in many
+formerly industrial areas. Along with \cite{Baccini21}, we find evidence
+that the experience of deindustralization was associated with support
+for Donald Trump, particularly among whites. However, we find that the
+related effects in the 2016 election are not associated with recent
+manufacturing job loss; rather, the opposite. Counties with
+manufacturing job losses from 2012-2015 tended to become more
+Democratic. We extend the analysis to the 2004-2015 period, to capture
+the long-term effects of deindustrialization on a region. Doing so, we
+find that regions experiencing more manufacturing job loss swung towards
+Donald Trump in 2016, and that this occurred more when those losing jobs
+were white.
 
-We replicate \cite{Baccini21}, which analyzes the effect of gross
-manufacturing job losses from 2012 to 2015 on the change in Democratic
-vote share in the 2016 presidential election.
-
-We extend Baccini and Weymouth's analysis by changing the quantity of
-interest from \textbf{gross} manufacturing job losses to \textbf{net}
-manufacturing job losses. For example, in Baccini and Weymouth's model,
-if a county lost 400 manufacturing jobs from 2012-2015 and also gained
-400 manufacturing jobs over the same period, they would count 400
-overall layoffs. Using our measure of \emph{net} manufacturing job
-losses, we would consider this example a 0 net change in manufacturing
-employment. Given that job destruction and creation is a natural dynamic
-within the economy (i.e.~seasonal employment, creative destruction), we
-think that \emph{net} job losses is a more meaningful measure.
-
-Using \emph{net} manufacturing job losses as our outcome, we replicate
-Baccini and Weymouth's main model, which uses 2012-2015 manufacturing
-(gross) job losses to explain the change in Democratic vote share in
-2016. Using their specifications, we find totally opposite results -
-that a \emph{net} increase in white manufacturing jobs \emph{increased}
-Democratic vote share, while a \emph{net} increase in non-white
-manufacturing jobs \emph{decreased} Democratic vote share.
-
-However, we don't think this is capturing the important dynamic at play.
-From 2012 to 2015, the national economy experienced a net increase in
-manufacturing jobs following the 2008 recession (See Figure 1). During
-this time of recovery, counties that experienced the most pronounced
-manufacturing job losses in prior years were also likely to experience
-the most pronounced recovery. Because of this v-shaped recovery,
-focusing only on 2012-2015 job losses/gains paints a distorted picture.
+Our analysis extends \cite{Baccini21} in several ways. First, we change
+focus from a measure of gross losses in manufacturing jobs to net
+losses. As discussed in \ref{datasec}, we believe this to be a more
+accurate measure of deindustrialization. Second, we change the temporal
+focus. Rather than focusing on manufacturing job loss in 2012-2015, we
+extend our analysis back to 2004. This is an important change. As shown
+XXXXXXXXXXXXXX FIGURE XXXXXXXXXXXXXXX, the bulk of U.S. manufacturing
+job loss took place prior to 2012; in fact, the 2012-2015 period was
+characterized by a slight rebound in manufacturing jobs. During this
+rebound, counties that experienced the most pronounced manufacturing job
+losses in prior years were also likely to experience the most pronounced
+recovery XXXXXXXXXXXXXXX FIGURE XXXXXXXXXXXXX. Because of this v-shaped
+recovery, focusing only on 2012-2015 job losses/gains paints a distorted
+picture. Finally, we augment the instrumental-variable approach with one
+based on covariate balancing, which produces similar results.
 
 \section{Data and Methods} 
+\label{datamethods}
 
 \subsection{Data} 
+\label{datasec}
 
@@
 turn towards Trump (a singular candidate, after all). To mitigate these
-risks, \cite{Baccini21} uses a Bartik instrument, which we adapt. This
-instrument essentially uses the cross-county distribution of
-manufacturing employment as a source of exogenous variation.
+risks, \cite{Baccini21} uses a Bartik instrument, which we adapt (see
+\cite{Bartik91}). This instrument essentially uses the cross-county
+distribution of manufacturing employment as a source of exogenous
+variation.
 
@@
 Using this instrument, we then conduct a two stage regression. First we
-estimate manufacturing job loss with the Bartik Instrument
+estimate manufacturing job loss with the Bartik Instrument and a set of
+county-level controls; then we use the estimated values of job losses to
+predict Democratic vote share. In these regressions we control for
+unemployment, service layoffs, the share of college-educated voters, and
+the share of male voters. For some estimates, we also control for the
+white share of the population. These controls are similar to those of
+\cite{Baccini21}.
+
+Our second approach involves attempting to balance the covariates of the
+deindustrialization treatment. We use the same covariates as are used in
+controls above, as well as manufacturing as share of the population and
+total population. We apply the method of Covariate Balancing Propensity
+Scores, as developed by \cite{Imai14}; this method generates weights to
+reduce the correlation between covariates and treatment, while
+addressing several of the issues with propensity score weights. Given
+covariate-balancing weights, we then conduct a single-stage weighted
+regression of change in Democratic vote share on manufacturing job loss,
+using the same controls as above.
+
+XXXXXXXXXXXXXXX BALANCE FIGURE??? XXXXXXXXXXXXXXXXXXXXXXXXXXX
+
+\subsection{Results}
+
+\subsection{Conclusion}
 
@@
 
-\% The appendix command is issued once, prior to all appendices, if any.
-\appendix
-
-\section{Mathematical Appendix}
-
 \end{document}

### 2021-12-10 Final Draft/Final Draft.Rmd
first draft of complete text

@@
 short: "Brother, Can You Spare a Manufacturing Job? "
-journal: "" # AER, AEJ, PP, JEL
 month: "`r format(Sys.Date(), '%m')`"
 year: "`r format(Sys.Date(), '%Y')`"
-vol: 1
-issue: 1
 author:
@@
 Previous analysis has frequently focused on racial animus, trade, or the conjunction of the two (\cite{Autor20}; \cite{che16}; \cite{BR21}).
-We extend the analysis of \cite{Baccini21}, one of the first papers to examine the effects of deindustrialization in a localized way.
+We extend the analysis of \cite{Baccini21}, one of the first papers to examine the political effects of deindustrialization while considering race and localization.
 Deindustrialization - the transition of the U.S.
-economy away from manufacturing - has led to widespread job loss and created knock-on adverse effects in many formerly industrial areas.
+economy away from manufacturing - has led to widespread job loss and created adverse knock-on effects for a wide swath of Americans.
+This experience has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing XXXXXXXXXXXX MAP FIGURE XXXXXXXXXXX.
+We believe the localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
+
 Along with \cite{Baccini21}, we find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites.
@@
 We extend the analysis to the 2004-2015 period, to capture the long-term effects of deindustrialization on a region.
-Doing so, we find that regions experiencing more manufacturing job loss swung towards Donald Trump in 2016, and that this occurred more when those losing jobs were white.
+Doing so, we find that regions experiencing more manufacturing job losses swung towards Donald Trump in 2016, and that this occurred more when those losing jobs were white.
 
@@
 Thus we believe the **net** job losses over a period are the more accurate measure.
+It can be argued that the non-seasonal or non-structural components of gross job losses are a useful covariate.
+Basic notions of prospect theory suggest that the loss of a job and subsequent regaining of another identical job may still create substantial discontent.
+Constructing a better measure of gross job losses is an area for further methodological and substantive research.
 
@@
 For some estimates, we also control for the white share of the population.
+We also apply state fixed effects to account for a wide variety of state-level changes from 2012-2016 (such as voter suppression tactics).
 These controls are similar to those of \cite{Baccini21}.
@@
 
-If we expand our measure of net manufacturing job losses to include the 2004 to 2011 period - which covers most of the period when the U.S.
-manufacturing economy was hit most intensely (See Figure 1) -- we get a result that corroborates the core intuition of Baccini and Weymouth (See Table 4).
-That is, we find that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased Democratic vote share.
+We find that counties experiencing deindustrialization from 2004-2015 are substantially more likely to vote for Trump.
+Further, we find that this effect is largely attributable to whites.
+In other words, net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased Democratic vote share.
+We find the same effect when using covariate balancing, albeit of reduced size.
 
-It is important to highlight the substantive importance of the *timing* of manufacturing layoffs on political outcomes.
-Whereas Baccini and Weymouth's analysis suggests that economic changes lead to immediate political consequences, our analysis shows that economic changes can have lagged and variable effects on political outcomes.
-The mechanisms of these lagged effects merit further study.
+The results can be found in XXXXXXXXXXXXX.
+The regression coefficient in Model 4, for instance, means that a loss of $10$ manufacturing jobs per $100$ workers in a county (a relatively extreme value) corresponds to a loss of $3.2 \%$ in Democratic vote share.
 
-[Note: to demonstrate our point about **variable** effects, In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in Democratic vote share in other elections (2012 and 2020).]
+This coefficient is still somewhat difficult to interpret, and made increasingly so by the winner-take-all system by which U.S.
+Electoral College votes are allocated.
+As an alternative perspective, we examined a range of counterfactual scenarios, in which counties experienced job losses
+
+XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL
+
+\subsubsection{Timing}
+
+Restricting our analysis to only the 2012-2015 period produces an opposite effect, in contrast to \cite{BW21} (when we use a net job loss metric).
+The loss of Democratic vote share seems to be associated with a gain in manufacturing jobs, both in general and among whites.
+We believe this time-restricted analysis suffers from an omitted variable bias.
+As discussed above, the 2012-2015 period can be broadly characterized as a slight rebound from the manufacturing job losses in the 2008 financial crisis.
+The counties that experience job losses from 2004-2012 are more likely to have job gains in 2012-2015.
+An apparent relationship between 2012-2015 job gains and loss of Democratic vote share in fact represents 2004-2012 job losses that may lead to both the later job gains and the loss of vote share.
+XXXXXXXXXXXXX FIGURE XXXXXXXXXXXX
+
+This result suggests an important temporal dimension to the political effects of deindustrialization - job losses in 2004-2012 make their effects felt in 2016.
+In some ways, this result is more plausible than if the 2012-2015 job losses were a significant covariate of voting.
+The effects of job loss may take some time to be felt, at both individual and community levels (see XXXXXXXXXXXXXX CITE).
+The mechanisms of this relationship make a good topic for subsequent research.
 
@@
 
-Sample figure:
+As much research has noted, the national and global implications of American  deindustrialization are only beginning to be felt - from the 2016 election to isolationism to the opioid epidemic.
+Previous analyses have often focused on choosing between explanations grounded in racial issues or political-economic evolutions XXXXXXXXXXXXXXXXXXXXXxxx CITE.
+We are joining a growing body of scholars searching for explanations at the intersection of the two.
+We believe that deindustrialization is fundamentally connected to particular places, and so the localized approach adopted by \cite{BW21} offers a great deal of promise.
+Further research might explore further ways in which geography has influenced the rightward turn in the U.S., for example through the use of techniques of spatial econometrics or the careful use of ethnography.
 
-American Economic Review Pointers:
-
-\begin{itemize}
-\item Do not use an "Introduction" heading. Begin your introductory material
-before the first section heading.
-
-\item Avoid style markup (except sparingly for emphasis).
-
-\item Avoid using explicit vertical or horizontal space.
-
-\item Captions are short and go below figures but above tables.
-
-\item The tablenotes or figurenotes environments may be used below tables
-or figures, respectively, as demonstrated below.
-
-\item If you have difficulties with the mathtime package, adjust the package
-options appropriately for your platform. If you can't get it to work, just
-remove the package or see our technical support document online (please
-refer to the author instructions).
-
-\item If you are using an appendix, it goes last, after the bibliography.
-Use regular section headings to make the appendix headings.
-
-\item If you are not using an appendix, you may delete the appendix command
-and sample appendix section heading.
-
-\item Either the natbib package or the harvard package may be used with bibtex.
-To include one of these packages, uncomment the appropriate usepackage command
-above. Note: you can't use both packages at once or compile-time errors will result.
-
-\end{itemize}
-
-\section{First Section in Body}
-
-Sample figure:
+While our study is oriented towards history, deindustrialization is in no way confined to the past.
+The trajectory of American manufacturing employment is far from certain, with continued competition from abroad and the perennial threat of unemployment.
+We believe the case of the U.S.
+also offers insight that is applicable to the phenomenon of 'premature deindustrialization' in the developing world, and the concurrent growth of populist parties in Hungary, Brazil, India and elsewhere.
+XXXXXXXXXXXXXXX CITE XXXXXXxx
 
@@
 
-Sample table:
-
-\begin{table}
-\caption{Caption for table above.}
-
-\begin{tabular}{lll}
-& Heading 1 & Heading 2 \\
-Row 1 & 1 & 2 \\
-Row 2 & 3 & 4%
-\end{tabular}
-\begin{tablenotes}
-Table notes environment without optional leadin.
-\end{tablenotes}
-\begin{tablenotes}[Source]
-Table notes environment with optional leadin (Source, in this case).
-\end{tablenotes}
-\end{table}
-
-References here (manual or bibTeX). If you are using bibTeX, add your bib file
-name in place of BibFile in the bibliography command.
-% Remove or comment out the next two lines if you are not using bibtex.
+\nocite{stargazer}
 \bibliographystyle{aea}

### 2021-12-10 Final Draft/Final-Draft.tex
first draft of complete text

@@
   Zagreb Mukerjee\thanks{
-  Darin: Harvard
-University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
-  Mukerjee: Harvard
-University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
+  Darin: Harvard University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
+  Mukerjee: Harvard University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
 }
@@
 \pubYear{2021}
-\pubVolume{1}
-\pubIssue{1}
+\pubVolume{}
+\pubIssue{}
 \JEL{}
@@
 two (\cite{Autor20}; \cite{che16}; \cite{BR21}). We extend the analysis
-of \cite{Baccini21}, one of the first papers to examine the effects of
-deindustrialization in a localized way. Deindustrialization - the
-transition of the U.S. economy away from manufacturing - has led to
-widespread job loss and created knock-on adverse effects in many
-formerly industrial areas. Along with \cite{Baccini21}, we find evidence
-that the experience of deindustralization was associated with support
-for Donald Trump, particularly among whites. However, we find that the
-related effects in the 2016 election are not associated with recent
-manufacturing job loss; rather, the opposite. Counties with
-manufacturing job losses from 2012-2015 tended to become more
-Democratic. We extend the analysis to the 2004-2015 period, to capture
-the long-term effects of deindustrialization on a region. Doing so, we
-find that regions experiencing more manufacturing job loss swung towards
-Donald Trump in 2016, and that this occurred more when those losing jobs
-were white.
+of \cite{Baccini21}, one of the first papers to examine the political
+effects of deindustrialization while considering race and localization.
+Deindustrialization - the transition of the U.S. economy away from
+manufacturing - has led to widespread job loss and created adverse
+knock-on effects for a wide swath of Americans. This experience has not
+been uniform; rather, it has been concentrated in certain areas of the
+country that were previously economically reliant on manufacturing
+XXXXXXXXXXXX MAP FIGURE XXXXXXXXXXX. We believe the localized nature of
+this analysis highlights the uneven and concentrated harms of
+deindustrialization.
+
+Along with \cite{Baccini21}, we find evidence that the experience of
+deindustralization was associated with support for Donald Trump,
+particularly among whites. However, we find that the related effects in
+the 2016 election are not associated with recent manufacturing job loss;
+rather, the opposite. Counties with manufacturing job losses from
+2012-2015 tended to become more Democratic. We extend the analysis to
+the 2004-2015 period, to capture the long-term effects of
+deindustrialization on a region. Doing so, we find that regions
+experiencing more manufacturing job losses swung towards Donald Trump in
+2016, and that this occurred more when those losing jobs were white.
 
@@
 believe the \textbf{net} job losses over a period are the more accurate
-measure.
+measure. It can be argued that the non-seasonal or non-structural
+components of gross job losses are a useful covariate. Basic notions of
+prospect theory suggest that the loss of a job and subsequent regaining
+of another identical job may still create substantial discontent.
+Constructing a better measure of gross job losses is an area for further
+methodological and substantive research.
 
@@
 the share of male voters. For some estimates, we also control for the
-white share of the population. These controls are similar to those of
+white share of the population. We also apply state fixed effects to
+account for a wide variety of state-level changes from 2012-2016 (such
+as voter suppression tactics). These controls are similar to those of
 \cite{Baccini21}.
@@
 
+We find that counties experiencing deindustrialization from 2004-2015
+are substantially more likely to vote for Trump. Further, we find that
+this effect is largely attributable to whites. In other words, net white
+manufacturing job losses decreased Democratic vote share, while net
+non-white manufacturing job losses increased Democratic vote share. We
+find the same effect when using covariate balancing, albeit of reduced
+size.
+
+The results can be found in XXXXXXXXXXXXX. The regression coefficient in
+Model 4, for instance, means that a loss of \(10\) manufacturing jobs
+per \(100\) workers in a county (a relatively extreme value) corresponds
+to a loss of \(3.2 \%\) in Democratic vote share.
+
+This coefficient is still somewhat difficult to interpret, and made
+increasingly so by the winner-take-all system by which U.S. Electoral
+College votes are allocated. As an alternative perspective, we examined
+a range of counterfactual scenarios, in which counties experienced job
+losses
+
+XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL
+
+\subsubsection{Timing}
+
+Restricting our analysis to only the 2012-2015 period produces an
+opposite effect, in contrast to \cite{BW21} (when we use a net job loss
+metric). The loss of Democratic vote share seems to be associated with a
+gain in manufacturing jobs, both in general and among whites. We believe
+this time-restricted analysis suffers from an omitted variable bias. As
+discussed above, the 2012-2015 period can be broadly characterized as a
+slight rebound from the manufacturing job losses in the 2008 financial
+crisis. The counties that experience job losses from 2004-2012 are more
+likely to have job gains in 2012-2015. An apparent relationship between
+2012-2015 job gains and loss of Democratic vote share in fact represents
+2004-2012 job losses that may lead to both the later job gains and the
+loss of vote share. XXXXXXXXXXXXX FIGURE XXXXXXXXXXXX
+
+This result suggests an important temporal dimension to the political
+effects of deindustrialization - job losses in 2004-2012 make their
+effects felt in 2016. In some ways, this result is more plausible than
+if the 2012-2015 job losses were a significant covariate of voting. The
+effects of job loss may take some time to be felt, at both individual
+and community levels (see XXXXXXXXXXXXXX CITE). The mechanisms of this
+relationship make a good topic for subsequent research.
+
 \subsection{Conclusion}
 
-If we expand our measure of net manufacturing job losses to include the
-2004 to 2011 period - which covers most of the period when the U.S.
-manufacturing economy was hit most intensely (See Figure 1) -- we get a
-result that corroborates the core intuition of Baccini and Weymouth (See
-Table 4). That is, we find that net white manufacturing job losses
-decreased Democratic vote share, while net non-white manufacturing job
-losses increased Democratic vote share.
+As much research has noted, the national and global implications of
+American deindustrialization are only beginning to be felt - from the
+2016 election to isolationism to the opioid epidemic. Previous analyses
+have often focused on choosing between explanations grounded in racial
+issues or political-economic evolutions XXXXXXXXXXXXXXXXXXXXXxxx CITE.
+We are joining a growing body of scholars searching for explanations at
+the intersection of the two. We believe that deindustrialization is
+fundamentally connected to particular places, and so the localized
+approach adopted by \cite{BW21} offers a great deal of promise. Further
+research might explore further ways in which geography has influenced
+the rightward turn in the U.S., for example through the use of
+techniques of spatial econometrics or the careful use of ethnography.
 
-It is important to highlight the substantive importance of the
-\emph{timing} of manufacturing layoffs on political outcomes. Whereas
-Baccini and Weymouth's analysis suggests that economic changes lead to
-immediate political consequences, our analysis shows that economic
-changes can have lagged and variable effects on political outcomes. The
-mechanisms of these lagged effects merit further study.
-
-{[}Note: to demonstrate our point about \textbf{variable} effects, In
-our next iteration of the analysis, we will show that manufacturing job
-losses had little explanatory effect on changes in Democratic vote share
-in other elections (2012 and 2020).{]}
-
-Sample figure:
-
-American Economic Review Pointers:
-
-\begin{itemize}
-\item Do not use an "Introduction" heading. Begin your introductory material
-before the first section heading.
-
-\item Avoid style markup (except sparingly for emphasis).
-
-\item Avoid using explicit vertical or horizontal space.
-
-\item Captions are short and go below figures but above tables.
-
-\item The tablenotes or figurenotes environments may be used below tables
-or figures, respectively, as demonstrated below.
-
-\item If you have difficulties with the mathtime package, adjust the package
-options appropriately for your platform. If you can't get it to work, just
-remove the package or see our technical support document online (please
-refer to the author instructions).
-
-\item If you are using an appendix, it goes last, after the bibliography.
-Use regular section headings to make the appendix headings.
-
-\item If you are not using an appendix, you may delete the appendix command
-and sample appendix section heading.
-
-\item Either the natbib package or the harvard package may be used with bibtex.
-To include one of these packages, uncomment the appropriate usepackage command
-above. Note: you can't use both packages at once or compile-time errors will result.
-
-\end{itemize}
-
-\section{First Section in Body}
-
-Sample figure:
+While our study is oriented towards history, deindustrialization is in
+no way confined to the past. The trajectory of American manufacturing
+employment is far from certain, with continued competition from abroad
+and the perennial threat of unemployment. We believe the case of the
+U.S. also offers insight that is applicable to the phenomenon of
+`premature deindustrialization' in the developing world, and the
+concurrent growth of populist parties in Hungary, Brazil, India and
+elsewhere. XXXXXXXXXXXXXXX CITE XXXXXXxx
 
@@
 
-Sample table:
-
-\begin{table}
-\caption{Caption for table above.}
-
-\begin{tabular}{lll}
-& Heading 1 & Heading 2 \\
-Row 1 & 1 & 2 \\
-Row 2 & 3 & 4%
-\end{tabular}
-\begin{tablenotes}
-Table notes environment without optional leadin.
-\end{tablenotes}
-\begin{tablenotes}[Source]
-Table notes environment with optional leadin (Source, in this case).
-\end{tablenotes}
-\end{table}
-
-References here (manual or bibTeX). If you are using bibTeX, add your
-bib file name in place of BibFile in the bibliography command. \% Remove
-or comment out the next two lines if you are not using bibtex.
+\nocite{stargazer}
 

### 2021-12-10 Final Draft/Final Draft.Rmd
typo fix

@@
 While our study is oriented towards history, deindustrialization is in no way confined to the past.
-The trajectory of American manufacturing employment is far from certain, with continued competition from abroad and the perennial threat of unemployment.
+The trajectory of American manufacturing employment is far from certain, with continued competition from abroad and the perennial threat of automation.
 We believe the case of the U.S.
 also offers insight that is applicable to the phenomenon of 'premature deindustrialization' in the developing world, and the concurrent growth of populist parties in Hungary, Brazil, India and elsewhere.
-XXXXXXXXXXXXXXX CITE XXXXXXxx
+XXXXXXXXXXXXXXX CITES XXXXXXxx
 

### 2021-12-10 Final Draft/Final Draft.Rmd
adding figures and text

@@
     affiliation: Harvard University
-acknowledgements: 
+acknowledgements: | 
+  Code available at https://github.com/zagrebmukerjee/ReplicationPaper
 abstract: |
@@
 output: rticles::aea_article
+header-includes: 
+ - \usepackage{graphicx}
+ - \usepackage{amsmath}
+ - \usepackage{amssymb}
 ---
 
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
+
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+library(rticles)
+library(tidyverse)
+library(stargazer)
+library(sandwich)
+library(lmtest)
+library(knitr)
+library(kableExtra)
+library(readxl)
+library(scales)
+library(tigris)
+
+knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
+```
+
 This paper analyzes the relationship between deindustrialization, race, and the election of Donald Trump in 2016.
-Previous analysis has frequently focused on racial animus, trade, or the conjunction of the two (\cite{Autor20}; \cite{che16}; \cite{BR21}).
+Previous analysis has frequently focused on racial animus, trade, or the conjunction of the two (\cite{Autor20}; \cite{Che16}; \cite{BR21}).
 We extend the analysis of \cite{Baccini21}, one of the first papers to examine the political effects of deindustrialization while considering race and localization.
@@
 economy away from manufacturing - has led to widespread job loss and created adverse knock-on effects for a wide swath of Americans.
-This experience has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing XXXXXXXXXXXX MAP FIGURE XXXXXXXXXXX.
+This incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
+The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing XXXXXXXXXXXX MAP FIGURE XXXXXXXXXXX.
 We believe the localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
@@
 This is an important change.
-As shown XXXXXXXXXXXXXX FIGURE XXXXXXXXXXXXXXX, the bulk of U.S.
+As shown in Figure \ref{natlPlot}, the bulk of U.S.
 manufacturing job loss took place prior to 2012; in fact, the 2012-2015 period was characterized by a slight rebound in manufacturing jobs.
-During this rebound, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery XXXXXXXXXXXXXXX FIGURE XXXXXXXXXXXXX.
+During this rebound, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery, as described in Figure \ref{vShapePlot}.
 Because of this v-shaped recovery, focusing only on 2012-2015 job losses/gains paints a distorted picture.
 Finally, we augment the instrumental-variable approach with one based on covariate balancing, which produces similar results.
+
+\begin{figure} \label{natlPlot}
+\caption{Nationwide Change in Manufacturing Employment, 1995-2019}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+# manufacturing layoffs over time
+
+national_ts <- read_xlsx("../National_Data_TS.xlsx")
+
+national_ts <- national_ts %>%
+  rename(year = 1,
+         net_job_change = 2) %>%
+  dplyr::select(year, net_job_change) %>%
+  rename(Year = year, `Job Change per Worker` = net_job_change) %>%
+  mutate(
+    Year = as.numeric(Year),
+    `Job Change per Worker` = `Job Change per Worker`*4) %>% group_by()
+
+ggplot(data = national_ts %>% filter(Year >= 1995),
+       aes(x = Year, y = `Job Change per Worker`)) +
+  ylab("Millions of Jobs") +
+  geom_col(fill = "#4287f5") + scale_x_continuous(breaks=seq(1995,2020,5)) +
+	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6)) +
+  theme_classic() +
+  theme(title = element_text(size = 8, hjust = .5),
+        axis.title.x = element_text(size = 8), 
+        axis.title.y = element_text(size = 8))
+
+```
+
+\begin{figurenotes}
+Gain or loss of national manufacturing jobs, divided by total national workforce.
+\end{figurenotes}
+\end{figure}
+
+\begin{figure} \label{vShapePlot}
+\caption{}
+
+\begin{figurenotes}
+Figure notes without optional leadin.
+\end{figurenotes}
+\end{figure}
 
@@
 XXXXXXXXXXXXXXXX sources of other data
+
+Basic descriptive statistics of job losses and other key covariates can be seen in Table \ref{tab:descTable}.
+
+```{r,  echo=F}
+descriptiveData <-  readRDS("../tableData.rds")
+
+knitr::kable(descriptiveData$table04,
+             caption = "Manufacturing Job Changes 2004-2015",label = "descTable",
+             booktabs = TRUE, digits = 2, format = 'latex')  %>%
+  kable_styling(latex_options = c("hold_position", "scale_down"))
+
+```
 
@@
 
-The results can be found in XXXXXXXXXXXXX.
+The results can be found in Table \ref{regResult04}.
 The regression coefficient in Model 4, for instance, means that a loss of $10$ manufacturing jobs per $100$ workers in a county (a relatively extreme value) corresponds to a loss of $3.2 \%$ in Democratic vote share.
+
+```{r,  echo=F, message = F, results = "asis"}
+
+regResultList <- readRDS("../regresults.rds")
+
+rownames(regResultList$secondStageModelNetC04A$coefficients )[rownames(regResultList$secondStageModelNetC04A$coefficients)=="firstStageModelOurs04_2$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC04$coefficients )[rownames(regResultList$secondStageModelNetC04$coefficients)=="firstStageModelOurs04_3$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04A$coefficients )[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="firstStageModelOurs04_5$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$coefficients )[rownames(regResultList$secondStageModelWNetC04$coefficients)=="firstStageModelOurs04_6$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetC04A$coefficients
+)[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$coefficients
+)[rownames(regResultList$secondStageModelWNetC04$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelNetC04A$beta )[rownames(regResultList$secondStageModelNetC04A$beta) =="firstStageModelOurs04_2$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC04$beta )[rownames(regResultList$secondStageModelNetC04$beta)=="firstStageModelOurs04_3$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="firstStageModelOurs04_5$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="firstStageModelOurs04_6$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+names(regResultList$rseNetC04A_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseNetC04_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseWNetC04A_2)[1] <- "White Manufacturing Layoffs"
+names(regResultList$rseWNetC04_2)[1] <- "White Manufacturing Layoffs"
+
+names(regResultList$rseWNetC04A_2)[names(regResultList$rseWNetC04A_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+names(regResultList$rseWNetC04_2)[names(regResultList$rseWNetC04_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+
+stargazer(regResultList$secondStageModelNetC04A,
+          regResultList$secondStageModelNetC04,
+          regResultList$secondStageModelWNetC04A,
+          regResultList$secondStageModelWNetC04,
+          se = list(
+            regResultList$rseNetC04A_2,
+            regResultList$rseNetC04_2,
+            regResultList$rseWNetC04A_2,
+            regResultList$rseWNetC04_2
+          ),
+          title = "Effect of Manufacturing Job Loss from 2004 to 2015",
+          dep.var.labels = "Change in Dem. Share, 2016-2012",
+          omit.stat = c("rsq","ser"),
+          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
+          add.lines = list(
+            c("White Share/Svc Layoffs Control", "No", "Yes", "No", "Yes")
+          ),
+          digits = 2,
+          header = F,
+          type = "latex",
+          label = "regResult04"
+)
+
+```
 
@@
 
-Restricting our analysis to only the 2012-2015 period produces an opposite effect, in contrast to \cite{BW21} (when we use a net job loss metric).
+Restricting our analysis to only the 2012-2015 period, while continuing to use the net job loss metric, produces an effect opposite to that of \cite{Baccini21}.
 The loss of Democratic vote share seems to be associated with a gain in manufacturing jobs, both in general and among whites.
@@
 As discussed above, the 2012-2015 period can be broadly characterized as a slight rebound from the manufacturing job losses in the 2008 financial crisis.
-The counties that experience job losses from 2004-2012 are more likely to have job gains in 2012-2015.
+The counties that experience job losses from 2004-2012 are more likely to have job gains in 2012-2015 (see \ref{vShapePlot}).
 An apparent relationship between 2012-2015 job gains and loss of Democratic vote share in fact represents 2004-2012 job losses that may lead to both the later job gains and the loss of vote share.
-XXXXXXXXXXXXX FIGURE XXXXXXXXXXXX
+These results can be seen in Table \ref{regResult12}.
+
+```{r,  echo=F, message = F, results = "asis"}
+
+rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetCA$coefficients 
+)[rownames(regResultList$secondStageModelWNetCA$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$coefficients
+)[rownames(regResultList$secondStageModelWNetC$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"
+
+rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+
+names(regResultList$rseNetCA_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseNetC_2)[1] <- "Manufacturing Layoffs"
+names(regResultList$rseWNetCA_2)[1] <- "White Manufacturing Layoffs"
+names(regResultList$rseWNetC_2)[1] <- "White Manufacturing Layoffs"
+
+names(regResultList$rseWNetCA_2)[names(regResultList$rseWNetCA_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+names(regResultList$rseWNetC_2)[names(regResultList$rseWNetC_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+
+stargazer(regResultList$secondStageModelNetCA,
+          regResultList$secondStageModelNetC,
+          regResultList$secondStageModelWNetCA,
+          regResultList$secondStageModelWNetC,
+          se = list(
+            regResultList$rseNetCA_2,
+            regResultList$rseNetC_2,
+            regResultList$rseWNetCA_2,
+            regResultList$rseWNetC_2
+          ),
+          title = "Effect of Manufacturing Job Loss from 2004 to 2015",
+          dep.var.labels = "Change in Dem. Share, 2016-2012",
+          omit.stat = c("rsq","ser"),
+          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
+          add.lines = list(
+            c("White Share/Svc Layoffs Control", "No", "Yes", "No", "Yes")
+          ),
+          digits = 2,
+          header = F,
+          type = "latex",
+          label = "regResult12"
+)
+
+```
 
@@
 In some ways, this result is more plausible than if the 2012-2015 job losses were a significant covariate of voting.
-The effects of job loss may take some time to be felt, at both individual and community levels (see XXXXXXXXXXXXXX CITE).
+The effects of job loss may take some time to be felt, at both individual and community levels (see \cite{Mckee09}, \cite{Foote19}).
 The mechanisms of this relationship make a good topic for subsequent research.
@@
 As much research has noted, the national and global implications of American  deindustrialization are only beginning to be felt - from the 2016 election to isolationism to the opioid epidemic.
-Previous analyses have often focused on choosing between explanations grounded in racial issues or political-economic evolutions XXXXXXXXXXXXXXXXXXXXXxxx CITE.
+Previous analyses have often focused on choosing between explanations grounded in racial issues or political-economic evolutions (ex: \cite{Green19}, \cite{Reny19}).
 We are joining a growing body of scholars searching for explanations at the intersection of the two.
-We believe that deindustrialization is fundamentally connected to particular places, and so the localized approach adopted by \cite{BW21} offers a great deal of promise.
+We believe that deindustrialization is fundamentally connected to particular places, and so the localized approach adopted by \cite{Baccini21} offers a great deal of promise.
 Further research might explore further ways in which geography has influenced the rightward turn in the U.S., for example through the use of techniques of spatial econometrics or the careful use of ethnography.
@@
 We believe the case of the U.S.
-also offers insight that is applicable to the phenomenon of 'premature deindustrialization' in the developing world, and the concurrent growth of populist parties in Hungary, Brazil, India and elsewhere.
-XXXXXXXXXXXXXXX CITES XXXXXXxx
+also offers insight that is applicable to the phenomenon of 'premature deindustrialization' in the developing world, and the concurrent growth of populist parties in Hungary, Brazil, India and elsewhere (\cite{Rodrik15}, \cite{Castillo16}).
 
-\begin{figure}
+\begin{figure} \label{}
+\caption{Caption for figure below.}
 
-\caption{Caption for figure below.}
 \begin{figurenotes}
@@
 
-\nocite{stargazer}
+\nocite{Stargazer}
 \bibliographystyle{aea}

### 2021-12-10 Final Draft/Final-Draft.tex
adding figures and text

@@
 
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
 \usepackage{hyperref}
@@
   Zagreb Mukerjee\thanks{
-  Darin: Harvard University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
-  Mukerjee: Harvard University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
+  Darin: Harvard
+University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
+  Mukerjee: Harvard
+University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
+  Code available at https://github.com/zagrebmukerjee/ReplicationPaper
 }
@@
 frequently focused on racial animus, trade, or the conjunction of the
-two (\cite{Autor20}; \cite{che16}; \cite{BR21}). We extend the analysis
+two (\cite{Autor20}; \cite{Che16}; \cite{BR21}). We extend the analysis
 of \cite{Baccini21}, one of the first papers to examine the political
@@
 manufacturing - has led to widespread job loss and created adverse
-knock-on effects for a wide swath of Americans. This experience has not
-been uniform; rather, it has been concentrated in certain areas of the
-country that were previously economically reliant on manufacturing
-XXXXXXXXXXXX MAP FIGURE XXXXXXXXXXX. We believe the localized nature of
-this analysis highlights the uneven and concentrated harms of
-deindustrialization.
+knock-on effects for a wide swath of Americans. This incorporates job
+losses due to trade with China and others (see \cite{Acemoglu16}); it
+also includes job losses due to automation, demand changes, and other
+factors. The experience of deindustrialization has not been uniform;
+rather, it has been concentrated in certain areas of the country that
+were previously economically reliant on manufacturing XXXXXXXXXXXX MAP
+FIGURE XXXXXXXXXXX. We believe the localized nature of this analysis
+highlights the uneven and concentrated harms of deindustrialization.
 
@@
 extend our analysis back to 2004. This is an important change. As shown
-XXXXXXXXXXXXXX FIGURE XXXXXXXXXXXXXXX, the bulk of U.S. manufacturing
-job loss took place prior to 2012; in fact, the 2012-2015 period was
-characterized by a slight rebound in manufacturing jobs. During this
-rebound, counties that experienced the most pronounced manufacturing job
-losses in prior years were also likely to experience the most pronounced
-recovery XXXXXXXXXXXXXXX FIGURE XXXXXXXXXXXXX. Because of this v-shaped
-recovery, focusing only on 2012-2015 job losses/gains paints a distorted
-picture. Finally, we augment the instrumental-variable approach with one
-based on covariate balancing, which produces similar results.
+in Figure \ref{natlPlot}, the bulk of U.S. manufacturing job loss took
+place prior to 2012; in fact, the 2012-2015 period was characterized by
+a slight rebound in manufacturing jobs. During this rebound, counties
+that experienced the most pronounced manufacturing job losses in prior
+years were also likely to experience the most pronounced recovery, as
+described in Figure \ref{vShapePlot}. Because of this v-shaped recovery,
+focusing only on 2012-2015 job losses/gains paints a distorted picture.
+Finally, we augment the instrumental-variable approach with one based on
+covariate balancing, which produces similar results.
+
+\begin{figure} \label{natlPlot}
+\caption{Nationwide Change in Manufacturing Employment, 1995-2019}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-2-1} \end{center}
+
+\begin{figurenotes}
+Gain or loss of national manufacturing jobs, divided by total national workforce.
+\end{figurenotes}
+\end{figure}
+
+\begin{figure} \label{vShapePlot}
+\caption{}
+
+\begin{figurenotes}
+Figure notes without optional leadin.
+\end{figurenotes}
+\end{figure}
 
@@
 XXXXXXXXXXXXXXXX sources of other data
+
+Basic descriptive statistics of job losses and other key covariates can
+be seen in Table \ref{tab:descTable}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:descTable}Manufacturing Job Changes 2004-2015}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{lrrrrr}
+\toprule
+  & Mean & Std Dev & 25th Pctile & Median & 75th Pctile\\
+\midrule
+Mfg Share of Emp & 0.20 & 0.15 & 0.09 & 0.17 & 0.29\\
+Mfg Share of Emp (White) & 0.16 & 0.13 & 0.06 & 0.13 & 0.22\\
+Mfg Share of Emp (Nonwhite) & 0.05 & 0.07 & 0.01 & 0.02 & 0.06\\
+Change in Mfg Jobs/ Worker & 0.04 & 0.09 & -0.01 & 0.02 & 0.06\\
+Change in Mfg Jobs/ Worker (W) & 0.03 & 0.07 & 0.00 & 0.02 & 0.06\\
+\addlinespace
+Change in Mfg Jobs/ Worker (NW) & 0.00 & 0.04 & -0.01 & 0.00 & 0.01\\
+\bottomrule
+\end{tabular}}
+\end{table}
 
@@
 
-The results can be found in XXXXXXXXXXXXX. The regression coefficient in
-Model 4, for instance, means that a loss of \(10\) manufacturing jobs
-per \(100\) workers in a county (a relatively extreme value) corresponds
-to a loss of \(3.2 \%\) in Democratic vote share.
+The results can be found in Table \ref{regResult04}. The regression
+coefficient in Model 4, for instance, means that a loss of \(10\)
+manufacturing jobs per \(100\) workers in a county (a relatively extreme
+value) corresponds to a loss of \(3.2 \%\) in Democratic vote share.
+
+\begin{table}[!htbp] \centering 
+  \caption{Effect of Manufacturing Job Loss from 2004 to 2015} 
+  \label{regResult04} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Change in Dem. Share, 2016-2012} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Manufacturing Layoffs & $-$0.34$^{**}$ & $-$0.38$^{**}$ &  &  \\ 
+  & (0.14) & (0.17) &  &  \\ 
+  & & & & \\ 
+ White Manufacturing Layoffs &  &  & $-$0.23$^{***}$ & $-$0.32$^{***}$ \\ 
+  &  &  & (0.08) & (0.10) \\ 
+  & & & & \\ 
+ Nonwhite Manufacturing Layoffs &  &  & 0.15$^{***}$ & 0.20$^{***}$ \\ 
+  &  &  & (0.05) & (0.06) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+White Share/Svc Layoffs Control & No & Yes & No & Yes \\ 
+Observations & 3,049 & 3,049 & 2,750 & 2,750 \\ 
+Adjusted R$^{2}$ & 0.72 & 0.72 & 0.75 & 0.75 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 
@@
 
-Restricting our analysis to only the 2012-2015 period produces an
-opposite effect, in contrast to \cite{BW21} (when we use a net job loss
-metric). The loss of Democratic vote share seems to be associated with a
-gain in manufacturing jobs, both in general and among whites. We believe
-this time-restricted analysis suffers from an omitted variable bias. As
-discussed above, the 2012-2015 period can be broadly characterized as a
-slight rebound from the manufacturing job losses in the 2008 financial
-crisis. The counties that experience job losses from 2004-2012 are more
-likely to have job gains in 2012-2015. An apparent relationship between
-2012-2015 job gains and loss of Democratic vote share in fact represents
-2004-2012 job losses that may lead to both the later job gains and the
-loss of vote share. XXXXXXXXXXXXX FIGURE XXXXXXXXXXXX
+Restricting our analysis to only the 2012-2015 period, while continuing
+to use the net job loss metric, produces an effect opposite to that of
+\cite{Baccini21}. The loss of Democratic vote share seems to be
+associated with a gain in manufacturing jobs, both in general and among
+whites. We believe this time-restricted analysis suffers from an omitted
+variable bias. As discussed above, the 2012-2015 period can be broadly
+characterized as a slight rebound from the manufacturing job losses in
+the 2008 financial crisis. The counties that experience job losses from
+2004-2012 are more likely to have job gains in 2012-2015 (see
+\ref{vShapePlot}). An apparent relationship between 2012-2015 job gains
+and loss of Democratic vote share in fact represents 2004-2012 job
+losses that may lead to both the later job gains and the loss of vote
+share. These results can be seen in Table \ref{regResult12}.
+
+\begin{table}[!htbp] \centering 
+  \caption{Effect of Manufacturing Job Loss from 2004 to 2015} 
+  \label{regResult12} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Change in Dem. Share, 2016-2012} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Manufacturing Layoffs & 0.43$^{**}$ & 0.37$^{**}$ &  &  \\ 
+  & (0.17) & (0.17) &  &  \\ 
+  & & & & \\ 
+ White Manufacturing Layoffs &  &  & 6.50$^{***}$ & 2.33$^{***}$ \\ 
+  &  &  & (2.20) & (0.76) \\ 
+  & & & & \\ 
+ Nonwhite Manufacturing Layoffs &  &  & $-$3.99$^{***}$ & $-$1.42$^{***}$ \\ 
+  &  &  & (1.36) & (0.47) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+White Share/Svc Layoffs Control & No & Yes & No & Yes \\ 
+Observations & 3,064 & 3,064 & 2,765 & 2,765 \\ 
+Adjusted R$^{2}$ & 0.73 & 0.73 & 0.75 & 0.75 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 
@@
 effects of job loss may take some time to be felt, at both individual
-and community levels (see XXXXXXXXXXXXXX CITE). The mechanisms of this
-relationship make a good topic for subsequent research.
+and community levels (see \cite{Mckee09}, \cite{Foote19}). The
+mechanisms of this relationship make a good topic for subsequent
+research.
 
@@
 have often focused on choosing between explanations grounded in racial
-issues or political-economic evolutions XXXXXXXXXXXXXXXXXXXXXxxx CITE.
-We are joining a growing body of scholars searching for explanations at
-the intersection of the two. We believe that deindustrialization is
-fundamentally connected to particular places, and so the localized
-approach adopted by \cite{BW21} offers a great deal of promise. Further
-research might explore further ways in which geography has influenced
-the rightward turn in the U.S., for example through the use of
-techniques of spatial econometrics or the careful use of ethnography.
+issues or political-economic evolutions (ex: \cite{Green19},
+\cite{Reny19}). We are joining a growing body of scholars searching for
+explanations at the intersection of the two. We believe that
+deindustrialization is fundamentally connected to particular places, and
+so the localized approach adopted by \cite{Baccini21} offers a great
+deal of promise. Further research might explore further ways in which
+geography has influenced the rightward turn in the U.S., for example
+through the use of techniques of spatial econometrics or the careful use
+of ethnography.
 
@@
 employment is far from certain, with continued competition from abroad
-and the perennial threat of unemployment. We believe the case of the
-U.S. also offers insight that is applicable to the phenomenon of
-`premature deindustrialization' in the developing world, and the
-concurrent growth of populist parties in Hungary, Brazil, India and
-elsewhere. XXXXXXXXXXXXXXX CITE XXXXXXxx
+and the perennial threat of automation. We believe the case of the U.S.
+also offers insight that is applicable to the phenomenon of `premature
+deindustrialization' in the developing world, and the concurrent growth
+of populist parties in Hungary, Brazil, India and elsewhere
+(\cite{Rodrik15}, \cite{Castillo16}).
 
-\begin{figure}
+\begin{figure} \label{}
+\caption{Caption for figure below.}
 
-\caption{Caption for figure below.}
 \begin{figurenotes}
@@
 
-\nocite{stargazer}
+\nocite{Stargazer}
 

### 2021-12-11 Final Draft/Final Draft.Rmd
updates to final draft

@@
 This incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
-The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing XXXXXXXXXXXX MAP FIGURE XXXXXXXXXXX.
+The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing, as demonstrated in Figure \ref{ManuMap}.
 We believe the localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
@@
 Finally, we augment the instrumental-variable approach with one based on covariate balancing, which produces similar results.
+
+\begin{figure} \label{ManuMap}
+\caption{Net Change in Manufacturing Employment from 2004 to 2015}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+# load map
+model_input <- readRDS("../model_5_input.rds")
+
+# state shapefile
+county_shape <- counties(
+  cb = TRUE,
+  resolution = "20m",
+  progress_bar = F
+) %>%
+  shift_geometry() %>%
+  mutate(STATEFP = as.numeric(STATEFP),
+         COUNTYFP = as.numeric(COUNTYFP))
+
+state_shape <- states(
+  cb = TRUE,
+  resolution = "20m",
+  progress_bar = F
+) %>%
+  filter(GEOID != "72" & GEOID != "02", GEOID != "15")
+
+# group counties into sextiles
+model_input <- model_input %>%
+  group_by() %>%
+  mutate(ntile_mfg = as.character(ntile(mfgNetChange_total , 6)))
+
+# find cutoffs
+
+sum <- model_input %>%
+  group_by(ntile_mfg) %>%
+  summarize(min = min(mfgNetChange_total),
+            max = max(mfgNetChange_total))
+
+labels = c(
+  "1" = "1% or Greater Gain",
+  "2" = "0% to 1% Gain",
+  "3" = "0% to 1% Loss",
+  "4" = "1% to 3% Loss",
+  "5" = "3% to 6% Loss",
+  "6" = "6% or Greater Loss")
+
+colors <- c("1" = "#778868",
+            "2" = "#b5b991",
+            "3" = "#f6edbd",
+            "4" = "#edbb8a",
+            "5" = "#de8a5a",
+            "6" = "#ca562c")
+
+#3d5941,#778868,#b5b991,#f6edbd,#edbb8a,#de8a5a,#ca562c
+mapping_county <- inner_join(county_shape, model_input,
+                      by = c("STATEFP" = "state_fips",
+                             "COUNTYFP" = "county_fips"))
+
+ggplot() +
+  geom_sf(data = mapping_county, aes(fill = ntile_mfg),
+          color = NA, size = .01) +
+  scale_fill_manual(values = colors,
+                    labels = labels) +
+  # add state lines
+  geom_sf(data = state_shape, fill = NA, color = "black", size = .1) +
+  coord_sf(datum = NA) +
+  theme_minimal() +
+  # geom_sf_text_repel(aes(label = state), data = mapping_small,
+  #                    force = .00001,  seed = 10,
+  #                    size = 2.5) +
+  theme(  axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          text = element_text(size = 8)) +
+  labs(title = "",
+       subtitle = "",
+       fill = "") +
+  theme(legend.key.size = unit(.4, 'cm'))
+
+```
+
+\begin{figurenotes}
+Calculated as net change in manufacturing employment from 2004-2015 divided by 2004 total employment.
+\end{figurenotes}
+\end{figure}
 
@@
 
+\begin{figure} \label{natlPlot}
+\caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+
+# load map
+model_input <- readRDS("../model_5_input.rds")
+model_results <- readRDS("../model_5_results.rds")
+
+# load voting data
+library(data.table)
+voting <- fread("..\\voting data.csv")
+
+# filter model input based on our regression filtering
+model_input <- model_input %>%
+  filter(is.finite(bartik_leo5_w2),
+         is.finite(mfgNetChange_white),
+         is.finite(mfgNetChange_nonwhite))
+
+# find the 25th percentile in manufacturing layoffs (our measure) across counties
+p25 <- quantile(model_input$mfgNetChange_white, (.25))
+
+# find the predicted democratic vote share
+model_input$P_ddem_1 <- model_results$fitted.values
+
+model_input <- model_input %>%
+  mutate(
+
+    # calculate the counterfactual change in democratic vote share
+    # by multiplying our regression coefficient against the difference
+    # between observed manufacturing layoffs (our measure) and the
+    # 25th percentile of layoffs (nationally)
+
+    # counterfactual net change in manufacturing job losses     
+    CF_netchange = p25,
+
+    # difference between counterfactual and actual net manufacturing job losses 
+    CF_d_netchange = CF_netchange - mfgNetChange_white,
+
+    # effect size -> coeff on white manufacturing layoffs times by the dif between CF and actual
+    CF_ddem_change = CF_d_netchange*model_results$coefficients[1],
+
+    # counterfactual predicted dem vote share
+
+    P_ddem_2 = P_ddem_1 + CF_ddem_change) %>%
+
+  dplyr::select(id, state_fips, state, state_name, county_fips,
+                county, year, dem_votes_pct1, ddem_votes_pct1,
+                P_ddem_1, mfgNetChange_white, mfgNetChange_total,
+                mfgNetChange_nonwhite,
+                CF_netchange,
+                CF_d_netchange,
+                CF_ddem_change,
+                P_ddem_2)
+
+# clear voting data
+voting <- voting %>%
+  dplyr::select(year, state, county_name, county_fips,
+         party, candidatevotes) %>%
+  filter(party == "DEMOCRAT" | party == "REPUBLICAN") %>%
+  group_by(year, county_fips) %>%
+  summarize(total_dem_rep_votes = sum(candidatevotes),
+         dem_votes = sum(candidatevotes[party == "DEMOCRAT"]),
+         rep_votes = sum(candidatevotes[party == "REPUBLICAN"])) %>%
+  mutate(dem_vote_share = dem_votes/total_dem_rep_votes)
+
+# prep model input data to be merged to voting data
+model_input <- model_input %>% mutate(
+  c_fips_long = case_when(
+    str_length(as.character(county_fips)) == 1 ~
+      paste0("00", as.character(county_fips)),
+    str_length(as.character(county_fips)) == 2 ~
+      paste0("0", as.character(county_fips)),
+    TRUE ~ as.character(county_fips)),
+  s_fips_long  = case_when(
+    str_length(as.character(state_fips)) == 1 ~
+      paste0("0", as.character(state_fips)),
+    TRUE ~ as.character(state_fips)),
+
+  fips_long = paste0(s_fips_long, c_fips_long),
+  fips_numeric = as.numeric(fips_long))
+
+# join model input to observed voting data
+model_input <- left_join(model_input, voting,
+                          by = c("fips_numeric" = "county_fips",
+                                 "year" = "year"))
+
+# calculate the counterfactual dem votes and rep votes
+model_input <- model_input %>%
+  mutate(
+    CF_dem_votes = dem_votes + CF_ddem_change*total_dem_rep_votes,
+    CF_rep_votes = rep_votes - CF_ddem_change*total_dem_rep_votes)
+
+# create mapping categories
+order = c(
+ # "+2% or greater", 
+  #"+1% to +2%",
+          "+0.5% to +1%",
+          "+0.25% to +0.5%", 
+          "0% to +0.25%", 
+          "0% to -0.25%")
+
+state_summary <- model_input %>%
+  group_by(state) %>%
+  summarize(actual_trump_votes = sum(rep_votes),
+            actual_dem_votes = sum(dem_votes),
+            CF_trump_votes = sum(CF_rep_votes),
+            CF_dem_votes = sum(CF_dem_votes)) %>%
+
+  mutate(changed_outcome  =
+           ifelse(
+             CF_dem_votes > CF_trump_votes &
+               actual_trump_votes > actual_dem_votes,
+             1, 0),
+    actual_trump_vs =
+      actual_trump_votes/(actual_trump_votes+ actual_dem_votes),
+    CF_trump_vs =
+      CF_trump_votes/(CF_trump_votes+CF_dem_votes),
+    delta_vs = CF_trump_vs - actual_trump_vs) %>%
+  mutate(
+    delta_vs_group = case_when(delta_vs < -.02 ~ "+2% or greater",
+                         delta_vs < -.01 ~ "+1% to +2%",
+                         delta_vs < -.005 ~ "+0.5% to +1%",
+                         delta_vs < -.0025 ~ "+0.25% to +0.5%",
+                         delta_vs < 0 ~ "0% to +0.25%",
+                         delta_vs < .0025 ~ "0% to -0.25%",
+                         delta_vs < .005 ~ "-0.25% to -0.5%",
+                         delta_vs < .01 ~ "-0.5% to -1%",
+                         TRUE ~ "-1% or greater")) %>%
+  mutate(delta_vs_group = factor(delta_vs_group, levels = order))
+
+colors =
+   c(
+    # "+2% or greater" = "#0059ff",
+     #"+1% to +2%" = "#4988fc",
+     "+0.5% to +1%" = "#86b0fc",
+     "+0.25% to +0.5%" = "#b8d1ff",
+     "0% to +0.25%" = "#dee9fc",
+     "0% to -0.25%" = "#ffeae8")
+
+# state shapefile
+state_shape <- states(
+  cb = TRUE,
+  resolution = "20m",
+  progress_bar = F
+) %>%
+  filter(GEOID != "72") %>%
+  shift_geometry()
+
+mapping <- inner_join(state_shape, state_summary,
+                      by = c("STUSPS" = "state"))
+
+mapping_small <- mapping #%>% filter(state != "DC")
+
+mapping_small <- mapping_small %>%
+  mutate(changed_outcome = ifelse(changed_outcome == 0,
+                                  "No",
+                                  "Yes"))
+
+#  make map
+flipped <- mapping_small %>% filter(changed_outcome == "Yes")
+ggplot() +
+  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "black", size = .1) +
+  scale_fill_manual(values = colors) +
+  labs(title = "Figure 3: Impact of Manufacturing Job Lossess on Democratic Vote Share",
+       subtitle = "Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses",
+       fill = "Change in Democratic Vote Share") +
+  geom_sf(data = flipped, fill = NA, 
+          aes(color = changed_outcome), 
+          size = 1) +
+  scale_color_manual(values = "#b32ab5", name = "Flipped Election") +
+  labs(color = "Flipped Election") +
+  coord_sf(datum = NA) +
+  theme_minimal() +
+  # geom_sf_text_repel(aes(label = state), data = mapping_small,
+  #                    force = .00001,  seed = 10,
+  #                    size = 2.5) +
+  theme(  axis.title.x=element_blank(),
+          axis.title.y=element_blank())
+
+```
+\begin{figurenotes}
+Gain or loss of national manufacturing jobs, divided by total national workforce.
+\end{figurenotes}
+\end{figure}
+
 XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL

### 2021-12-11 Final Draft/Final-Draft.tex
updates to final draft

@@
   Zagreb Mukerjee\thanks{
-  Darin: Harvard
-University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
-  Mukerjee: Harvard
-University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
+  Darin: Harvard University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
+  Mukerjee: Harvard University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
   Code available at https://github.com/zagrebmukerjee/ReplicationPaper
@@
 rather, it has been concentrated in certain areas of the country that
-were previously economically reliant on manufacturing XXXXXXXXXXXX MAP
-FIGURE XXXXXXXXXXX. We believe the localized nature of this analysis
-highlights the uneven and concentrated harms of deindustrialization.
+were previously economically reliant on manufacturing, as demonstrated
+in Figure \ref{ManuMap}. We believe the localized nature of this
+analysis highlights the uneven and concentrated harms of
+deindustrialization.
 
@@
 
+\begin{figure} \label{ManuMap}
+\caption{Net Change in Manufacturing Employment from 2004 to 2015}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-2-1} \end{center}
+
+\begin{figurenotes}
+Calculated as net change in manufacturing employment from 2004-2015 divided by 2004 total employment.
+\end{figurenotes}
+\end{figure}
+
 \begin{figure} \label{natlPlot}
@@
 
-\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-2-1} \end{center}
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-3-1} \end{center}
 
@@
 
+\begin{figure} \label{natlPlot}
+\caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-6-1} \end{center}
+\begin{figurenotes}
+Gain or loss of national manufacturing jobs, divided by total national workforce.
+\end{figurenotes}
+\end{figure}
+
 XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL

### 2021-12-11 Final Draft/Final Draft.Rmd
tweaks

@@
 
-\begin{figurenotes}
-Calculated as net change in manufacturing employment from 2004-2015 divided by 2004 total employment.
-\end{figurenotes}
 \end{figure}
@@
 
-Using this instrument, we then conduct a two stage regression.
+Using this instrument, we then conduct a two-stage regression.
 First we estimate manufacturing job loss with the Bartik Instrument and a set of county-level controls; then we use the estimated values of job losses to predict Democratic vote share.
@@
 As an alternative perspective, we examined a range of counterfactual scenarios, in which counties experienced job losses
+XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL
 
@@
   scale_fill_manual(values = colors) +
-  labs(title = "Figure 3: Impact of Manufacturing Job Lossess on Democratic Vote Share",
-       subtitle = "Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses",
+  labs(title = "",
+       subtitle = "",
        fill = "Change in Democratic Vote Share") +
@@
 ```
-\begin{figurenotes}
-Gain or loss of national manufacturing jobs, divided by total national workforce.
-\end{figurenotes}
 \end{figure}
-
-XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL
 

### 2021-12-12 Final Draft/Final Draft.Rmd
pushing changes to final draft

--- 2021-12-11 Final Draft/Final Draft.Rmd
@@
 This paper analyzes the relationship between deindustrialization, race, and the election of Donald Trump in 2016.
-Previous analysis has frequently focused on racial animus, trade, or the conjunction of the two (\cite{Autor20}; \cite{Che16}; \cite{BR21}).
-We extend the analysis of \cite{Baccini21}, one of the first papers to examine the political effects of deindustrialization while considering race and localization.
+Previous analysis has  focused on racial animus, trade, or the conjunction of the two on  political polarization and election outcomes (\cite{Autor20}; \cite{Che16}; \cite{BR21}).
+We extend the analysis of \cite{Baccini21}, one of the first papers to examine the political effects of deindustrialization that while considering race and localization.
 Deindustrialization - the transition of the U.S.
 economy away from manufacturing - has led to widespread job loss and created adverse knock-on effects for a wide swath of Americans.
-This incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
-The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing, as demonstrated in Figure \ref{ManuMap}.
-We believe the localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
+Our measure of dindustrialization incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
+The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing, as demonstrated in Figure \label{ManuMap}.
+The localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
 
-Along with \cite{Baccini21}, we find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites.
-However, we find that the related effects in the 2016 election are not associated with recent manufacturing job loss; rather, the opposite.
-Counties with manufacturing job losses from 2012-2015 tended to become more Democratic.
-We extend the analysis to the 2004-2015 period, to capture the long-term effects of deindustrialization on a region.
-Doing so, we find that regions experiencing more manufacturing job losses swung towards Donald Trump in 2016, and that this occurred more when those losing jobs were white.
-
-Our analysis extends \cite{Baccini21} in several ways.
-First, we change focus from a measure of gross losses in manufacturing jobs to net losses.
-As discussed in \ref{datasec}, we believe this to be a more accurate measure of deindustrialization.
-Second, we change the temporal focus.
-Rather than focusing on manufacturing job loss in 2012-2015, we extend our analysis back to 2004.
-This is an important change.
-As shown in Figure \ref{natlPlot}, the bulk of U.S.
-manufacturing job loss took place prior to 2012; in fact, the 2012-2015 period was characterized by a slight rebound in manufacturing jobs.
-During this rebound, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery, as described in Figure \ref{vShapePlot}.
-Because of this v-shaped recovery, focusing only on 2012-2015 job losses/gains paints a distorted picture.
-Finally, we augment the instrumental-variable approach with one based on covariate balancing, which produces similar results.
+<!-- FIGURE X: MAP OF DEINDUSTRIALIZATION HERE  -->
 
 \begin{figure} \label{ManuMap}
-\caption{Net Change in Manufacturing Employment from 2004 to 2015}
+\caption{Concentration of Deindustrialization (2004-2015) in the eastern Heartland}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
@@
           text = element_text(size = 8)) +
-  labs(title = "",
+  labs(title = "Net Change in Manufacturing Employment from 2004 to 2015",
        subtitle = "",
@@
 \end{figure}
+
+Like \cite{Baccini21}, we find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites. \cite{Baccini21}
+find that gross manufacturing layoffs between 2012-2015 were associated with a loss in Democratic vote share.
+However, using a different measure of deindustrialization - *net* change in manufacturing employment - we find the oppposite effect: that counties with manufacturing job *gains* from 2012-2015 tended to swing towards Donald Trump in 2016.
+We extend the analysis to the 2004-2015 period in order to capture the long-term effects of deindustrialization on a region.
+Doing so, we find that regions experiencing more manufacturing job losses swung towards Donald Trump in 2016, and that this occurred more when those losing jobs were white.
+
+Our analysis extends \cite{Baccini21} in several ways.
+First, we change focus from a measure of gross losses in manufacturing jobs to net losses.
+As discussed in \ref{datasec}, we believe this to be a more accurate measure of deindustrialization.
+Second, we change the temporal focus.
+Rather than focusing on manufacturing job loss in 2012-2015, we extend our analysis back to 2004.
+This is an important change.
+As shown in Figure \ref{natlPlot}, the bulk of U.S.
+manufacturing job loss took place prior to 2012; in fact, the 2012-2015 period was characterized by a slight rebound in manufacturing jobs.
+During this rebound, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery, as described in Figure \ref{vShapePlot}.
+Because of this v-shaped recovery, focusing only on 2012-2015 job losses/gains paints a distorted picture.
+Finally, we augment the instrumental-variable approach with one based on covariate balancing, which produces similar results.
+
+<!-- FIGURE X: TIME SERIES OF MANUFACUTRING EMPLOYMENT  -->
 
@@
 ```
-
 \begin{figurenotes}
-Gain or loss of national manufacturing jobs, divided by total national workforce.
-\end{figurenotes}
-\end{figure}
-
-\begin{figure} \label{vShapePlot}
-\caption{}
-
-\begin{figurenotes}
-Figure notes without optional leadin.
+"Gain or loss of national manufacturing jobs, divided by total national workforce."
 \end{figurenotes}
@@
 
-\begin{figure} \label{natlPlot}
+\begin{figure} \label{counterfactual}
 \caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
@@
 \bibliography{references}
+
+\appendix
+
+\section{Appendix}
+
+<!-- FIGURE X: V SHAPRED RECOVERY  -->
+
+\begin{figure} \label{vShapePlot}
+\caption{V-Shaped Recovery in Manufacturing Job Losses}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+
+ntile_summary <- readRDS("../v_shaped_recovery.rds")
+
+ntile_summary <- ntile_summary %>% mutate(n_tile_04_11 = as.numeric(n_tile_04_11))
+# plot 2004-2011 manu layoffs by deciles
+ggplot(data = ntile_summary,
+       aes(x = n_tile_04_11, y = mean_04_11)) +
+  theme_minimal() +
+  ylab("Manufacturing Layoffs (04-11)") +
+  xlab("Decile")+
+  ggtitle("Manufacturing Layoffs from 2004-2011 by Deciles") +
+  geom_col(fill = "#4287f5") +
+  scale_x_continuous(breaks=seq(1,10,1))
+
+```
+\begin{figurenotes}
+"Stuff here"
+\end{figurenotes}
+\end{figure}
+
+\begin{figure} \label{vShapePlot}
+\caption{V-Shaped Recovery in Manufacturing Job Losses}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+
+# plot 2012-2015 manu layoffs by deciles
+ggplot(data = ntile_summary,
+       aes(x = n_tile_04_11, y = mean_12_15)) +
+  theme_minimal() +
+  ylab("Manufacturing Layoffs (12-15)") +
+  xlab("Decile of Manufacturing Layoffs (04-11)")+
+  ggtitle("Manufacturing Layoffs from 2012-2015 by 2004-2011 Deciles") +
+  geom_col(fill = "#4287f5") +
+  scale_x_continuous(breaks=seq(1,10,1))
+
+```
+
+\begin{figurenotes}
+"Stuff here"
+\end{figurenotes}
+\end{figure}

### 2021-12-12 Final Draft/Final-Draft.tex
tweaks
pushing changes to final draft

@@
 This paper analyzes the relationship between deindustrialization, race,
-and the election of Donald Trump in 2016. Previous analysis has
-frequently focused on racial animus, trade, or the conjunction of the
-two (\cite{Autor20}; \cite{Che16}; \cite{BR21}). We extend the analysis
-of \cite{Baccini21}, one of the first papers to examine the political
-effects of deindustrialization while considering race and localization.
-Deindustrialization - the transition of the U.S. economy away from
-manufacturing - has led to widespread job loss and created adverse
-knock-on effects for a wide swath of Americans. This incorporates job
+and the election of Donald Trump in 2016. Previous analysis has focused
+on racial animus, trade, or the conjunction of the two on political
+polarization and election outcomes (\cite{Autor20}; \cite{Che16};
+\cite{BR21}). We extend the analysis of \cite{Baccini21}, one of the
+first papers to examine the political effects of deindustrialization
+that while considering race and localization. Deindustrialization - the
+transition of the U.S. economy away from manufacturing - has led to
+widespread job loss and created adverse knock-on effects for a wide
+swath of Americans. Our measure of dindustrialization incorporates job
 losses due to trade with China and others (see \cite{Acemoglu16}); it
@@
 were previously economically reliant on manufacturing, as demonstrated
-in Figure \ref{ManuMap}. We believe the localized nature of this
-analysis highlights the uneven and concentrated harms of
-deindustrialization.
+in Figure \label{ManuMap}. The localized nature of this analysis
+highlights the uneven and concentrated harms of deindustrialization.
 
-Along with \cite{Baccini21}, we find evidence that the experience of
+\begin{figure} \label{ManuMap}
+\caption{Concentration of Deindustrialization (2004-2015) in the eastern Heartland}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-2-1} \end{center}
+
+\begin{figurenotes}
+Calculated as net change in manufacturing employment from 2004-2015 divided by 2004 total employment.
+\end{figurenotes}
+\end{figure}
+
+Like \cite{Baccini21}, we find evidence that the experience of
 deindustralization was associated with support for Donald Trump,
-particularly among whites. However, we find that the related effects in
-the 2016 election are not associated with recent manufacturing job loss;
-rather, the opposite. Counties with manufacturing job losses from
-2012-2015 tended to become more Democratic. We extend the analysis to
-the 2004-2015 period, to capture the long-term effects of
-deindustrialization on a region. Doing so, we find that regions
-experiencing more manufacturing job losses swung towards Donald Trump in
-2016, and that this occurred more when those losing jobs were white.
+particularly among whites. \cite{Baccini21} find that gross
+manufacturing layoffs between 2012-2015 were associated with a loss in
+Democratic vote share. However, using a different measure of
+deindustrialization - \emph{net} change in manufacturing employment - we
+find the oppposite effect: that counties with manufacturing job
+\emph{gains} from 2012-2015 tended to swing towards Donald Trump in
+2016. We extend the analysis to the 2004-2015 period in order to capture
+the long-term effects of deindustrialization on a region. Doing so, we
+find that regions experiencing more manufacturing job losses swung
+towards Donald Trump in 2016, and that this occurred more when those
+losing jobs were white.
 
@@
 
-\begin{figure} \label{ManuMap}
-\caption{Net Change in Manufacturing Employment from 2004 to 2015}
-
-\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-2-1} \end{center}
-
-\begin{figurenotes}
-Calculated as net change in manufacturing employment from 2004-2015 divided by 2004 total employment.
-\end{figurenotes}
-\end{figure}
-
 \begin{figure} \label{natlPlot}
@@
 \begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-3-1} \end{center}
-
 \begin{figurenotes}
-Gain or loss of national manufacturing jobs, divided by total national workforce.
-\end{figurenotes}
-\end{figure}
-
-\begin{figure} \label{vShapePlot}
-\caption{}
-
-\begin{figurenotes}
-Figure notes without optional leadin.
+"Gain or loss of national manufacturing jobs, divided by total national workforce."
 \end{figurenotes}
@@
 
+\appendix
+
+\section{Appendix}
+
+\begin{figure} \label{vShapePlot}
+\caption{V-Shaped Recovery in Manufacturing Job Losses}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-8-1} \end{center}
+\begin{figurenotes}
+"Stuff here"
+\end{figurenotes}
+\end{figure}
+
+\begin{figure} \label{vShapePlot}
+\caption{V-Shaped Recovery in Manufacturing Job Losses}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-9-1} \end{center}
+
+\begin{figurenotes}
+"Stuff here"
+\end{figurenotes}
+\end{figure}
+
 \end{document}

### 2021-12-12 rCode/counterfactual analysis.R

@@ -1,0 +1,273 @@
+# load voting data
+library(data.table)
+library(tidyverse)
+library(stargazer)
+library(sandwich)
+library(lmtest)
+library(knitr)
+library(kableExtra)
+library(readxl)
+library(scales)
+library(tigris)
+
+# clear screen
+shell("cls")
+
+# clear enviornment
+rm(list = ls()) # clear enviornment
+
+options(scien = 999)
+
+
+write.excel <- function(x,
+                        row.names = FALSE,
+                        col.names = TRUE,
+                        ...) {
+  write.table(
+    x,
+    "clipboard",
+    sep = "\t",
+    row.names = row.names,
+    col.names = col.names,
+    ...
+  )
+} 
+
+# load input
+model_input <- readRDS("model_5_input.rds")
+model_results <- readRDS("model_5_results.rds")
+
+voting <- fread("voting data.csv")
+electoral_votes <- fread("electoral votes.csv")
+
+# get list of states for matching on different versions of state names
+state_match <- unique(model_input %>%
+                        group_by() %>% filter(state_name != "") %>%
+                        select(state, state_name))
+
+# filter model input based on our regression filtering
+model_input <- model_input %>%
+  filter(
+    is.finite(bartik_leo5_w2),
+    is.finite(mfgNetChange_white),
+    is.finite(mfgNetChange_nonwhite)
+  )
+
+# select relevant vars
+model_small <- model_input %>%
+  dplyr::select(
+    id,
+    state_fips,
+    state,
+    state_name,
+    county_fips,
+    county,
+    year,
+    dem_votes_pct1,
+    ddem_votes_pct1,
+    mfgNetChange_white,
+    mfgNetChange_total,
+    mfgNetChange_nonwhite
+  )
+
+# clean voting data
+voting <- voting %>%
+  dplyr::select(year, state, county_name, county_fips,
+                party, candidatevotes) %>%
+  filter(party == "DEMOCRAT" | party == "REPUBLICAN") %>%
+  group_by(year, county_fips) %>%
+  summarize(
+    total_dem_rep_votes = sum(candidatevotes),
+    dem_votes = sum(candidatevotes[party == "DEMOCRAT"]),
+    rep_votes = sum(candidatevotes[party == "REPUBLICAN"])
+  ) %>%
+  mutate(dem_vote_share = dem_votes / total_dem_rep_votes)
+
+
+# prep model input data to be merged to voting data
+model_small <- model_small %>% mutate(
+  c_fips_long = case_when(
[…]

### 2021-12-12 rCode/replicateRegsAndExtend_short v2.R

@@ -528,22 +528,20 @@ saveRDS(list(
 
 
 ##################################################
-#
+# show v-shaped recovery
 ##################################################
-
 
 datasetOurs04_15 <- datasetClean(electionYear = 2016, startYear = 2004, aggregateYears = 2004:2015)
 datasetOurs04_11 <- datasetClean(electionYear = 2016, startYear = 2004, aggregateYears = 2004:2011)
 datasetOurs12_15 <- datasetClean(electionYear = 2016, startYear = 2011, aggregateYears = 2012:2015)
 
-
+# merge together manu layoffs over different time periods
 summary_12_15 <- datasetOurs12_15 %>% 
   group_by() %>%
   dplyr::select(id:county,
     mfgNetChange_total) %>% 
   rename(mfgNetChange_12_15 = mfgNetChange_total)
     
-
 summary_04_15 <- datasetOurs04_15 %>% 
   group_by() %>%
   dplyr::select(id:county,
@@ -556,22 +554,14 @@ summary_04_11 <- datasetOurs04_11 %>%
                 mfgNetChange_total) %>% 
   rename(mfgNetChange_04_11 = mfgNetChange_total)
 
-
+# merge everything together
 summary_vshape <- inner_join(summary_12_15, summary_04_15)
 summary_vshape <- inner_join(summary_vshape, summary_04_11)
 
-#library(ggpubr)
-
-ggplot(data = summary_vshape # %>% filter(state_name == "Tennessee")
-       ,
-       aes(x = mfgNetChange_04_15, y = mfgNetChange_12_15)) +
-  geom_point() +
-  theme_bw() + stat_cor(method = "pearson", label.x = 0, label.y = .3)
 
 summary_vshape <- summary_vshape %>%
   mutate(
     n_tile_04_15 = as.character(ntile(mfgNetChange_04_15, 10)),
-    
     n_tile_04_11 = as.character(ntile(mfgNetChange_04_11, 10)),
     n_tile_12_15 = as.character(ntile(mfgNetChange_12_15, 10))
   ) %>%
@@ -581,17 +571,6 @@ summary_vshape <- summary_vshape %>%
   arrange(mfgNetChange_12_15) %>%
   mutate(rank_12_15 = row_number())
 
-ggplot(data = summary_vshape  %>% filter(!is.na(rank_04_11),
-                                         !is.na(rank_12_15))
-       ,
[…]

### 2021-12-12 Final Draft/Final Draft.Rmd
pushing updates to final draft

@@
 library(tigris)
-
+library(dplyr)
 knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
@@
 
-\begin{figure} \label{counterfactual}
+\begin{figure} \label{counterfactual1}
 \caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
@@
 
+\begin{figure} \label{counterfactual2}
+\caption{Clinton Electoral College Votes}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+
+# load map
+simulation_results <- readRDS("../counterfactual_simu_results.rds")
+num_sims <- 1000
+
+summary <- simulation_results %>%
+  group_by(ptile) %>%
+  arrange(trump_votes_cf) %>%
+  summarize(median_result = clinton_votes_cf[row_number() == (num_sims/2)],
+            lower = clinton_votes_cf[row_number() == (num_sims/40)],
+            upper = clinton_votes_cf[row_number() ==(num_sims- (num_sims/40))])
+
+# plot distribution and each percentile
+
+# first plot CI
+ggplot(summary, aes(ptile, median_result)) + 
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper),
+                color = "blue") +
+  geom_hline(yintercept = 270, color = "red") +
+  theme_bw() +
+  ylab("Outcome: Clinton Electoral College Votes\n") +
+  xlab("Input Assumption: Percentile of Manufacturing Layoffs\n") +
+  ggtitle("Counterfactual Presidential Election Simulation Results")
+
+```
+\end{figure}
+
+\begin{figure} \label{counterfactual3}
+\caption{Clinton Winning Freq}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+
+library(dplyr)
+library(ggplot2)
+summary2 <- simulation_results %>%
+  mutate(hil_wins = case_when(clinton_votes_cf > 270 ~ 1,
+                              TRUE ~ 0)) %>%
+  group_by(ptile) %>%
+  summarize(perc_wins =  sum(hil_wins)/n())
+
+ggplot(summary2, aes(ptile, perc_wins)) + 
+  geom_col(fill = "#4287f5")  +
+  theme_bw() +
+  ylab("Outcome: Frequency of Clinton Winning\nIn 1000 Simulations") +
+  xlab("Input Assumption: Percentile of Manufacturing Layoffs\n") +
+  ggtitle("Counterfactual Presidential Election Simulation Results")
+
+```
+\end{figure}
+
 \subsubsection{Timing}

### 2021-12-12 Final Draft/Final-Draft.tex
pushing updates to final draft

@@
 
-Using this instrument, we then conduct a two stage regression. First we
+Using this instrument, we then conduct a two-stage regression. First we
 estimate manufacturing job loss with the Bartik Instrument and a set of
@@
 a range of counterfactual scenarios, in which counties experienced job
-losses
+losses XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL
 
-\begin{figure} \label{counterfactual}
+\begin{figure} \label{counterfactual1}
 \caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
@@
 \begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-6-1} \end{center}
-\begin{figurenotes}
-Gain or loss of national manufacturing jobs, divided by total national workforce.
-\end{figurenotes}
 \end{figure}
 
-XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL
+\begin{figure} \label{counterfactual2}
+\caption{Clinton Electoral College Votes}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-7-1} \end{center}
+\end{figure}
+
+\begin{figure} \label{counterfactual3}
+\caption{Clinton Winning Freq}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-8-1} \end{center}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-8-1} \end{center}
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-10-1} \end{center}
 \begin{figurenotes}
@@
 
-\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-9-1} \end{center}
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-11-1} \end{center}
 

### 2021-12-12 Final Draft/Final Draft.Rmd
small tweaks to titles

@@
 The primary outcome variable is the county's change in Democratic vote share between 2012 and 2016.
-We obtain this from XXXXXXXXX
+We obtain this from
+<!--  sources of electoral data -->
 
@@
 
-XXXXXXXXXXXXXXXX sources of other data
+<!--  sources of other data -->
 
@@
 As an alternative perspective, we examined a range of counterfactual scenarios, in which counties experienced job losses
-XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL
+<!--  what should I read in the counterfactual -->
 
@@
 \begin{figure} \label{counterfactual2}
-\caption{Clinton Electoral College Votes}
+\caption{Counterfactual Presidential Election Simulation Results}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
@@
   theme_bw() +
-  ylab("Outcome: Clinton Electoral College Votes\n") +
-  xlab("Input Assumption: Percentile of Manufacturing Layoffs\n") +
-  ggtitle("Counterfactual Presidential Election Simulation Results")
+  ylab("Clinton Electoral College Votes\n") +
+  xlab("Assumed Percentile of Manufacturing Layoffs\n")
 

### 2021-12-12 Final Draft/Final Draft.Rmd
adding placeins package

--- 2021-12-12 Final Draft/Final Draft.Rmd
@@
  - \usepackage{amssymb}
+ - \usepackage{placeins}
 ---
@@
 knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
+
+knitr::knit_hooks$set(plot = function (x, options) {
+  float_correct <- function(f, y, opts)  {
+    if (is.null(opts$regfloat) || opts$regfloat==FALSE)
+      paste0(f(y, opts), "\n\n\\FloatBarrier\n")
+    else
+      f(y, opts)
+  }
+  if (!is.null(options$out.width) || !is.null(options$out.height) ||
+      !is.null(options$out.extra) || options$fig.align != "default" ||
+      !is.null(options$fig.subcap)) {
+    if (is.null(options$fig.scap))
+      options$fig.scap = NA
+    return(float_correct(knitr:::hook_plot_tex, x, options))
+  }
+  return(float_correct(knitr:::hook_plot_md_base, x, options))
+})
+
 ```
@@
 
+\FloatBarrier
 \begin{figure} \label{ManuMap}
 \caption{Concentration of Deindustrialization (2004-2015) in the eastern Heartland}
-```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center" , regfloat=FALSE}
 # load map
@@
 \end{figure}
+\FloatBarrier
 
@@
 <!-- FIGURE X: TIME SERIES OF MANUFACUTRING EMPLOYMENT  -->
-
+\FloatBarrier
 \begin{figure} \label{natlPlot}
 \caption{Nationwide Change in Manufacturing Employment, 1995-2019}
-```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
 # manufacturing layoffs over time
@@
 Basic descriptive statistics of job losses and other key covariates can be seen in Table \ref{tab:descTable}.
-
-```{r,  echo=F}
+\FloatBarrier
+```{r,  echo=F, regfloat=FALSE}
 descriptiveData <-  readRDS("../tableData.rds")
@@
 ```
+\FloatBarrier
 
@@
 The regression coefficient in Model 4, for instance, means that a loss of $10$ manufacturing jobs per $100$ workers in a county (a relatively extreme value) corresponds to a loss of $3.2 \%$ in Democratic vote share.
-
-```{r,  echo=F, message = F, results = "asis"}
+\FloatBarrier
+```{r,  echo=F, message = F, results = "asis", regfloat=FALSE}
 
@@
 ```
-
+\FloatBarrier
 This coefficient is still somewhat difficult to interpret, and made increasingly so by the winner-take-all system by which U.S.
@@
 
+\FloatBarrier
 \begin{figure} \label{counterfactual1}
 \caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
-```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
 
@@
 \end{figure}
+\FloatBarrier
 
+\FloatBarrier
 \begin{figure} \label{counterfactual2}
 \caption{Clinton Electoral College Votes}
-```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
 
@@
 \end{figure}
+\FloatBarrier
 
+\FloatBarrier
 \begin{figure} \label{counterfactual3}
 \caption{Clinton Winning Freq}
-```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
 
@@
 \end{figure}
-
+\FloatBarrier
 \subsubsection{Timing}
@@
 These results can be seen in Table \ref{regResult12}.
-
-```{r,  echo=F, message = F, results = "asis"}
+\FloatBarrier
+```{r,  echo=F, message = F, results = "asis", regfloat=FALSE}
 
@@
 ```
-
+\FloatBarrier
 This result suggests an important temporal dimension to the political effects of deindustrialization - job losses in 2004-2012 make their effects felt in 2016.

### 2021-12-12 Final Draft/Final Draft.Rmd
merge

@@
 \begin{figure} \label{counterfactual2}
-\caption{Clinton Electoral College Votes}
-```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
+\caption{Counterfactual Presidential Election Simulation Results}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
 

### 2021-12-12 Final Draft/Final Draft.Rmd
abstract change. Some other changes

@@
 This paper examines the potential contribution of deindustrialization.
-We use an instrumental-variable approach and a covariate-balancing approach to identify the effect of manufacturing job loss on change in Democratic vote share.
-We find that Democratic vote share falls in counties with high manufacturing job loss since 2004.
+We exploit county-level differences in manufacturing density as a source of exogenous variation, using both instrumental-variable regression and covariate balancing methods.
+Counterintuitively, we find that counties that gained manufacturing jobs from 2012-2015 are more likely to have swung towards Trump.
+We believe this is due to an omitted variable - the job loss experienced from 2004 to 2012.
+Counties that experienced prior deindustrialization were more likely to exhibit increased support for Trump, as well as a slight manufacturing rebound in 2012-2015.
 Disaggregating this result by race shows that the Democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
@@
 Our measure of dindustrialization incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
-The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing, as demonstrated in Figure \label{ManuMap}.
+The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing, as demonstrated in Figure \ref{ManuMap}.
 The localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
@@
 
-Like \cite{Baccini21}, we find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites. \cite{Baccini21}
-find that gross manufacturing layoffs between 2012-2015 were associated with a loss in Democratic vote share.
+Like \cite{Baccini21}, we find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites.
+\cite{Baccini21} find that gross manufacturing layoffs between 2012-2015 were associated with a loss in Democratic vote share.
 However, using a different measure of deindustrialization - *net* change in manufacturing employment - we find the oppposite effect: that counties with manufacturing job *gains* from 2012-2015 tended to swing towards Donald Trump in 2016.
@@
 
-\begin{figure} \label{}
-\caption{Caption for figure below.}
-
-\begin{figurenotes}
-Figure notes without optional leadin.
-\end{figurenotes}
-\begin{figurenotes}[Source]
-Figure notes with optional leadin (Source, in this case).
-\end{figurenotes}
-\end{figure}
-
 \nocite{Stargazer}

### 2021-12-12 Final Draft/Final Draft.Rmd
updates to final draft

--- 2021-12-12 Final Draft/Final Draft.Rmd
@@
 
+\section{Introduction} 
+\label{Introduction}
+
 This paper analyzes the relationship between deindustrialization, race, and the election of Donald Trump in 2016.
-Previous analysis has  focused on racial animus, trade, or the conjunction of the two on  political polarization and election outcomes (\cite{Autor20}; \cite{Che16}; \cite{BR21}).
-We extend the analysis of \cite{Baccini21}, one of the first papers to examine the political effects of deindustrialization that while considering race and localization.
+Previous analyses have  focused on the effects of racial animus, trade, or the conjunction of the two on  political polarization and election outcomes (\cite{Autor20}; \cite{Che16}; \cite{BR21}).
+We extend the analysis of \cite{Baccini21}, one of the first papers to examine the political effects of deindustrialization while considering race and localization.
+
 Deindustrialization - the transition of the U.S.
@@
 Our measure of dindustrialization incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
-The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing, as demonstrated in Figure \label{ManuMap}.
+The experience of deindustrialization has not been uniform; rather, it has been concentrated in areas of the country that were previously economically reliant on manufacturing.
+As shown in Figure \ref{ManuMap}, states across the eastern half of America, particularly in the South and Midwest, have experienced the most pronouncd manufacturing employment losses.
 The localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
@@
 \begin{figure} \label{ManuMap}
-\caption{Concentration of Deindustrialization (2004-2015) in the eastern Heartland}
+\caption{Concentration of Deindustrialization (2004-2015) in the eastern United States }
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center" , regfloat=FALSE}
@@
           text = element_text(size = 8)) +
-  labs(title = "Net Change in Manufacturing Employment from 2004 to 2015",
+  labs(title = "",
        subtitle = "",
-       fill = "") +
+       fill = "Net Manufacturing Employment\nLosses from 2004 to 2015") +
   theme(legend.key.size = unit(.4, 'cm'))
@@
 ```
-
+\begin{figurenotes}
+Calculated at the county-level as the net change in manufacturing employment between 2004 and 2015 divided by 2004 total employment.
+\end{figurenotes}
 \end{figure}
@@
 
-Like \cite{Baccini21}, we find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites. \cite{Baccini21}
-find that gross manufacturing layoffs between 2012-2015 were associated with a loss in Democratic vote share.
-However, using a different measure of deindustrialization - *net* change in manufacturing employment - we find the oppposite effect: that counties with manufacturing job *gains* from 2012-2015 tended to swing towards Donald Trump in 2016.
-We extend the analysis to the 2004-2015 period in order to capture the long-term effects of deindustrialization on a region.
-Doing so, we find that regions experiencing more manufacturing job losses swung towards Donald Trump in 2016, and that this occurred more when those losing jobs were white.
+In their central analysis, \cite{Baccini21} analyzed the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
+\cite{Baccini21} find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites.
 
 Our analysis extends \cite{Baccini21} in several ways.
-First, we change focus from a measure of gross losses in manufacturing jobs to net losses.
+First, we change focus from a measure of *gross* losses in manufacturing jobs to *net* losses.
 As discussed in \ref{datasec}, we believe this to be a more accurate measure of deindustrialization.
@@
 This is an important change.
-As shown in Figure \ref{natlPlot}, the bulk of U.S.
+As shown in Figure \ref{natlPlotTS}, the bulk of U.S.
 manufacturing job loss took place prior to 2012; in fact, the 2012-2015 period was characterized by a slight rebound in manufacturing jobs.
-During this rebound, counties that experienced the most pronounced manufacturing job losses in prior years were also likely to experience the most pronounced recovery, as described in Figure \ref{vShapePlot}.
-Because of this v-shaped recovery, focusing only on 2012-2015 job losses/gains paints a distorted picture.
-Finally, we augment the instrumental-variable approach with one based on covariate balancing, which produces similar results.
+Finally, we augment the instrumental-variable approach with one based on covariate balancing.
+
+Like \cite{Baccini21}, our results suggest that the experience of deindustralization was associated with support for Donald Trump, particularly among whites.
+However, our results differ from \cite{Baccini21} in regards to the *timing* of the impact of manufacturing job losses on employment.
+In fact, using our preferred measure of deindustrialization - *net* change in manufacturing employment - we find that counties with manufacturing job *gains* from 2012-2015 tended to swing towards Donald Trump in 2016.
+Given this counter-intuitive result, we extend the analysis to the 2004-2015 period in order to capture the long-term effects of deindustrialization on a region.
+Doing so, we find that regions experiencing more manufacturing job losses from 2004-2015 swung towards Donald Trump in 2016, and that this occurred more when those losing jobs were white.
+We get similar result using our covariate-matching approach.
+Relative to \cite{Baccini21}, our results point to the substantive importance of the timing of manufacturing layoffs on political outcomes.
 
@@
 \FloatBarrier
-\begin{figure} \label{natlPlot}
+\begin{figure} \label{natlPlotTS}
 \caption{Nationwide Change in Manufacturing Employment, 1995-2019}
@@
 \begin{figurenotes}
-"Gain or loss of national manufacturing jobs, divided by total national workforce."
+Annual net change in manufacturing employment in the United States. 
 \end{figurenotes}
@@
 Following \cite{Baccini21}, our unit of analysis is the county.
-This allows us to capture not only the direct effects of deindustrialization on laid-off manufacturing workers, but also on the local economy.
+This allows us to capture not only the direct effects of deindustrialization on laid-off manufacturing workers, but also possible spillover effects on the greater population within the county.
 The primary outcome variable is the county's change in Democratic vote share between 2012 and 2016.
-We obtain this from
-<!--  sources of electoral data -->
+We obtain this from the publically-available replication data provided by \cite{Baccini21}.
 
@@
 At the end there are only $1500$ manufacturing workers.
-This is a loss of $500/10000 = 5\%.$
+Using our measure of net change in manufacturing employment, this is a loss of $500/10000 = 5\%.$
 
@@
 \begin{figure} \label{counterfactual2}
-\caption{Counterfactual Presidential Election Simulation Results}
-```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
+
+\caption{Clinton Electoral College Votes}
+```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
 

### 2021-12-12 Final Draft/Final-Draft.tex
adding placeins package
updates to final draft

@@
 \usepackage{amssymb}
+\usepackage{placeins}
 \usepackage{booktabs}
@@
 
+\section{Introduction} 
+\label{Introduction}
+
 This paper analyzes the relationship between deindustrialization, race,
-and the election of Donald Trump in 2016. Previous analysis has focused
-on racial animus, trade, or the conjunction of the two on political
-polarization and election outcomes (\cite{Autor20}; \cite{Che16};
-\cite{BR21}). We extend the analysis of \cite{Baccini21}, one of the
-first papers to examine the political effects of deindustrialization
-that while considering race and localization. Deindustrialization - the
-transition of the U.S. economy away from manufacturing - has led to
-widespread job loss and created adverse knock-on effects for a wide
-swath of Americans. Our measure of dindustrialization incorporates job
-losses due to trade with China and others (see \cite{Acemoglu16}); it
-also includes job losses due to automation, demand changes, and other
-factors. The experience of deindustrialization has not been uniform;
-rather, it has been concentrated in certain areas of the country that
-were previously economically reliant on manufacturing, as demonstrated
-in Figure \label{ManuMap}. The localized nature of this analysis
-highlights the uneven and concentrated harms of deindustrialization.
+and the election of Donald Trump in 2016. Previous analyses have focused
+on the effects of racial animus, trade, or the conjunction of the two on
+political polarization and election outcomes (\cite{Autor20};
+\cite{Che16}; \cite{BR21}). We extend the analysis of \cite{Baccini21},
+one of the first papers to examine the political effects of
+deindustrialization while considering race and localization.
 
+Deindustrialization - the transition of the U.S. economy away from
+manufacturing - has led to widespread job loss and created adverse
+knock-on effects for a wide swath of Americans. Our measure of
+dindustrialization incorporates job losses due to trade with China and
+others (see \cite{Acemoglu16}); it also includes job losses due to
+automation, demand changes, and other factors. The experience of
+deindustrialization has not been uniform; rather, it has been
+concentrated in areas of the country that were previously economically
+reliant on manufacturing. As shown in Figure \ref{ManuMap}, states
+across the eastern half of America, particularly in the South and
+Midwest, have experienced the most pronouncd manufacturing employment
+losses. The localized nature of this analysis highlights the uneven and
+concentrated harms of deindustrialization.
+
+\FloatBarrier
 \begin{figure} \label{ManuMap}
-\caption{Concentration of Deindustrialization (2004-2015) in the eastern Heartland}
+\caption{Concentration of Deindustrialization (2004-2015) in the eastern United States }
 
@@
 
+\FloatBarrier
+\begin{figurenotes}
+Calculated at the county-level as the net change in manufacturing employment between 2004 and 2015 divided by 2004 total employment.
+\end{figurenotes}
 \end{figure}
+\FloatBarrier
 
-Like \cite{Baccini21}, we find evidence that the experience of
-deindustralization was associated with support for Donald Trump,
-particularly among whites. \cite{Baccini21} find that gross
-manufacturing layoffs between 2012-2015 were associated with a loss in
-Democratic vote share. However, using a different measure of
-deindustrialization - \emph{net} change in manufacturing employment - we
-find the oppposite effect: that counties with manufacturing job
-\emph{gains} from 2012-2015 tended to swing towards Donald Trump in
-2016. We extend the analysis to the 2004-2015 period in order to capture
-the long-term effects of deindustrialization on a region. Doing so, we
-find that regions experiencing more manufacturing job losses swung
-towards Donald Trump in 2016, and that this occurred more when those
-losing jobs were white.
+In their central analysis, \cite{Baccini21} analyzed the effect of gross
+manufacturing job losses from 2012 to 2015 on the change in Democratic
+vote share in the 2016 presidential election. \cite{Baccini21} find
+evidence that the experience of deindustralization was associated with
+support for Donald Trump, particularly among whites.
 
 Our analysis extends \cite{Baccini21} in several ways. First, we change
-focus from a measure of gross losses in manufacturing jobs to net
-losses. As discussed in \ref{datasec}, we believe this to be a more
-accurate measure of deindustrialization. Second, we change the temporal
-focus. Rather than focusing on manufacturing job loss in 2012-2015, we
-extend our analysis back to 2004. This is an important change. As shown
-in Figure \ref{natlPlot}, the bulk of U.S. manufacturing job loss took
-place prior to 2012; in fact, the 2012-2015 period was characterized by
-a slight rebound in manufacturing jobs. During this rebound, counties
-that experienced the most pronounced manufacturing job losses in prior
-years were also likely to experience the most pronounced recovery, as
-described in Figure \ref{vShapePlot}. Because of this v-shaped recovery,
-focusing only on 2012-2015 job losses/gains paints a distorted picture.
+focus from a measure of \emph{gross} losses in manufacturing jobs to
+\emph{net} losses. As discussed in \ref{datasec}, we believe this to be
+a more accurate measure of deindustrialization. Second, we change the
+temporal focus. Rather than focusing on manufacturing job loss in
+2012-2015, we extend our analysis back to 2004. This is an important
+change. As shown in Figure \ref{natlPlotTS}, the bulk of U.S.
+manufacturing job loss took place prior to 2012; in fact, the 2012-2015
+period was characterized by a slight rebound in manufacturing jobs.
 Finally, we augment the instrumental-variable approach with one based on
-covariate balancing, which produces similar results.
+covariate balancing.
 
-\begin{figure} \label{natlPlot}
+Like \cite{Baccini21}, our results suggest that the experience of
+deindustralization was associated with support for Donald Trump,
+particularly among whites. However, our results differ from
+\cite{Baccini21} in regards to the \emph{timing} of the impact of
+manufacturing job losses on employment. In fact, using our preferred
+measure of deindustrialization - \emph{net} change in manufacturing
+employment - we find that counties with manufacturing job \emph{gains}
+from 2012-2015 tended to swing towards Donald Trump in 2016. Given this
+counter-intuitive result, we extend the analysis to the 2004-2015 period
+in order to capture the long-term effects of deindustrialization on a
+region. Doing so, we find that regions experiencing more manufacturing
+job losses from 2004-2015 swung towards Donald Trump in 2016, and that
+this occurred more when those losing jobs were white. We get similar
+result using our covariate-matching approach. Relative to
+\cite{Baccini21}, our results point to the substantive importance of the
+timing of manufacturing layoffs on political outcomes.
+
+\FloatBarrier
+\begin{figure} \label{natlPlotTS}
 \caption{Nationwide Change in Manufacturing Employment, 1995-2019}
@@
 \begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-3-1} \end{center}
+
+\FloatBarrier
 \begin{figurenotes}
-"Gain or loss of national manufacturing jobs, divided by total national workforce."
+Annual net change in manufacturing employment in the United States. 
 \end{figurenotes}
 \end{figure}
+\FloatBarrier
 
@@
 allows us to capture not only the direct effects of deindustrialization
-on laid-off manufacturing workers, but also on the local economy. The
-primary outcome variable is the county's change in Democratic vote share
-between 2012 and 2016. We obtain this from XXXXXXXXX
+on laid-off manufacturing workers, but also possible spillover effects
+on the greater population within the county. The primary outcome
+variable is the county's change in Democratic vote share between 2012
+and 2016. We obtain this from the publically-available replication data
+provided by \cite{Baccini21}.
 
@@
 \(8000\) non-manufacturing workers. At the end there are only \(1500\)
-manufacturing workers. This is a loss of \(500/10000 = 5\%.\)
+manufacturing workers. Using our measure of net change in manufacturing
+employment, this is a loss of \(500/10000 = 5\%.\)
 
@@
 
-XXXXXXXXXXXXXXXX sources of other data
-
 Basic descriptive statistics of job losses and other key covariates can
-be seen in Table \ref{tab:descTable}.
+be seen in Table \ref{tab:descTable}. \FloatBarrier
 
@@
 \end{table}
+\FloatBarrier
 
@@
 value) corresponds to a loss of \(3.2 \%\) in Democratic vote share.
+\FloatBarrier
 
@@
 \end{table} 
+\FloatBarrier
 
@@
 a range of counterfactual scenarios, in which counties experienced job
-losses XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL
+losses
 
+\FloatBarrier
 \begin{figure} \label{counterfactual1}
@@
 \begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-6-1} \end{center}
+
+\FloatBarrier
 \end{figure}
+\FloatBarrier
 
+\FloatBarrier
 \begin{figure} \label{counterfactual2}
+
 \caption{Clinton Electoral College Votes}
@@
 \begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-7-1} \end{center}
+
+\FloatBarrier
 \end{figure}
+\FloatBarrier
 
+\FloatBarrier
 \begin{figure} \label{counterfactual3}
@@
 \begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-8-1} \end{center}
+
+\FloatBarrier
 \end{figure}
-
+\FloatBarrier
 \subsubsection{Timing}
@@
 share. These results can be seen in Table \ref{regResult12}.
+\FloatBarrier
 
@@
 \begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-10-1} \end{center}
+
+\FloatBarrier
 \begin{figurenotes}
@@
 
+\FloatBarrier
+
 \begin{figurenotes}

### 2021-12-12 rCode/matchingResults.R
adding file

@@ -1,0 +1,295 @@
+library(CBPS)
+library(cobalt)
+
+
+datasetOurs04Limited <- datasetOurs04 %>%  
+  filter(is.finite(mfgNetChange_total), is.finite(mfgNetChange_white ), is.finite(mfgNetChange_nonwhite ), is.finite(bartik_leo5_w2))
+
+
+
+plot(datasetOurs04Limited$ddem_votes_pct1, datasetOurs04Limited$mfgNetChange_total)
+
+plot(datasetOurs04Limited$mfgNetChange_white, datasetOurs04Limited$msl_educ_prop)
+
+fit04 <- CBPS(mfgNetChange_total ~ LAU_unemp_rate_4y + pers_m_total_share_4y +
+                pers_coll_share_4y + white_counties_4y + msl_service_pc4y + mfgShare_total + totalEmp_total, data = datasetOurs04Limited, method = "exact")
+
+fit04_white <- CBPS(mfgNetChange_white ~ LAU_unemp_rate_4y + pers_m_total_share_4y +
+                pers_coll_share_4y + white_counties_4y + msl_service_pc4y + mfgShare_white + totalEmp_white, data = datasetOurs04Limited, method = "exact")
+
+plot(fit04)
+plot(fit04_white)
+
+balance(fit04)
+balance(fit04_white)
+
+
+###############################################################
+# Test to make sure my listwise deletion didn't do too much
+################################################################
+
+# model 2
+firstStageModelOurs04L_2 <- felm(
+  data = datasetOurs04Limited,
+  formula = mfgNetChange_total ~ bartik_leo5  +
+    LAU_unemp_rate_4y + pers_m_total_share_4y +
+    pers_coll_share_4y + white_counties_4y   | id_state)
+
+secondStageModelOurs04L_2 <- felm(
+  data = datasetOurs04Limited,
+  formula = ddem_votes_pct1 ~ firstStageModelOurs04L_2$fitted.values +
+    LAU_unemp_rate_4y + pers_m_total_share_4y +
+    pers_coll_share_4y + white_counties_4y  | id_state)
+
+rseOurs04L2_1 <- coeftest(firstStageModelOurs04L_2, vcov = vcovHC(firstStageModelOurs04L_2, type = "HC0"))[,2]
[…]

### 2021-12-12 Final Draft/Final Draft.Rmd
add cbps results

@@
 library(dplyr)
+library(CBPS)
 knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
@@
 We apply the method of Covariate Balancing Propensity Scores, as developed by \cite{Imai14}; this method generates weights to reduce the correlation between covariates and treatment, while addressing several of the issues with propensity score weights.
+We find significant imbalance in the data - in other words, it is relatively easy to predict the 'treatment' of job loss given the covariates (see Appendix for balance plots).
 Given covariate-balancing weights, we then conduct a single-stage weighted regression of change in Democratic vote share on manufacturing job loss, using the same controls as above.
-
-XXXXXXXXXXXXXXX BALANCE FIGURE??? XXXXXXXXXXXXXXXXXXXXXXXXXXX
 
@@
 regResultList <- readRDS("../regresults.rds")
+matchResultList <- readRDS("../cbpsResults.rds")
 
-rownames(regResultList$secondStageModelNetC04A$coefficients )[rownames(regResultList$secondStageModelNetC04A$coefficients)=="firstStageModelOurs04_2$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC04$coefficients )[rownames(regResultList$secondStageModelNetC04$coefficients)=="firstStageModelOurs04_3$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04A$coefficients )[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="firstStageModelOurs04_5$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$coefficients )[rownames(regResultList$secondStageModelWNetC04$coefficients)=="firstStageModelOurs04_6$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC04A$coefficients )[rownames(regResultList$secondStageModelNetC04A$coefficients)=="firstStageModelOurs04_2$fitted.values"] <-  "Job Losses"
+rownames(regResultList$secondStageModelNetC04$coefficients )[rownames(regResultList$secondStageModelNetC04$coefficients)=="firstStageModelOurs04_3$fitted.values"] <-  "Job Losses"
+rownames(regResultList$secondStageModelWNetC04A$coefficients )[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="firstStageModelOurs04_5$fitted.values"] <-  "White Job Losses"
+rownames(regResultList$secondStageModelWNetC04$coefficients )[rownames(regResultList$secondStageModelWNetC04$coefficients)=="firstStageModelOurs04_6$fitted.values"] <-  "White Job Losses"
 
 rownames(regResultList$secondStageModelWNetC04A$coefficients
-)[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+)[rownames(regResultList$secondStageModelWNetC04A$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
 rownames(regResultList$secondStageModelWNetC04$coefficients
-)[rownames(regResultList$secondStageModelWNetC04$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+)[rownames(regResultList$secondStageModelWNetC04$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
 
-rownames(regResultList$secondStageModelNetC04A$beta )[rownames(regResultList$secondStageModelNetC04A$beta) =="firstStageModelOurs04_2$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC04$beta )[rownames(regResultList$secondStageModelNetC04$beta)=="firstStageModelOurs04_3$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="firstStageModelOurs04_5$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="firstStageModelOurs04_6$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetC04A$beta )[rownames(regResultList$secondStageModelNetC04A$beta) =="firstStageModelOurs04_2$fitted.values"] <-  "Job Losses"
+rownames(regResultList$secondStageModelNetC04$beta )[rownames(regResultList$secondStageModelNetC04$beta)=="firstStageModelOurs04_3$fitted.values"] <-  "Job Losses"
+rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="firstStageModelOurs04_5$fitted.values"] <-  "White Job Losses"
+rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="firstStageModelOurs04_6$fitted.values"] <-  "White Job Losses"
 
-rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetC04A$beta )[rownames(regResultList$secondStageModelWNetC04A$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
+rownames(regResultList$secondStageModelWNetC04$beta )[rownames(regResultList$secondStageModelWNetC04$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
 
-names(regResultList$rseNetC04A_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseNetC04_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseWNetC04A_2)[1] <- "White Manufacturing Layoffs"
-names(regResultList$rseWNetC04_2)[1] <- "White Manufacturing Layoffs"
+rownames(matchResultList$secondStageModelOurs04LW_3$coefficients)[rownames(matchResultList$secondStageModelOurs04LW_3$coefficients) == "mfgNetChange_total"] <- "Job Losses"
+rownames(matchResultList$secondStageModelOurs04LW_6$coefficients)[rownames(matchResultList$secondStageModelOurs04LW_6$coefficients) == "mfgNetChange_white"] <- "White Job Losses"
+rownames(matchResultList$secondStageModelOurs04LW_6$coefficients)[rownames(matchResultList$secondStageModelOurs04LW_6$coefficients) == "mfgNetChange_nonwhite"] <- "Nonwhite Job Losses"
 
-names(regResultList$rseWNetC04A_2)[names(regResultList$rseWNetC04A_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
-names(regResultList$rseWNetC04_2)[names(regResultList$rseWNetC04_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+rownames(matchResultList$secondStageModelOurs04LW_3$beta)[rownames(matchResultList$secondStageModelOurs04LW_3$beta) == "mfgNetChange_total"] <- "Job Losses"
+rownames(matchResultList$secondStageModelOurs04LW_6$beta)[rownames(matchResultList$secondStageModelOurs04LW_6$beta) == "mfgNetChange_white"] <- "White Job Losses"
+rownames(matchResultList$secondStageModelOurs04LW_6$beta)[rownames(matchResultList$secondStageModelOurs04LW_6$beta) == "mfgNetChange_nonwhite"] <- "Nonwhite Job Losses"
+
+names(regResultList$rseNetC04A_2)[1] <- "Job Losses"
+names(regResultList$rseNetC04_2)[1] <- "Job Losses"
+names(regResultList$rseWNetC04A_2)[1] <- "White Job Losses"
+names(regResultList$rseWNetC04_2)[1] <- "White Job Losses"
+
+names(regResultList$rseWNetC04A_2)[names(regResultList$rseWNetC04A_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Job Losses"
+names(regResultList$rseWNetC04_2)[names(regResultList$rseWNetC04_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Job Losses"
+
+names(matchResultList$rseOurs04LW3_2)[1] <- "Job Losses"
+names(matchResultList$rseOurs04LW6_2)[1] <- "White Job Losses"
+names(matchResultList$rseOurs04LW6_2)[names(matchResultList$rseOurs04LW6_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Job Losses"
 
@@
           regResultList$secondStageModelNetC04,
+          matchResultList$secondStageModelOurs04LW_3,
           regResultList$secondStageModelWNetC04A,
           regResultList$secondStageModelWNetC04,
+          matchResultList$secondStageModelOurs04LW_6,
           se = list(
@@
             regResultList$rseNetC04_2,
+            matchResultList$rseOurs04LW3_2,
             regResultList$rseWNetC04A_2,
-            regResultList$rseWNetC04_2
+            regResultList$rseWNetC04_2,
+            matchResultList$rseOurs04LW6_2
           ),
@@
           omit.stat = c("rsq","ser"),
-          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
+          keep = c("Job Losses", "White Job Losses", "Nonwhite Job Losses"),
           add.lines = list(
-            c("White Share/Svc Layoffs Control", "No", "Yes", "No", "Yes")
+            c("White Share/Svc Layoffs", "No", "Yes", "Yes", "No", "Yes", "Yes"),
+            c("Covariate Balancing", "No", "No", "Yes", "No", "No", "Yes")
           ),
@@
 
-\caption{Clinton Electoral College Votes}
+\caption{Counterfactual Presidential Election Simulation Results}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
   ylab("Clinton Electoral College Votes\n") +
-  xlab("Assumed Percentile of Manufacturing Layoffs\n")
+  xlab("Assumed Percentile of Manufacturing Layoffs\n")   +
+  theme(axis.title.x = element_text(size = 8), 
+        axis.title.y = element_text(size = 8))
 
@@
 \begin{figure} \label{counterfactual3}
-\caption{Clinton Winning Freq}
+\caption{ Counterfactual Clinton Win Frequency}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
   theme_bw() +
-  ylab("Outcome: Frequency of Clinton Winning\nIn 1000 Simulations") +
-  xlab("Input Assumption: Percentile of Manufacturing Layoffs\n") +
+  ylab("Clinton Wins\nIn 1000 Simulations") +
+  xlab("Percentile of Manufacturing Layoffs\n") +
   ggtitle("Counterfactual Presidential Election Simulation Results")
@@
 
-<!-- FIGURE X: V SHAPRED RECOVERY  -->
+<!-- FIGURE X: V SHAPED RECOVERY  -->
 
@@
 \end{figure}
+
+\begin{figure} \label{balPlot}
+\caption{Covariate Balance in Aggregate}
+
+```{r, message = F, fig.width = 5.5, fig.align="center"}
+cbpsObjs <- readRDS("../cbpsObjects.rds")
+plot(cbpsObjs$fit04)
+
+```
+
+\end{figure}
+
+\begin{figure} \label{balPlotWhite}
+\caption{Covariate Balance in Whites}
+
+```{r, message = F, fig.width = 5.5, fig.align="center"}
+plot(cbpsObjs$fit04_white)
+
+```
+
+\end{figure}

### 2021-12-12 Final Draft/Final-Draft.tex
add cbps results

@@
   Zagreb Mukerjee\thanks{
-  Darin: Harvard University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
-  Mukerjee: Harvard University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
+  Darin: Harvard
+University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
+  Mukerjee: Harvard
+University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
   Code available at https://github.com/zagrebmukerjee/ReplicationPaper
@@
 What led to Donald Trump's surprising 2016 election victory? This paper
-examines the potential contribution of deindustrialization. We use an
-instrumental-variable approach and a covariate-balancing approach to
-identify the effect of manufacturing job loss on change in Democratic
-vote share. We find that Democratic vote share falls in counties with
-high manufacturing job loss since 2004. Disaggregating this result by
-race shows that the Democratic vote share fell where layoffs affected
-white populations, and rose where layoffs affected nonwhites. This
-suggests a racial component to how voters process economic hardship.
+examines the potential contribution of deindustrialization. We exploit
+county-level differences in manufacturing density as a source of
+exogenous variation, using both instrumental-variable regression and
+covariate balancing methods. Counterintuitively, we find that counties
+that gained manufacturing jobs from 2012-2015 are more likely to have
+swung towards Trump. We believe this is due to an omitted variable - the
+job loss experienced from 2004 to 2012. Counties that experienced prior
+deindustrialization were more likely to exhibit increased support for
+Trump, as well as a slight manufacturing rebound in 2012-2015.
+Disaggregating this result by race shows that the Democratic vote share
+fell where layoffs affected white populations, and rose where layoffs
+affected nonwhites. This suggests a racial component to how voters
+process economic hardship.
 \end{abstract}
@@
 reduce the correlation between covariates and treatment, while
-addressing several of the issues with propensity score weights. Given
-covariate-balancing weights, we then conduct a single-stage weighted
-regression of change in Democratic vote share on manufacturing job loss,
-using the same controls as above.
-
-XXXXXXXXXXXXXXX BALANCE FIGURE??? XXXXXXXXXXXXXXXXXXXXXXXXXXX
+addressing several of the issues with propensity score weights. We find
+significant imbalance in the data - in other words, it is relatively
+easy to predict the `treatment' of job loss given the covariates (see
+Appendix for balance plots). Given covariate-balancing weights, we then
+conduct a single-stage weighted regression of change in Democratic vote
+share on manufacturing job loss, using the same controls as above.
 
@@
   \label{regResult04} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{Change in Dem. Share, 2016-2012} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+\\[-1.8ex] & \multicolumn{6}{c}{Change in Dem. Share, 2016-2012} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
 \hline \\[-1.8ex] 
- Manufacturing Layoffs & $-$0.34$^{**}$ & $-$0.38$^{**}$ &  &  \\ 
-  & (0.14) & (0.17) &  &  \\ 
-  & & & & \\ 
- White Manufacturing Layoffs &  &  & $-$0.23$^{***}$ & $-$0.32$^{***}$ \\ 
-  &  &  & (0.08) & (0.10) \\ 
-  & & & & \\ 
- Nonwhite Manufacturing Layoffs &  &  & 0.15$^{***}$ & 0.20$^{***}$ \\ 
-  &  &  & (0.05) & (0.06) \\ 
-  & & & & \\ 
+ Job Losses & $-$0.34$^{**}$ & $-$0.38$^{**}$ & $-$0.03$^{***}$ &  &  &  \\ 
+  & (0.14) & (0.17) & (0.01) &  &  &  \\ 
+  & & & & & & \\ 
+ White Job Losses &  &  &  & $-$0.23$^{***}$ & $-$0.32$^{***}$ & $-$0.07$^{***}$ \\ 
+  &  &  &  & (0.08) & (0.10) & (0.02) \\ 
+  & & & & & & \\ 
+ Nonwhite Job Losses &  &  &  & 0.15$^{***}$ & 0.20$^{***}$ & 0.09$^{**}$ \\ 
+  &  &  &  & (0.05) & (0.06) & (0.04) \\ 
+  & & & & & & \\ 
 \hline \\[-1.8ex] 
-White Share/Svc Layoffs Control & No & Yes & No & Yes \\ 
-Observations & 3,049 & 3,049 & 2,750 & 2,750 \\ 
-Adjusted R$^{2}$ & 0.72 & 0.72 & 0.75 & 0.75 \\ 
+White Share/Svc Layoffs & No & Yes & Yes & No & Yes & Yes \\ 
+Covariate Balancing & No & No & Yes & No & No & Yes \\ 
+Observations & 3,049 & 3,049 & 2,750 & 2,750 & 2,750 & 2,750 \\ 
+Adjusted R$^{2}$ & 0.72 & 0.72 & 0.74 & 0.75 & 0.75 & 0.73 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 
@@
 
-\caption{Clinton Electoral College Votes}
+\caption{Counterfactual Presidential Election Simulation Results}
 
@@
 \begin{figure} \label{counterfactual3}
-\caption{Clinton Winning Freq}
+\caption{ Counterfactual Clinton Win Frequency}
 
@@
 
+\begin{figure} \label{balPlot}
+\caption{Covariate Balance in Aggregate}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-12-1} \end{center}
+
+\FloatBarrier
+
+\end{figure}
+
+\begin{figure} \label{balPlotWhite}
+\caption{Covariate Balance in Whites}
+
+\begin{center}\includegraphics{Final-Draft_files/figure-latex/unnamed-chunk-13-1} \end{center}
+
+\FloatBarrier
+
+\end{figure}
+
 \end{document}

### 2021-12-12 rCode/matchingResults.R

@@ -17,7 +17,9 @@ fit04 <- CBPS(mfgNetChange_total ~ LAU_unemp_rate_4y + pers_m_total_share_4y +
 fit04_white <- CBPS(mfgNetChange_white ~ LAU_unemp_rate_4y + pers_m_total_share_4y +
                 pers_coll_share_4y + white_counties_4y + msl_service_pc4y + mfgShare_white + totalEmp_white, data = datasetOurs04Limited, method = "exact")
 
-plot(fit04)
+saveRDS(list(fit04 = fit04, fit04_white = fit04_white), "cbpsObjects.rds")
+
+plot(fit04, main = "COV")
 plot(fit04_white)
 
 balance(fit04)
@@ -121,9 +123,6 @@ stargazer(BW_secondStageModel6, secondStageModelOurs04_6,
 ###############################################################
 
 
-
-
-
 # model 2
 secondStageModelOurs04LW_2 <- felm(
   data = datasetOurs04Limited,
@@ -198,7 +197,15 @@ stargazer(BW_secondStageModel6,
           se = list(rse6_2,
                     rseOurs04LW6_2), type = "text")
 
-
+saveRDS(list(rseOurs04LW2_2 = rseOurs04LW2_2,
+             rseOurs04LW3_2 = rseOurs04LW3_2,
+             rseOurs04LW5_2 = rseOurs04LW5_2,
+             rseOurs04LW6_2 = rseOurs04LW6_2,
+             secondStageModelOurs04LW_2 = secondStageModelOurs04LW_2,
+             secondStageModelOurs04LW_3 = secondStageModelOurs04LW_3,
+             secondStageModelOurs04LW_5 = secondStageModelOurs04LW_5,
+             secondStageModelOurs04LW_6 = secondStageModelOurs04LW_6),
+        "cbpsResults.rds")
 
 ###############################################################
 # now with weights and IV

### 2021-12-12 Final Draft/Final Draft.Rmd

@@
 As shown in Figure \ref{ManuMap}, states across the eastern half of America, particularly in the South and Midwest, have experienced the most pronouncd manufacturing employment losses.
+The localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
+
+This paper analyzes the relationship between deindustrialization, race, and the election of Donald Trump in 2016.
+Previous analysis has  focused on racial animus, trade, or the conjunction of the two on  political polarization and election outcomes (\cite{Autor20}; \cite{Che16}; \cite{BR21}).
+We extend the analysis of \cite{Baccini21}, one of the first papers to examine the political effects of deindustrialization that while considering race and localization.
+Deindustrialization - the transition of the U.S.
+economy away from manufacturing - has led to widespread job loss and created adverse knock-on effects for a wide swath of Americans.
+Our measure of dindustrialization incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
+The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing, as demonstrated in Figure \ref{ManuMap}.
 The localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
@@
 The primary outcome variable is the county's change in Democratic vote share between 2012 and 2016.
-We obtain this from the publically-available replication data provided by \cite{Baccini21}.
+We obtain data on election outocmes and various covariate terms from the publically-available replication data provided by \cite{Baccini21}.
 
@@
 
-In this choice we diverge from \cite{Baccini21}, which uses **gross** manufacturing job losses.
-For example, if a county lost $450$ manufacturing jobs from 2012-2015 and also gained $400$ manufacturing jobs over the same period, this would be $450$ **gross** job losses, but only $50$ **net** job losses.
-The **gross** measure captures several dynamics unrelated to deindustrialization - for example, seasonal unemployment in a food-manufacturing region, or workers moving between jobs.
-Thus we believe the **net** job losses over a period are the more accurate measure.
-It can be argued that the non-seasonal or non-structural components of gross job losses are a useful covariate.
-Basic notions of prospect theory suggest that the loss of a job and subsequent regaining of another identical job may still create substantial discontent.
+In this choice we diverge from \cite{Baccini21}, which uses *gross* manufacturing job losses.
+For example, if a county lost $450$ manufacturing jobs from 2012-2015 and also gained $400$ manufacturing jobs over the same period, this would be $450$ *gross* job losses, but only $50$ *net* job losses.
+The *gross* measure captures several dynamics unrelated to deindustrialization - for example, seasonal unemployment in a food-manufacturing region, or workers moving between jobs.
+Thus we believe the *net* job losses over a period are the more accurate measure.
+Additionally, there is precedent in the literature to use *net* employment changes, as \cite{Autor21} have done.
+Nevertheless, it can be argued that the non-seasonal or non-structural components of gross job losses are a useful covariate.
+For instance, basic notions of prospect theory suggest that the loss of a job and subsequent regaining of another identical job may still create substantial discontent.
 Constructing a better measure of gross job losses is an area for further methodological and substantive research.
@@
 A regression of change in Democratic vote share on manufacturing job losses risks endogeneity, in case counties with manufacturing job losses were otherwise predisposed to turn towards Trump (a singular candidate, after all).
-To mitigate these risks, \cite{Baccini21} uses a Bartik instrument, which we adapt (see \cite{Bartik91}).
+To mitigate these risks, \cite{Baccini21} use a Bartik instrument, which we adapt (see \cite{Bartik91}).
 This instrument essentially uses the cross-county distribution of manufacturing employment as a source of exogenous variation.
@@
 First we estimate manufacturing job loss with the Bartik Instrument and a set of county-level controls; then we use the estimated values of job losses to predict Democratic vote share.
-In these regressions we control for unemployment, service layoffs, the share of college-educated voters, and the share of male voters.
-For some estimates, we also control for the white share of the population.
+In these regressions we control for unemployment, the share of college-educated voters, and the share of male voters.
+For some estimates, we also control for the white share of the population and service layoffs.
 We also apply state fixed effects to account for a wide variety of state-level changes from 2012-2016 (such as voter suppression tactics).
@@
 The results can be found in Table \ref{regResult04}.
-The regression coefficient in Model 4, for instance, means that a loss of $10$ manufacturing jobs per $100$ workers in a county (a relatively extreme value) corresponds to a loss of $3.2 \%$ in Democratic vote share.
+The regression coefficient in Model 4, for instance, means that a loss of $10$ white manufacturing jobs per $100$ workers in a county (a relatively extreme value) corresponds to a $3.2$ percentage point loss in Democratic vote share.
 \FloatBarrier
@@
 Electoral College votes are allocated.
-As an alternative perspective, we examined a range of counterfactual scenarios, in which counties experienced job losses
-<!--  what should I read in the counterfactual -->
+As an alternative perspective, we examined a range of counterfactual scenarios, in which counties manufacturing experienced job losses between the 1st and 99th percentiles across all counties.
+For example, in the map below, we assume that all counties in the US experienced a loss in white manufacturing employment equivalent to the level experienced by a county at the 25th percentile.
+Here, that level is equivalent to a 0 net loss in white manufacturing jobs between 2004-2015 per 100 workers in 2004 (a relatively low level of job losses).
+Setting all counties' white manufacturing job losses to 0, we use the point estimates of our regression coefficients from Model 3 in \ref{regResult04} to estimate the counterfactual change in Democratic vote share.
+We then aggregate our county-level findings to estimate the overall counterfactual change in Democratic vote share at the state level.
+We find that, had all counties experienced the 25th percentile level in manufacturing job losses, most states would have leaned more Democratic in 2016, and that Michigan and Pennsylvania would have flipped.
 

### 2021-12-12 Final Draft/Final Draft.Rmd
updates

--- 2021-12-12 Final Draft/Final Draft.Rmd
@@
 
+Like \cite{Baccini21}, we find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites.
+\cite{Baccini21} find that gross manufacturing layoffs between 2012-2015 were associated with a loss in Democratic vote share.
+However, using a different measure of deindustrialization - *net* change in manufacturing employment - we find the oppposite effect: that counties with manufacturing job *gains* from 2012-2015 tended to swing towards Donald Trump in 2016.
+We extend the analysis to the 2004-2015 period in order to capture the long-term effects of deindustrialization on a region.
+Doing so, we find that regions experiencing more manufacturing job losses swung towards Donald Trump in 2016, and that this occurred more when those losing jobs were white.
+
 Like \cite{Baccini21}, our results suggest that the experience of deindustralization was associated with support for Donald Trump, particularly among whites.
@@
 Electoral College votes are allocated.
-As an alternative perspective, we examined a range of counterfactual scenarios, in which counties experienced job losses
-<!--  what should I read in the counterfactual -->
+As an alternative perspective, we examined a range of counterfactual scenarios, in which counties manufacturing experienced job losses between the 1st and 99th percentiles across all counties.
+
+For example, in the map below, we assume that all counties in the US experienced a loss in white manufacturing employment equivalent to the level experienced by a county at the 25th percentile.
+Here, that level is equivalent to a 0 net loss in white manufacturing jobs between 2004-2015 per 100 workers in 2004 (a relatively low level of job losses).
+Setting all counties' white manufacturing job losses to 0, we use the point estimates of our regression coefficients from Model 3 in Table \ref{regResult04} to estimate the counterfactual change in Democratic vote share.
+We find that, had all counties experienced the 25th percentile level in manufacturing job losses, most states would have leaned more Democratic in 2016, and that Michigan and Pennsylvania would have flipped.
 
@@
 \begin{figure} \label{counterfactual1}
-\caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
+\caption{Counterfactual Scenario: Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
   theme(  axis.title.x=element_blank(),
-          axis.title.y=element_blank())
+          axis.title.y=element_blank(),
+          legend.key.size = unit(.3, 'cm'))
 
@@
 
-\caption{Clinton Electoral College Votes}
+\caption{Counterfactual Simulation Results: Democratic Electoral College Votes Assuming White Manufacturing Job Losses Between 1st and 99th Percentile }
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
 ```
+\begin{figurenotes}
+Figures show a 95% confidence interval for Democratic Electoral College Votes at Each Percentile of Manufacturing Job Losses.
+\end{figurenotes}
 \end{figure}

### 2021-12-12 Final Draft/Final-Draft.tex
updates

--- 2021-12-12 Final Draft/Final-Draft.tex
@@
 concentrated harms of deindustrialization.
+
+This paper analyzes the relationship between deindustrialization, race,
+and the election of Donald Trump in 2016. Previous analysis has focused
+on racial animus, trade, or the conjunction of the two on political
+polarization and election outcomes (\cite{Autor20}; \cite{Che16};
+\cite{BR21}). We extend the analysis of \cite{Baccini21}, one of the
+first papers to examine the political effects of deindustrialization
+that while considering race and localization. Deindustrialization - the
+transition of the U.S. economy away from manufacturing - has led to
+widespread job loss and created adverse knock-on effects for a wide
+swath of Americans. Our measure of dindustrialization incorporates job
+losses due to trade with China and others (see \cite{Acemoglu16}); it
+also includes job losses due to automation, demand changes, and other
+factors. The experience of deindustrialization has not been uniform;
+rather, it has been concentrated in certain areas of the country that
+were previously economically reliant on manufacturing, as demonstrated
+in Figure \ref{ManuMap}. The localized nature of this analysis
+highlights the uneven and concentrated harms of deindustrialization.
 
@@
 covariate balancing.
+
+Like \cite{Baccini21}, we find evidence that the experience of
+deindustralization was associated with support for Donald Trump,
+particularly among whites. \cite{Baccini21} find that gross
+manufacturing layoffs between 2012-2015 were associated with a loss in
+Democratic vote share. However, using a different measure of
+deindustrialization - \emph{net} change in manufacturing employment - we
+find the oppposite effect: that counties with manufacturing job
+\emph{gains} from 2012-2015 tended to swing towards Donald Trump in
+2016. We extend the analysis to the 2004-2015 period in order to capture
+the long-term effects of deindustrialization on a region. Doing so, we
+find that regions experiencing more manufacturing job losses swung
+towards Donald Trump in 2016, and that this occurred more when those
+losing jobs were white.
 
@@
 variable is the county's change in Democratic vote share between 2012
-and 2016. We obtain this from the publically-available replication data
-provided by \cite{Baccini21}.
+and 2016. We obtain data on election outocmes and various covariate
+terms from the publically-available replication data provided by
+\cite{Baccini21}.
 
@@
 
-In this choice we diverge from \cite{Baccini21}, which uses
-\textbf{gross} manufacturing job losses. For example, if a county lost
-\(450\) manufacturing jobs from 2012-2015 and also gained \(400\)
-manufacturing jobs over the same period, this would be \(450\)
-\textbf{gross} job losses, but only \(50\) \textbf{net} job losses. The
-\textbf{gross} measure captures several dynamics unrelated to
-deindustrialization - for example, seasonal unemployment in a
-food-manufacturing region, or workers moving between jobs. Thus we
-believe the \textbf{net} job losses over a period are the more accurate
-measure. It can be argued that the non-seasonal or non-structural
-components of gross job losses are a useful covariate. Basic notions of
-prospect theory suggest that the loss of a job and subsequent regaining
-of another identical job may still create substantial discontent.
-Constructing a better measure of gross job losses is an area for further
-methodological and substantive research.
+In this choice we diverge from \cite{Baccini21}, which uses \emph{gross}
+manufacturing job losses. For example, if a county lost \(450\)
+manufacturing jobs from 2012-2015 and also gained \(400\) manufacturing
+jobs over the same period, this would be \(450\) \emph{gross} job
+losses, but only \(50\) \emph{net} job losses. The \emph{gross} measure
+captures several dynamics unrelated to deindustrialization - for
+example, seasonal unemployment in a food-manufacturing region, or
+workers moving between jobs. Thus we believe the \emph{net} job losses
+over a period are the more accurate measure. Additionally, there is
+precedent in the literature to use \emph{net} employment changes, as
+\cite{Autor21} have done. Nevertheless, it can be argued that the
+non-seasonal or non-structural components of gross job losses are a
+useful covariate. For instance, basic notions of prospect theory suggest
+that the loss of a job and subsequent regaining of another identical job
+may still create substantial discontent. Constructing a better measure
+of gross job losses is an area for further methodological and
+substantive research.
 
@@
 turn towards Trump (a singular candidate, after all). To mitigate these
-risks, \cite{Baccini21} uses a Bartik instrument, which we adapt (see
+risks, \cite{Baccini21} use a Bartik instrument, which we adapt (see
 \cite{Bartik91}). This instrument essentially uses the cross-county
@@
 predict Democratic vote share. In these regressions we control for
-unemployment, service layoffs, the share of college-educated voters, and
-the share of male voters. For some estimates, we also control for the
-white share of the population. We also apply state fixed effects to
+unemployment, the share of college-educated voters, and the share of
+male voters. For some estimates, we also control for the white share of
+the population and service layoffs. We also apply state fixed effects to
 account for a wide variety of state-level changes from 2012-2016 (such
@@
 The results can be found in Table \ref{regResult04}. The regression
-coefficient in Model 4, for instance, means that a loss of \(10\)
+coefficient in Model 4, for instance, means that a loss of \(10\) white
 manufacturing jobs per \(100\) workers in a county (a relatively extreme
-value) corresponds to a loss of \(3.2 \%\) in Democratic vote share.
-\FloatBarrier
+value) corresponds to a \(3.2\) percentage point loss in Democratic vote
+share. \FloatBarrier
 
@@
 College votes are allocated. As an alternative perspective, we examined
-a range of counterfactual scenarios, in which counties experienced job
-losses
+a range of counterfactual scenarios, in which counties manufacturing
+experienced job losses between the 1st and 99th percentiles across all
+counties.
+
+For example, in the map below, we assume that all counties in the US
+experienced a loss in white manufacturing employment equivalent to the
+level experienced by a county at the 25th percentile. Here, that level
+is equivalent to a 0 net loss in white manufacturing jobs between
+2004-2015 per 100 workers in 2004 (a relatively low level of job
+losses). Setting all counties' white manufacturing job losses to 0, we
+use the point estimates of our regression coefficients from Model 3 in
+Table \ref{regResult04} to estimate the counterfactual change in
+Democratic vote share. We find that, had all counties experienced the
+25th percentile level in manufacturing job losses, most states would
+have leaned more Democratic in 2016, and that Michigan and Pennsylvania
+would have flipped.
 
@@
 \begin{figure} \label{counterfactual1}
-\caption{Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
+\caption{Counterfactual Scenario: Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
 
@@
 
-\caption{Clinton Electoral College Votes}
+\caption{Counterfactual Simulation Results: Democratic Electoral College Votes Assuming White Manufacturing Job Losses Between 1st and 99th Percentile }
 
@@
 \end{figure}
+\begin{figurenotes}
+Figures show a 95% confidence interval for Democratic Electoral College Votes at Each Percentile of Manufacturing Job Losses.
+\end{figurenotes}
 \FloatBarrier

### 2021-12-12 Final Draft/Final Draft.Rmd
final draft updates

--- 2021-12-12 Final Draft/Final Draft.Rmd
@@
 library(dplyr)
+library(glmnet)
 library(CBPS)
@@
 As an alternative perspective, we examined a range of counterfactual scenarios, in which counties manufacturing experienced job losses between the 1st and 99th percentiles across all counties.
-For example, in the map below, we assume that all counties in the US experienced a loss in white manufacturing employment equivalent to the level experienced by a county at the 25th percentile.
+
+For example, in the map in Figure \ref{counterfactual1} below, we assume that all counties in the US experienced a loss in white manufacturing employment equivalent to the level experienced by a county at the 25th percentile.
 Here, that level is equivalent to a 0 net loss in white manufacturing jobs between 2004-2015 per 100 workers in 2004 (a relatively low level of job losses).
-Setting all counties' white manufacturing job losses to 0, we use the point estimates of our regression coefficients from Model 3 in \ref{regResult04} to estimate the counterfactual change in Democratic vote share.
-We then aggregate our county-level findings to estimate the overall counterfactual change in Democratic vote share at the state level.
+Setting all counties' white manufacturing job losses to 0, we use the point estimates of our regression coefficients from Model 4 in Table \ref{regResult04} to estimate the counterfactual change in Democratic vote share.
 We find that, had all counties experienced the 25th percentile level in manufacturing job losses, most states would have leaned more Democratic in 2016, and that Michigan and Pennsylvania would have flipped.
@@
 
+We also demonstrate uncertainity around our coefficient estimates using a simulation appraoch.
+Specifically, for each percentile of white manufacturing job losses, we simulate 1,000 election outcomes by drawing from the distribution around our coefficent point estimate 1,000 times (again, using the results from Model 3 in Table \ref{regResult04}).
+In Figure \ref{counterfactual2}, we find that, assuming the 24th percentile or lower of white manufacturing job losses, we find that the median estimate in our simulation shows Democratic winning at least 270 electoral college votes.
+Using the 95\% confidence intervals produced from the simulation exercise, we find that we would be 95\% confident that Democrats would have won the national election had white manufacturing job losses been at the 5th percentile or lower.
+This result suggest that manufacturing job losses would have had to have been substantially lower and *negative* (e.g., job gains) in order for the national election outcome to have been flipped with 95\% confidence.
+
 \FloatBarrier
@@
 
-\caption{Counterfactual Presidential Election Simulation Results}
+\caption{Counterfactual Simulation Results: Democratic Electoral College Votes Assuming White Manufacturing Job Losses Between 1st and 99th Percentile }
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
   theme_bw() +
-  ylab("Clinton Electoral College Votes\n") +
-  xlab("Assumed Percentile of Manufacturing Layoffs\n")   +
+  ylab("Democratic Electoral College Votes\n") +
+  xlab("Assumed Percentile of White Manufacturing Job Losses\n")   +
   theme(axis.title.x = element_text(size = 8), 
@@
 ```
+\begin{figurenotes}
+Figure shows a 95\% confidence interval for Democratic Electoral College Votes at Each Percentile of Manufacturing Job Losses.
+The black dot indicates the median electoral college vote estimate at each percentile.
+The red line shows the 270 electoral vote threshold.
+\end{figurenotes}
 \end{figure}
@@
 
+Finally, using the same simulation approach described above, in Figure \ref{counterfactual3} we illustrate the freuqency with which Demcorats would have won the presidential election (270 votes) given each percentile of white manufacturing job losses.
+Our simulation results show that, when we assumed 24th percentile or lower of white manufacturing job losses,  Democrats won the presidential election in at least 50 percent of simulations.
+When we assumed the 17th percentile or lower, Democrats won the presidential election in at least 75 percent of simulations.
+Taken together, these results suggest that Democrats would have had a significantly higher chance of winning the presidential election had white manufacturing job layoffs been substantially lower.
+
 \FloatBarrier
 \begin{figure} \label{counterfactual3}
-\caption{ Counterfactual Clinton Win Frequency}
+\caption{Counterfactual Simulation Results: Democratic Presidential Win Frequency}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
   theme_bw() +
-  ylab("Clinton Wins\nIn 1000 Simulations") +
-  xlab("Percentile of Manufacturing Layoffs\n") +
-  ggtitle("Counterfactual Presidential Election Simulation Results")
+  ylab("Frequency of Democratic Presidential Win\nIn 1000 Simulations") +
+  xlab("Assumed Percentile of White Manufacturing Job Losses\n") +
+  ggtitle("") + theme(text = element_text(size = 8))
 

### 2021-12-12 Final Draft/Final-Draft.tex
final draft updates

@@
 
-Like \cite{Baccini21}, we find evidence that the experience of
-deindustralization was associated with support for Donald Trump,
-particularly among whites. \cite{Baccini21} find that gross
-manufacturing layoffs between 2012-2015 were associated with a loss in
-Democratic vote share. However, using a different measure of
-deindustrialization - \emph{net} change in manufacturing employment - we
-find the oppposite effect: that counties with manufacturing job
-\emph{gains} from 2012-2015 tended to swing towards Donald Trump in
-2016. We extend the analysis to the 2004-2015 period in order to capture
-the long-term effects of deindustrialization on a region. Doing so, we
-find that regions experiencing more manufacturing job losses swung
-towards Donald Trump in 2016, and that this occurred more when those
-losing jobs were white.
-
 Like \cite{Baccini21}, our results suggest that the experience of
@@
 
+We also demonstrate uncertainity around our coefficient estimates using
+a simulation appraoch. Specifically, for each percentile of white
+manufacturing job losses, we simulate 1,000 election outcomes by drawing
+from the distribution around our coefficent point estimate (again, using
+the results from Model 3 in Table \ref{regResult04}). In Figure
+\ref{counterfactual2}, we find that, assuming the 24th percentile or
+lower of white manufacturing job losses, we find that the median
+estimate in our simulation shows Democratic winning at least 270
+electoral college votes. Using the 95\% confidence intervals produced
+from the simulation exercise, we find that we would only be 95\%
+confident that Democrats would have won the national election had white
+manufacturing job losses been at the 5th percentile or lower. This
+result suggest that manufacturing job losses would have had to have been
+\emph{negative} (e.g., job gains) in order for the national election
+outcome to have been flipped with 95\% confidence.
+
 \FloatBarrier
@@
 \FloatBarrier
+\begin{figurenotes}
+Figure shows a 95\% confidence interval for Democratic Electoral College Votes at Each Percentile of Manufacturing Job Losses.
+The black dot indicates the median electoral college vote estimate at each percentile.
+The red line shows the 270 electoral vote threshold.
+\end{figurenotes}
 \end{figure}
-\begin{figurenotes}
-Figures show a 95% confidence interval for Democratic Electoral College Votes at Each Percentile of Manufacturing Job Losses.
-\end{figurenotes}
 \FloatBarrier
+
+Finally, using the same simulation approach described above, in Figure
+\ref{counterfactual3} we illustrate the freuqency with which Demcorats
+would have won the presidential election (270 votes) given each
+percentile of white manufacturing job losses. Our simulation results
+show that, when we assumed 24th percentile or lower of white
+manufacturing job losses, Democrats won the presidential election in at
+least 50 percent of simulations. When we assumed the 17th percentile or
+lower, Democrats won the presidential election in at least 75 percent of
+simulations. Taken together, these results suggest that Democrats would
+have had a significantly higher chance of winning the presidential
+election had white manufacturing job layoffs been substantially lower.
 
@@
 \begin{figure} \label{counterfactual3}
-\caption{Clinton Winning Freq}
+\caption{Counterfactual Simulation Results: Democratic Presidential Win Frequency}
 

### 2021-12-12 Final Draft/Final Draft.Rmd
updates

@@
 We exploit county-level differences in manufacturing density as a source of exogenous variation, using both instrumental-variable regression and covariate balancing methods.
-Counterintuitively, we find that counties that gained manufacturing jobs from 2012-2015 are more likely to have swung towards Trump.
+Counter-intuitively, we find that counties that gained manufacturing jobs from 2012-2015 are more likely to have swung towards Trump.
 We believe this is due to an omitted variable - the job loss experienced from 2004 to 2012.
 Counties that experienced prior deindustrialization were more likely to exhibit increased support for Trump, as well as a slight manufacturing rebound in 2012-2015.
-Disaggregating this result by race shows that the Democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
+Dis-aggregating this result by race shows that the Democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
 This suggests a racial component to how voters process economic hardship.
@@
 economy away from manufacturing - has led to widespread job loss and created adverse knock-on effects for a wide swath of Americans.
-Our measure of dindustrialization incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
+Our measure of deindustrialization incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
 The experience of deindustrialization has not been uniform; rather, it has been concentrated in areas of the country that were previously economically reliant on manufacturing.
-As shown in Figure \ref{ManuMap}, states across the eastern half of America, particularly in the South and Midwest, have experienced the most pronouncd manufacturing employment losses.
+As shown in Figure \ref{ManuMap}, states across the eastern half of America, particularly in the South and Midwest, have experienced the most pronounced manufacturing employment losses.
 The localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
@@
 economy away from manufacturing - has led to widespread job loss and created adverse knock-on effects for a wide swath of Americans.
-Our measure of dindustrialization incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
+Our measure of deindustrialization incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
 The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing, as demonstrated in Figure \ref{ManuMap}.
@@
 In their central analysis, \cite{Baccini21} analyzed the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.
-\cite{Baccini21} find evidence that the experience of deindustralization was associated with support for Donald Trump, particularly among whites.
+\cite{Baccini21} find evidence that the experience of deindustrialization was associated with support for Donald Trump, particularly among whites.
 
@@
 The primary outcome variable is the county's change in Democratic vote share between 2012 and 2016.
-We obtain data on election outocmes and various covariate terms from the publically-available replication data provided by \cite{Baccini21}.
+We obtain data on election outcomes and various covariate terms from the publicly-available replication data provided by \cite{Baccini21}.
 
@@
 
-We also demonstrate uncertainity around our coefficient estimates using a simulation appraoch.
-Specifically, for each percentile of white manufacturing job losses, we simulate 1,000 election outcomes by drawing from the distribution around our coefficent point estimate 1,000 times (again, using the results from Model 3 in Table \ref{regResult04}).
+We also demonstrate uncertainty around our coefficient estimates using a simulation approach.
+Specifically, for each percentile of white manufacturing job losses, we simulate 1,000 election outcomes by drawing from the distribution around our coefficient point estimate 1,000 times (again, using the results from Model 3 in Table \ref{regResult04}).
 In Figure \ref{counterfactual2}, we find that, assuming the 24th percentile or lower of white manufacturing job losses, we find that the median estimate in our simulation shows Democratic winning at least 270 electoral college votes.
@@
 
-Finally, using the same simulation approach described above, in Figure \ref{counterfactual3} we illustrate the freuqency with which Demcorats would have won the presidential election (270 votes) given each percentile of white manufacturing job losses.
+Using the same simulation approach described above, in Figure \ref{counterfactual3} we illustrate the frequency with which Democrats would have won the presidential election (270 votes) given each percentile of white manufacturing job losses.
 Our simulation results show that, when we assumed 24th percentile or lower of white manufacturing job losses,  Democrats won the presidential election in at least 50 percent of simulations.
@@
 Taken together, these results suggest that Democrats would have had a significantly higher chance of winning the presidential election had white manufacturing job layoffs been substantially lower.
+
+Finally, it is important to note that, in the counterfactual and simulation exercises shown in Figures \ref{counterfactual1}, \ref{counterfactual2}, and \ref{counterfactual3}, we estimate the change in Democratic vote share assuming various levels of white manufacturing job losses *holding all else equal, including non-white manufacturing job losses.* Given that white and non-white manufacturing job losses are weakly-to-moderately correlated across counties (r = .33), this is likely a poor assumption, because, in reality, a decline in white manufacturing job losses would likely correspond to a decline in non-white manufacturing job losses.
+Given that non-white manufacturing job losses were expected to *increase* Democratic vote share in 2016, this means that our simulation results may be overestimating effect sizes because it does not take into account this second-order impact.
 
@@
 
-\begin{figure} \label{vShapePlot}
-\caption{V-Shaped Recovery in Manufacturing Job Losses}
+\begin{figure} \label{vShapePlot1}
+\caption{V-Shaped Recovery in Manufacturing Job Losses: Manufacturing Job Losses (2004-2011) by (2004-2011) Decile Groupings}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
@@
   theme_minimal() +
-  ylab("Manufacturing Layoffs (04-11)") +
-  xlab("Decile")+
-  ggtitle("Manufacturing Layoffs from 2004-2011 by Deciles") +
+  ylab("Manufacturing Losses (04-11)") +
+  xlab("Deciles")+
+  ggtitle("Manufacturing Job Losses from 2004-2011 by Deciles") +
   geom_col(fill = "#4287f5") +
@@
 \begin{figurenotes}
-"Stuff here"
+Deciles are determined based on our preferred measure of deindustrialization: total net manufacturing job losses from 2004-2015 divided by total 2004 employment.
+Counties in decile 1 had the lowest manufacturing job losses (i.e., an increase in manufacturing employment) while counties in decile 10 had the highest manufacturing job losses.
+The y-axis shows the mean measure of manufacturing job lossess (2004-2015) per 2004 worker across counties in each decile group.
 \end{figurenotes}
@@
 
-\begin{figure} \label{vShapePlot}
-\caption{V-Shaped Recovery in Manufacturing Job Losses}
+\begin{figure} \label{vShapePlot2}
+\caption{V-Shaped Recovery in Manufacturing Job Losses: Manufacturing Job Losses (2012-2015) by 2004-2011 Decile Groupings}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
@@
 \begin{figurenotes}
-"Stuff here"
+Deciles are determined based on our preferred measure of deindustrialization: total net manufacturing job losses from 2004-2015 divided by total 2004 employment.
+The y-axis shows the mean measure of manufacturing job losses (2012-2015) per 2011 worker across counties in each decile group.
+The chart shows that counties with the most manufacturing job losses from 2004-2011 (e.g., in the highest deciles) experienced the most manufacturing *gains* from 2012-2015.
 \end{figurenotes}

### 2021-12-12 Final Draft/Final-Draft.tex
updates

@@
 
-For example, in the map below, we assume that all counties in the US
-experienced a loss in white manufacturing employment equivalent to the
-level experienced by a county at the 25th percentile. Here, that level
-is equivalent to a 0 net loss in white manufacturing jobs between
-2004-2015 per 100 workers in 2004 (a relatively low level of job
-losses). Setting all counties' white manufacturing job losses to 0, we
-use the point estimates of our regression coefficients from Model 3 in
-Table \ref{regResult04} to estimate the counterfactual change in
-Democratic vote share. We find that, had all counties experienced the
-25th percentile level in manufacturing job losses, most states would
-have leaned more Democratic in 2016, and that Michigan and Pennsylvania
-would have flipped.
+For example, in the map in Figure \ref{counterfactual1} below, we assume
+that all counties in the US experienced a loss in white manufacturing
+employment equivalent to the level experienced by a county at the 25th
+percentile. Here, that level is equivalent to a 0 net loss in white
+manufacturing jobs between 2004-2015 per 100 workers in 2004 (a
+relatively low level of job losses). Setting all counties' white
+manufacturing job losses to 0, we use the point estimates of our
+regression coefficients from Model 4 in Table \ref{regResult04} to
+estimate the counterfactual change in Democratic vote share. We find
+that, had all counties experienced the 25th percentile level in
+manufacturing job losses, most states would have leaned more Democratic
+in 2016, and that Michigan and Pennsylvania would have flipped.
 
@@
 manufacturing job losses, we simulate 1,000 election outcomes by drawing
-from the distribution around our coefficent point estimate (again, using
-the results from Model 3 in Table \ref{regResult04}). In Figure
-\ref{counterfactual2}, we find that, assuming the 24th percentile or
-lower of white manufacturing job losses, we find that the median
+from the distribution around our coefficent point estimate 1,000 times
+(again, using the results from Model 3 in Table \ref{regResult04}). In
+Figure \ref{counterfactual2}, we find that, assuming the 24th percentile
+or lower of white manufacturing job losses, we find that the median
 estimate in our simulation shows Democratic winning at least 270
 electoral college votes. Using the 95\% confidence intervals produced
-from the simulation exercise, we find that we would only be 95\%
-confident that Democrats would have won the national election had white
+from the simulation exercise, we find that we would be 95\% confident
+that Democrats would have won the national election had white
 manufacturing job losses been at the 5th percentile or lower. This
 result suggest that manufacturing job losses would have had to have been
-\emph{negative} (e.g., job gains) in order for the national election
-outcome to have been flipped with 95\% confidence.
+substantially lower and \emph{negative} (e.g., job gains) in order for
+the national election outcome to have been flipped with 95\% confidence.
 
@@
 
-Finally, using the same simulation approach described above, in Figure
+Using the same simulation approach described above, in Figure
 \ref{counterfactual3} we illustrate the freuqency with which Demcorats
@@
 election had white manufacturing job layoffs been substantially lower.
+
+Finally, it is important to note that, in the counterfactual and
+simulation exercises shown in Figures \ref{counterfactual1},
+\ref{counterfactual2}, and \ref{counterfactual3}, we estimate the change
+in Democratic vote share assuming various levels of white manufacturing
+job losses \emph{holding all else equal, including non-white
+manufacturing job losses.} Given that white and non-white manufacturing
+job losses are weakly-to-moderately correlated across counties (r =
+.33), this is likely a poor assumption, because, in reality, a decline
+in white manufacturing job losses would likely correspond to a decline
+in non-white manufacturing job losses. Given that non-white
+manufacturing job losses were expected to \emph{increase} Democratic
+vote share in 2016, this means that our simulation results may be
+overestimating effect sizes because it does not take into account this
+second-order impact.
 

### 2021-12-12 Final Draft/Final Draft.Rmd
updates

@@
 Counties that experienced prior deindustrialization were more likely to exhibit increased support for Trump, as well as a slight manufacturing rebound in 2012-2015.
-Dis-aggregating this result by race shows that the Democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites.
+Dis-aggregating this result by race shows that the Democratic vote share fell where job losses affected white populations, and rose where job losses affected nonwhites.
 This suggests a racial component to how voters process economic hardship.
@@
 We get similar result using our covariate-matching approach.
-Relative to \cite{Baccini21}, our results point to the substantive importance of the timing of manufacturing layoffs on political outcomes.
+Relative to \cite{Baccini21}, our results point to the substantive importance of the timing of manufacturing job losses on political outcomes.
 
@@
 
-Finally, it is important to note that, in the counterfactual and simulation exercises shown in Figures \ref{counterfactual1}, \ref{counterfactual2}, and \ref{counterfactual3}, we estimate the change in Democratic vote share assuming various levels of white manufacturing job losses *holding all else equal, including non-white manufacturing job losses.* Given that white and non-white manufacturing job losses are weakly-to-moderately correlated across counties (r = .33), this is likely a poor assumption, because, in reality, a decline in white manufacturing job losses would likely correspond to a decline in non-white manufacturing job losses.
+It is important to note that, in the counterfactual and simulation exercises shown in Figures \ref{counterfactual1}, \ref{counterfactual2}, and \ref{counterfactual3}, we estimate the change in Democratic vote share assuming various levels of white manufacturing job losses *holding all else equal, including non-white manufacturing job losses.* Given that white and non-white manufacturing job losses are weakly-to-moderately correlated across counties (r = .33), this is likely a poor assumption, because, in reality, a decline in white manufacturing job losses would likely correspond to a decline in non-white manufacturing job losses.
 Given that non-white manufacturing job losses were expected to *increase* Democratic vote share in 2016, this means that our simulation results may be overestimating effect sizes because it does not take into account this second-order impact.
@@
 \FloatBarrier
+
+More broadly, we would like to acknowledge our focus on white manufacturing job losses over non-white manufacturing job losses.
+We focus on white manufacturing job losses for two reasons.
+First, in the United States, manufacturing employment and job losses have historically been predominately white (See Table \ref{tab:descTable}).
+Second, our regression results (See Table \ref{regResult04}) suggest that white manufacturing job losses have a larger negative effect on Democratic vote share relative to the magnitude of the positive effect from non-white manufacturing job losses.
+For these reasons, our results suggest that, in aggregate, white manufacturing job losses have had larger effect on political outcomes than non-white manufacturing job losses.
+However, we would like to highlight that the political consequences from non-white manufacturing job losses is a topic that is under-explored in this paper, and is an important area for future work.
+
 \subsubsection{Timing}
@@
   theme_minimal() +
-  ylab("Manufacturing Losses (04-11)") +
-  xlab("Deciles")+
-  ggtitle("Manufacturing Job Losses from 2004-2011 by Deciles") +
+  ylab("Mean Manufacturing Job Losses (04-11)") +
+  xlab("Decile of Manufacturing Job Losses (04-11)")+
+  ggtitle("") +
   geom_col(fill = "#4287f5") +
-  scale_x_continuous(breaks=seq(1,10,1))
+  scale_x_continuous(breaks=seq(1,10,1))  + theme(text = element_text(size = 8))
 
@@
 Counties in decile 1 had the lowest manufacturing job losses (i.e., an increase in manufacturing employment) while counties in decile 10 had the highest manufacturing job losses.
-The y-axis shows the mean measure of manufacturing job lossess (2004-2015) per 2004 worker across counties in each decile group.
+The y-axis shows the mean measure of manufacturing job losses (2004-2015) per 2004 worker across counties in each decile group.
 \end{figurenotes}
@@
   theme_minimal() +
-  ylab("Manufacturing Layoffs (12-15)") +
-  xlab("Decile of Manufacturing Layoffs (04-11)")+
-  ggtitle("Manufacturing Layoffs from 2012-2015 by 2004-2011 Deciles") +
+  ylab("Mean Manufacturing Job Losses (12-15)") +
+  xlab("Decile of Manufacturing Job Losses (04-11)")+
+  ggtitle("") +
   geom_col(fill = "#4287f5") +
-  scale_x_continuous(breaks=seq(1,10,1))
+  scale_x_continuous(breaks=seq(1,10,1)) + theme(text = element_text(size = 8))
 

### 2021-12-12 Final Draft/Final-Draft.tex
updates

@@
 exogenous variation, using both instrumental-variable regression and
-covariate balancing methods. Counterintuitively, we find that counties
+covariate balancing methods. Counter-intuitively, we find that counties
 that gained manufacturing jobs from 2012-2015 are more likely to have
@@
 Trump, as well as a slight manufacturing rebound in 2012-2015.
-Disaggregating this result by race shows that the Democratic vote share
+Dis-aggregating this result by race shows that the Democratic vote share
 fell where layoffs affected white populations, and rose where layoffs
@@
 knock-on effects for a wide swath of Americans. Our measure of
-dindustrialization incorporates job losses due to trade with China and
+deindustrialization incorporates job losses due to trade with China and
 others (see \cite{Acemoglu16}); it also includes job losses due to
@@
 across the eastern half of America, particularly in the South and
-Midwest, have experienced the most pronouncd manufacturing employment
+Midwest, have experienced the most pronounced manufacturing employment
 losses. The localized nature of this analysis highlights the uneven and
@@
 widespread job loss and created adverse knock-on effects for a wide
-swath of Americans. Our measure of dindustrialization incorporates job
+swath of Americans. Our measure of deindustrialization incorporates job
 losses due to trade with China and others (see \cite{Acemoglu16}); it
@@
 vote share in the 2016 presidential election. \cite{Baccini21} find
-evidence that the experience of deindustralization was associated with
+evidence that the experience of deindustrialization was associated with
 support for Donald Trump, particularly among whites.
@@
 variable is the county's change in Democratic vote share between 2012
-and 2016. We obtain data on election outocmes and various covariate
-terms from the publically-available replication data provided by
+and 2016. We obtain data on election outcomes and various covariate
+terms from the publicly-available replication data provided by
 \cite{Baccini21}.
@@
 
-We also demonstrate uncertainity around our coefficient estimates using
-a simulation appraoch. Specifically, for each percentile of white
+We also demonstrate uncertainty around our coefficient estimates using a
+simulation approach. Specifically, for each percentile of white
 manufacturing job losses, we simulate 1,000 election outcomes by drawing
-from the distribution around our coefficent point estimate 1,000 times
+from the distribution around our coefficient point estimate 1,000 times
 (again, using the results from Model 3 in Table \ref{regResult04}). In
@@
 Using the same simulation approach described above, in Figure
-\ref{counterfactual3} we illustrate the freuqency with which Demcorats
+\ref{counterfactual3} we illustrate the frequency with which Democrats
 would have won the presidential election (270 votes) given each
@@
 
-Finally, it is important to note that, in the counterfactual and
-simulation exercises shown in Figures \ref{counterfactual1},
-\ref{counterfactual2}, and \ref{counterfactual3}, we estimate the change
-in Democratic vote share assuming various levels of white manufacturing
-job losses \emph{holding all else equal, including non-white
-manufacturing job losses.} Given that white and non-white manufacturing
-job losses are weakly-to-moderately correlated across counties (r =
-.33), this is likely a poor assumption, because, in reality, a decline
-in white manufacturing job losses would likely correspond to a decline
-in non-white manufacturing job losses. Given that non-white
-manufacturing job losses were expected to \emph{increase} Democratic
-vote share in 2016, this means that our simulation results may be
-overestimating effect sizes because it does not take into account this
-second-order impact.
+It is important to note that, in the counterfactual and simulation
+exercises shown in Figures \ref{counterfactual1}, \ref{counterfactual2},
+and \ref{counterfactual3}, we estimate the change in Democratic vote
+share assuming various levels of white manufacturing job losses
+\emph{holding all else equal, including non-white manufacturing job
+losses.} Given that white and non-white manufacturing job losses are
+weakly-to-moderately correlated across counties (r = .33), this is
+likely a poor assumption, because, in reality, a decline in white
+manufacturing job losses would likely correspond to a decline in
+non-white manufacturing job losses. Given that non-white manufacturing
+job losses were expected to \emph{increase} Democratic vote share in
+2016, this means that our simulation results may be overestimating
+effect sizes because it does not take into account this second-order
+impact.
 
@@
 \FloatBarrier
+
+Finally, we would like to acknowledge our focus on white manufacturing
+job losses over non-white manufacturing job losses. In this analysis, we
+focus on white manufacturing job losses for two reasons. First, in the
+United States, manufacturing employment and job losses have historically
+been predominately white (See Table \ref{tab:descTable}). Second, our
+results suggest that the white manufacturing job losses have a larger
+negative effect on Democratic vote share relative to the magnitude of
+the positive effect from non-white manufacturing losses. For these
+reasons, our results suggest that, in aggregate, white-manufacturing
+losses have had a more significant effect on political outcomes than
+non-white manufacturing job losses. However, we would like to highlight
+that the political consequences from non-white deindustrialization is an
+important area for future work.
+
 \subsubsection{Timing}
@@
 
-\begin{figure} \label{vShapePlot}
-\caption{V-Shaped Recovery in Manufacturing Job Losses}
+\begin{figure} \label{vShapePlot1}
+\caption{V-Shaped Recovery in Manufacturing Job Losses: Manufacturing Job Losses (2004-2011) by (2004-2011) Decile Groupings}
 
@@
 \begin{figurenotes}
-"Stuff here"
+Deciles are determined based on our preferred measure of deindustrialization: total net manufacturing job losses from 2004-2015 divided by total 2004 employment.
+Counties in decile 1 had the lowest manufacturing job losses (i.e., an increase in manufacturing employment) while counties in decile 10 had the highest manufacturing job losses.
+The y-axis shows the mean measure of manufacturing job losses (2004-2015) per 2004 worker across counties in each decile group.
 \end{figurenotes}
@@
 
-\begin{figure} \label{vShapePlot}
-\caption{V-Shaped Recovery in Manufacturing Job Losses}
+\begin{figure} \label{vShapePlot2}
+\caption{V-Shaped Recovery in Manufacturing Job Losses: Manufacturing Job Losses (2012-2015) by 2004-2011 Decile Groupings}
 

### 2021-12-12 Final Draft/Final Draft.Rmd
figure fix, small changes

--- 2021-12-12 Final Draft/Final Draft.Rmd
@@
 \FloatBarrier
-\begin{figure} \label{ManuMap}
+\begin{figure} 
 \caption{Concentration of Deindustrialization (2004-2015) in the eastern United States }
+\label{ManuMap}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center" , regfloat=FALSE}
@@
 \FloatBarrier
-\begin{figure} \label{natlPlotTS}
+\begin{figure}
 \caption{Nationwide Change in Manufacturing Employment, 1995-2019}
+\label{natlPlotTS}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
           type = "latex",
-          label = "regResult04"
+          label = "regResult04", column.sep.width = "2pt", font.size = "small"
 )
@@
 \FloatBarrier
-\begin{figure} \label{counterfactual1}
+\begin{figure} 
 \caption{Counterfactual Scenario: Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
+\label{counterfactual1}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
 \FloatBarrier
-\begin{figure} \label{counterfactual2}
+\begin{figure}
 
 \caption{Counterfactual Simulation Results: Democratic Electoral College Votes Assuming White Manufacturing Job Losses Between 1st and 99th Percentile }
+\label{counterfactual2}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
 \FloatBarrier
-\begin{figure} \label{counterfactual3}
+\begin{figure} 
 \caption{Counterfactual Simulation Results: Democratic Presidential Win Frequency}
+\label{counterfactual3}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}
@@
 As discussed above, the 2012-2015 period can be broadly characterized as a slight rebound from the manufacturing job losses in the 2008 financial crisis.
-The counties that experience job losses from 2004-2012 are more likely to have job gains in 2012-2015 (see \ref{vShapePlot}).
+The counties that experience job losses from 2004-2012 are more likely to have job gains in 2012-2015 (see \ref{fig:vShapePlot1}).
 An apparent relationship between 2012-2015 job gains and loss of Democratic vote share in fact represents 2004-2012 job losses that may lead to both the later job gains and the loss of vote share.
@@
 
-\begin{figure} \label{vShapePlot1}
+\begin{figure} 
 \caption{V-Shaped Recovery in Manufacturing Job Losses: Manufacturing Job Losses (2004-2011) by (2004-2011) Decile Groupings}
+\label{fig:vShapePlot1}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
@@
 
-\begin{figure} \label{vShapePlot2}
+\begin{figure} 
 \caption{V-Shaped Recovery in Manufacturing Job Losses: Manufacturing Job Losses (2012-2015) by 2004-2011 Decile Groupings}
+\label{vShapePlot2}
 ```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
@@
 
-\begin{figure} \label{balPlot}
+\begin{figure} 
 \caption{Covariate Balance in Aggregate}
-
+\label{balPlot}
 ```{r, message = F, fig.width = 5.5, fig.align="center"}
@@
 
-\begin{figure} \label{balPlotWhite}
+\begin{figure} 
 \caption{Covariate Balance in Whites}
-
+\label{balPlotWhite}
 ```{r, message = F, fig.width = 5.5, fig.align="center"}

### 2021-12-12 Final Draft/Final-Draft.tex
figure fix, small changes

@@
 \FloatBarrier
-\begin{figure} \label{ManuMap}
+\begin{figure} 
 \caption{Concentration of Deindustrialization (2004-2015) in the eastern United States }
+\label{ManuMap}
 
@@
 \FloatBarrier
-\begin{figure} \label{natlPlotTS}
+\begin{figure}
 \caption{Nationwide Change in Manufacturing Employment, 1995-2019}
+\label{natlPlotTS}
 
@@
   \label{regResult04} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
+\small 
+\begin{tabular}{@{\extracolsep{2pt}}lcccccc} 
 \\[-1.8ex]\hline 
@@
 \FloatBarrier
-\begin{figure} \label{counterfactual1}
+\begin{figure} 
 \caption{Counterfactual Scenario: Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses}
+\label{counterfactual1}
 
@@
 \FloatBarrier
-\begin{figure} \label{counterfactual2}
+\begin{figure}
 
 \caption{Counterfactual Simulation Results: Democratic Electoral College Votes Assuming White Manufacturing Job Losses Between 1st and 99th Percentile }
+\label{counterfactual2}
 
@@
 
-It is important to note that, in the counterfactual and simulation
-exercises shown in Figures \ref{counterfactual1}, \ref{counterfactual2},
-and \ref{counterfactual3}, we estimate the change in Democratic vote
-share assuming various levels of white manufacturing job losses
-\emph{holding all else equal, including non-white manufacturing job
-losses.} Given that white and non-white manufacturing job losses are
-weakly-to-moderately correlated across counties (r = .33), this is
-likely a poor assumption, because, in reality, a decline in white
-manufacturing job losses would likely correspond to a decline in
-non-white manufacturing job losses. Given that non-white manufacturing
-job losses were expected to \emph{increase} Democratic vote share in
-2016, this means that our simulation results may be overestimating
-effect sizes because it does not take into account this second-order
-impact.
+Finally, it is important to note that, in the counterfactual and
+simulation exercises shown in Figures \ref{counterfactual1},
+\ref{counterfactual2}, and \ref{counterfactual3}, we estimate the change
+in Democratic vote share assuming various levels of white manufacturing
+job losses \emph{holding all else equal, including non-white
+manufacturing job losses.} Given that white and non-white manufacturing
+job losses are weakly-to-moderately correlated across counties (r =
+.33), this is likely a poor assumption, because, in reality, a decline
+in white manufacturing job losses would likely correspond to a decline
+in non-white manufacturing job losses. Given that non-white
+manufacturing job losses were expected to \emph{increase} Democratic
+vote share in 2016, this means that our simulation results may be
+overestimating effect sizes because it does not take into account this
+second-order impact.
 
 \FloatBarrier
-\begin{figure} \label{counterfactual3}
+\begin{figure} 
 \caption{Counterfactual Simulation Results: Democratic Presidential Win Frequency}
+\label{counterfactual3}
 
@@
 \FloatBarrier
-
-Finally, we would like to acknowledge our focus on white manufacturing
-job losses over non-white manufacturing job losses. In this analysis, we
-focus on white manufacturing job losses for two reasons. First, in the
-United States, manufacturing employment and job losses have historically
-been predominately white (See Table \ref{tab:descTable}). Second, our
-results suggest that the white manufacturing job losses have a larger
-negative effect on Democratic vote share relative to the magnitude of
-the positive effect from non-white manufacturing losses. For these
-reasons, our results suggest that, in aggregate, white-manufacturing
-losses have had a more significant effect on political outcomes than
-non-white manufacturing job losses. However, we would like to highlight
-that the political consequences from non-white deindustrialization is an
-important area for future work.
-
 \subsubsection{Timing}
@@
 2004-2012 are more likely to have job gains in 2012-2015 (see
-\ref{vShapePlot}). An apparent relationship between 2012-2015 job gains
-and loss of Democratic vote share in fact represents 2004-2012 job
+\ref{fig:vShapePlot1}). An apparent relationship between 2012-2015 job
+gains and loss of Democratic vote share in fact represents 2004-2012 job
 losses that may lead to both the later job gains and the loss of vote
@@
 
-\begin{figure} \label{vShapePlot1}
+\begin{figure} 
 \caption{V-Shaped Recovery in Manufacturing Job Losses: Manufacturing Job Losses (2004-2011) by (2004-2011) Decile Groupings}
+\label{fig:vShapePlot1}
 
@@
 Counties in decile 1 had the lowest manufacturing job losses (i.e., an increase in manufacturing employment) while counties in decile 10 had the highest manufacturing job losses.
-The y-axis shows the mean measure of manufacturing job losses (2004-2015) per 2004 worker across counties in each decile group.
+The y-axis shows the mean measure of manufacturing job lossess (2004-2015) per 2004 worker across counties in each decile group.
 \end{figurenotes}
@@
 
-\begin{figure} \label{vShapePlot2}
+\begin{figure} 
 \caption{V-Shaped Recovery in Manufacturing Job Losses: Manufacturing Job Losses (2012-2015) by 2004-2011 Decile Groupings}
+\label{vShapePlot2}
 
@@
 
-\begin{figure} \label{balPlot}
+\begin{figure} 
 \caption{Covariate Balance in Aggregate}
+\label{balPlot}
 
@@
 
-\begin{figure} \label{balPlotWhite}
+\begin{figure} 
 \caption{Covariate Balance in Whites}
+\label{balPlotWhite}
 

### 2021-12-12 Final Draft/Final-Draft.tex

--- 2021-12-12 Final Draft/Final-Draft.tex
@@
 Dis-aggregating this result by race shows that the Democratic vote share
-fell where layoffs affected white populations, and rose where layoffs
-affected nonwhites. This suggests a racial component to how voters
-process economic hardship.
+fell where job losses affected white populations, and rose where job
+losses affected nonwhites. This suggests a racial component to how
+voters process economic hardship.
 \end{abstract}
@@
 \cite{Baccini21}, our results point to the substantive importance of the
-timing of manufacturing layoffs on political outcomes.
+timing of manufacturing job losses on political outcomes.
 
 \FloatBarrier
-\begin{figure} \label{natlPlotTS}
+\begin{figure}
 \caption{Nationwide Change in Manufacturing Employment, 1995-2019}
+\label{natlPlotTS}
 
@@
 \FloatBarrier
-\begin{figure} \label{counterfactual3}
+\begin{figure} 
 \caption{Counterfactual Simulation Results: Democratic Presidential Win Frequency}
+\label{counterfactual3}
 
@@
 
-Finally, we would like to acknowledge our focus on white manufacturing
-job losses over non-white manufacturing job losses. In this analysis, we
+More broadly, we would like to acknowledge our focus on white
+manufacturing job losses over non-white manufacturing job losses. We
 focus on white manufacturing job losses for two reasons. First, in the
@@
 been predominately white (See Table \ref{tab:descTable}). Second, our
-results suggest that the white manufacturing job losses have a larger
-negative effect on Democratic vote share relative to the magnitude of
-the positive effect from non-white manufacturing losses. For these
-reasons, our results suggest that, in aggregate, white-manufacturing
-losses have had a more significant effect on political outcomes than
-non-white manufacturing job losses. However, we would like to highlight
-that the political consequences from non-white deindustrialization is an
-important area for future work.
+regression results (See Table \ref{regResult04}) suggest that white
+manufacturing job losses have a larger negative effect on Democratic
+vote share relative to the magnitude of the positive effect from
+non-white manufacturing job losses. For these reasons, our results
+suggest that, in aggregate, white manufacturing job losses have had
+larger effect on political outcomes than non-white manufacturing job
+losses. However, we would like to highlight that the political
+consequences from non-white manufacturing job losses is a topic that is
+under-explored in this paper, and is an important area for future work.
 

### 2021-12-13 Final Draft/Final Draft.Rmd
updates
tiny tweaks

@@
 The y-axis shows the mean measure of manufacturing job losses (2012-2015) per 2011 worker across counties in each decile group.
-The chart shows that counties with the most manufacturing job losses from 2004-2011 (e.g., in the highest deciles) experienced the most manufacturing *gains* from 2012-2015.
+The chart shows that counties with the most manufacturing job losses from 2004-2011 (i.e.
+in the highest deciles) experienced the most manufacturing *gains* from 2012-2015.
 \end{figurenotes}

### 2021-12-13 Final Draft/Final Draft.Rmd
updates

--- 2021-12-12 Final Draft/Final Draft.Rmd
@@
 As shown in Figure \ref{ManuMap}, states across the eastern half of America, particularly in the South and Midwest, have experienced the most pronounced manufacturing employment losses.
-The localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
-
-This paper analyzes the relationship between deindustrialization, race, and the election of Donald Trump in 2016.
-Previous analysis has  focused on racial animus, trade, or the conjunction of the two on  political polarization and election outcomes (\cite{Autor20}; \cite{Che16}; \cite{BR21}).
-We extend the analysis of \cite{Baccini21}, one of the first papers to examine the political effects of deindustrialization that while considering race and localization.
-Deindustrialization - the transition of the U.S.
-economy away from manufacturing - has led to widespread job loss and created adverse knock-on effects for a wide swath of Americans.
-Our measure of deindustrialization incorporates job losses due to trade with China and others (see \cite{Acemoglu16}); it also includes job losses due to automation, demand changes, and other factors.
-The experience of deindustrialization has not been uniform; rather, it has been concentrated in certain areas of the country that were previously economically reliant on manufacturing, as demonstrated in Figure \ref{ManuMap}.
 The localized nature of this analysis highlights the uneven and concentrated harms of deindustrialization.
@@
 At the end there are only $1500$ manufacturing workers.
-Using our measure of net change in manufacturing employment, this is a loss of $500/10000 = 5\%.$
+Using our measure of net manufacturing job losses, this is a loss of $500/10000 = 5\%.$
 
@@
 The *gross* measure captures several dynamics unrelated to deindustrialization - for example, seasonal unemployment in a food-manufacturing region, or workers moving between jobs.
-Thus we believe the *net* job losses over a period are the more accurate measure.
+Thus we believe the *net* job losses over a period are the more accurate measure of deindustrialization.
 Additionally, there is precedent in the literature to use *net* employment changes, as \cite{Autor21} have done.
@@
 Our first test involves an instrumental-variable approach.
-A regression of change in Democratic vote share on manufacturing job losses risks endogeneity, in case counties with manufacturing job losses were otherwise predisposed to turn towards Trump (a singular candidate, after all).
+A regression of change in Democratic vote share on manufacturing job losses risks endogeneity, in case counties with manufacturing job losses were otherwise predisposed to turn towards Trump.
 To mitigate these risks, \cite{Baccini21} use a Bartik instrument, which we adapt (see \cite{Bartik91}).
@@
 
-Our second approach involves attempting to balance the covariates of the deindustrialization treatment.
+A potential weakness of our first approach is that manufacturing employment may be correlated with swinging towards Trump for reasons other than manufacturing job losses.
+To account for this potential ommitted variable bias, we use a second approach that attempts to balance the covariates of the deindustrialization treatment.
 We use the same covariates as are used in controls above, as well as manufacturing as share of the population and total population.
@@
 Given covariate-balancing weights, we then conduct a single-stage weighted regression of change in Democratic vote share on manufacturing job loss, using the same controls as above.
+Essentially, this approach can be conceptualized as a form of matching that reduces the potential ommitted variable bias in our first approach, but may introduce selection bias (as some counties will be given low weights).
 

### 2021-12-13 Final Draft/Final-Draft.tex
updates

@@
 concentrated harms of deindustrialization.
-
-This paper analyzes the relationship between deindustrialization, race,
-and the election of Donald Trump in 2016. Previous analysis has focused
-on racial animus, trade, or the conjunction of the two on political
-polarization and election outcomes (\cite{Autor20}; \cite{Che16};
-\cite{BR21}). We extend the analysis of \cite{Baccini21}, one of the
-first papers to examine the political effects of deindustrialization
-that while considering race and localization. Deindustrialization - the
-transition of the U.S. economy away from manufacturing - has led to
-widespread job loss and created adverse knock-on effects for a wide
-swath of Americans. Our measure of deindustrialization incorporates job
-losses due to trade with China and others (see \cite{Acemoglu16}); it
-also includes job losses due to automation, demand changes, and other
-factors. The experience of deindustrialization has not been uniform;
-rather, it has been concentrated in certain areas of the country that
-were previously economically reliant on manufacturing, as demonstrated
-in Figure \ref{ManuMap}. The localized nature of this analysis
-highlights the uneven and concentrated harms of deindustrialization.
 
@@
 \(8000\) non-manufacturing workers. At the end there are only \(1500\)
-manufacturing workers. Using our measure of net change in manufacturing
-employment, this is a loss of \(500/10000 = 5\%.\)
+manufacturing workers. Using our measure of net manufacturing job
+losses, this is a loss of \(500/10000 = 5\%.\)
 
@@
 workers moving between jobs. Thus we believe the \emph{net} job losses
-over a period are the more accurate measure. Additionally, there is
-precedent in the literature to use \emph{net} employment changes, as
-\cite{Autor21} have done. Nevertheless, it can be argued that the
-non-seasonal or non-structural components of gross job losses are a
-useful covariate. For instance, basic notions of prospect theory suggest
-that the loss of a job and subsequent regaining of another identical job
-may still create substantial discontent. Constructing a better measure
-of gross job losses is an area for further methodological and
-substantive research.
+over a period are the more accurate measure of deindustrialization.
+Additionally, there is precedent in the literature to use \emph{net}
+employment changes, as \cite{Autor21} have done. Nevertheless, it can be
+argued that the non-seasonal or non-structural components of gross job
+losses are a useful covariate. For instance, basic notions of prospect
+theory suggest that the loss of a job and subsequent regaining of
+another identical job may still create substantial discontent.
+Constructing a better measure of gross job losses is an area for further
+methodological and substantive research.
 
@@
 counties with manufacturing job losses were otherwise predisposed to
-turn towards Trump (a singular candidate, after all). To mitigate these
-risks, \cite{Baccini21} use a Bartik instrument, which we adapt (see
-\cite{Bartik91}). This instrument essentially uses the cross-county
-distribution of manufacturing employment as a source of exogenous
-variation.
+turn towards Trump. To mitigate these risks, \cite{Baccini21} use a
+Bartik instrument, which we adapt (see \cite{Bartik91}). This instrument
+essentially uses the cross-county distribution of manufacturing
+employment as a source of exogenous variation.
 
@@
 
-Our second approach involves attempting to balance the covariates of the
-deindustrialization treatment. We use the same covariates as are used in
-controls above, as well as manufacturing as share of the population and
-total population. We apply the method of Covariate Balancing Propensity
-Scores, as developed by \cite{Imai14}; this method generates weights to
-reduce the correlation between covariates and treatment, while
-addressing several of the issues with propensity score weights. We find
-significant imbalance in the data - in other words, it is relatively
-easy to predict the `treatment' of job loss given the covariates (see
-Appendix for balance plots). Given covariate-balancing weights, we then
-conduct a single-stage weighted regression of change in Democratic vote
-share on manufacturing job loss, using the same controls as above.
+A potential weakness of our first approach is that manufacturing
+employment in a county may be correlated with swinging towards Trump for
+reasons other than manufacturing job losses. To account for this
+potential ommitted variable bias, we use a second approach that attempts
+to balance the covariates of the deindustrialization treatment. We use
+the same covariates as are used in controls above, as well as
+manufacturing as share of the population and total population. We apply
+the method of Covariate Balancing Propensity Scores, as developed by
+\cite{Imai14}; this method generates weights to reduce the correlation
+between covariates and treatment, while addressing several of the issues
+with propensity score weights. We find significant imbalance in the data
+- in other words, it is relatively easy to predict the `treatment' of
+job loss given the covariates (see Appendix for balance plots). Given
+covariate-balancing weights, we then conduct a single-stage weighted
+regression of change in Democratic vote share on manufacturing job loss,
+using the same controls as above. Essentially, this approach can be
+conceptualized as a form of matching that reduces the potential ommitted
+variable bias in our first approach, but may introduce selection bias
+(as some counties will be given low weights).
 

### 2021-12-13 Final Draft/Final Draft.Rmd
more tweaks

--- 2021-12-13 Final Draft/Final Draft.Rmd
@@
 Doing so, we find that regions experiencing more manufacturing job losses from 2004-2015 swung towards Donald Trump in 2016, and that this occurred more when those losing jobs were white.
-We get similar result using our covariate-matching approach.
+We get directionally similar results using our covariate-matching approach - differences in magnitude are an object of further investigation.
 Relative to \cite{Baccini21}, our results point to the substantive importance of the timing of manufacturing job losses on political outcomes.

### 2021-12-13 Final Draft/Final Draft.Rmd
dataverse and table row names

--- 2021-12-13 Final Draft/Final Draft.Rmd
@@
 acknowledgements: | 
-  Code available at https://github.com/zagrebmukerjee/ReplicationPaper
+  Code available at https://github.com/zagrebmukerjee/ReplicationPaper; https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/7U2UIQ
 abstract: |

### 2021-12-13 rCode/tablesAndFigures.R

@@ -17,9 +17,9 @@ tableOurs <- datasetList$datasetOurs %>%
     `Mfg Share of Emp` = mfgShare_total,
     `Mfg Share of Emp (White)` = mfgShare_white,
     `Mfg Share of Emp (Nonwhite)` = mfgShare_nonwhite,
-    `Change in Mfg Jobs/ Worker` = mfgNetChange_total,
-    `Change in Mfg Jobs/ Worker (W)` = mfgNetChange_white,
-    `Change in Mfg Jobs/ Worker (NW)` = mfgNetChange_nonwhite
+    `Mfg Job Loss/ Worker` = mfgNetChange_total,
+    `Mfg Job Loss/ Worker (W)` = mfgNetChange_white,
+    `Mfg Job Loss/ Worker (NW)` = mfgNetChange_nonwhite
   ) %>% 
   pivot_longer(cols = -c( "state_fips", "county_fips") ,names_to = "variable") %>%
   mutate(
@@ -28,9 +28,9 @@ tableOurs <- datasetList$datasetOurs %>%
       "Mfg Share of Emp",
       "Mfg Share of Emp (White)",
       "Mfg Share of Emp (Nonwhite)",
-      "Change in Mfg Jobs/ Worker",
-      "Change in Mfg Jobs/ Worker (W)",
-      "Change in Mfg Jobs/ Worker (NW)"
+      "Mfg Job Loss/ Worker",
+      "Mfg Job Loss/ Worker (W)",
+      "Mfg Job Loss/ Worker (NW)"
       ))) %>% 
   group_by(variable) %>% 
   summarize(
@@ -61,9 +61,9 @@ table04 <- datasetList$datasetOurs04 %>%
     `Mfg Share of Emp` = mfgShare_total,
     `Mfg Share of Emp (White)` = mfgShare_white,
     `Mfg Share of Emp (Nonwhite)` = mfgShare_nonwhite,
-    `Change in Mfg Jobs/ Worker` = mfgNetChange_total,
-    `Change in Mfg Jobs/ Worker (W)` = mfgNetChange_white,
-    `Change in Mfg Jobs/ Worker (NW)` = mfgNetChange_nonwhite
+    `Mfg Job Loss/ Worker` = mfgNetChange_total,
+    `Mfg Job Loss/ Worker (W)` = mfgNetChange_white,
+    `Mfg Job Loss/ Worker (NW)` = mfgNetChange_nonwhite
   ) %>% 
[…]

### 2021-12-13 Final Draft/Final Draft.Rmd
more language changes

@@
 We apply the method of Covariate Balancing Propensity Scores, as developed by \cite{Imai14}; this method generates weights to reduce the correlation between covariates and treatment, while addressing several of the issues with propensity score weights.
-We find significant imbalance in the data - in other words, it is relatively easy to predict the 'treatment' of job loss given the covariates (see Appendix for balance plots).
+We find significant imbalance in the data - in other words, it is relatively easy to predict the 'treatment' of job loss given the covariates (see Figures \ref{balPlot} and \ref{balPlotWhite} for balance plots).
 Given covariate-balancing weights, we then conduct a single-stage weighted regression of change in Democratic vote share on manufacturing job loss, using the same controls as above.
@@
 In other words, net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased Democratic vote share.
-We find the same effect when using covariate balancing, albeit of reduced size.
+We find the same effect when using covariate balancing, albeit of reduced size (we are investigating the difference in magnitude).
 

### 2021-12-13 Final Draft/Final-Draft.tex
wording

@@
   Zagreb Mukerjee\thanks{
-  Darin: Harvard University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
-  Mukerjee: Harvard University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
-  Code available at https://github.com/zagrebmukerjee/ReplicationPaper
+  Darin: Harvard
+University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
+  Mukerjee: Harvard
+University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
+  Code available at https://github.com/zagrebmukerjee/ReplicationPaper;
+  https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/7U2UIQ
 }
@@
 job losses from 2004-2015 swung towards Donald Trump in 2016, and that
-this occurred more when those losing jobs were white. We get similar
-result using our covariate-matching approach. Relative to
-\cite{Baccini21}, our results point to the substantive importance of the
-timing of manufacturing job losses on political outcomes.
+this occurred more when those losing jobs were white. We get
+directionally similar results using our covariate-matching approach -
+differences in magnitude are an object of further investigation.
+Relative to \cite{Baccini21}, our results point to the substantive
+importance of the timing of manufacturing job losses on political
+outcomes.
 
@@
 \midrule
-Mfg Share of Emp & 0.20 & 0.15 & 0.09 & 0.17 & 0.29\\
-Mfg Share of Emp (White) & 0.16 & 0.13 & 0.06 & 0.13 & 0.22\\
-Mfg Share of Emp (Nonwhite) & 0.05 & 0.07 & 0.01 & 0.02 & 0.06\\
-Change in Mfg Jobs/ Worker & 0.04 & 0.09 & -0.01 & 0.02 & 0.06\\
-Change in Mfg Jobs/ Worker (W) & 0.03 & 0.07 & 0.00 & 0.02 & 0.06\\
+Mfg Share of Emp & 0.13 & 0.10 & 0.05 & 0.11 & 0.19\\
+Mfg Share of Emp (White) & 0.10 & 0.08 & 0.04 & 0.08 & 0.15\\
+Mfg Share of Emp (Nonwhite) & 0.03 & 0.04 & 0.00 & 0.01 & 0.04\\
+Mfg Job Loss/ Worker & 0.02 & 0.06 & 0.00 & 0.01 & 0.04\\
+Mfg Job Loss/ Worker (W) & 0.02 & 0.04 & 0.00 & 0.01 & 0.04\\
 \addlinespace
-Change in Mfg Jobs/ Worker (NW) & 0.00 & 0.04 & -0.01 & 0.00 & 0.01\\
+Mfg Job Loss/ Worker (NW) & 0.00 & 0.03 & 0.00 & 0.00 & 0.00\\
 \bottomrule
@@
 A potential weakness of our first approach is that manufacturing
-employment in a county may be correlated with swinging towards Trump for
-reasons other than manufacturing job losses. To account for this
-potential ommitted variable bias, we use a second approach that attempts
-to balance the covariates of the deindustrialization treatment. We use
-the same covariates as are used in controls above, as well as
-manufacturing as share of the population and total population. We apply
-the method of Covariate Balancing Propensity Scores, as developed by
-\cite{Imai14}; this method generates weights to reduce the correlation
-between covariates and treatment, while addressing several of the issues
-with propensity score weights. We find significant imbalance in the data
-- in other words, it is relatively easy to predict the `treatment' of
-job loss given the covariates (see Appendix for balance plots). Given
-covariate-balancing weights, we then conduct a single-stage weighted
-regression of change in Democratic vote share on manufacturing job loss,
-using the same controls as above. Essentially, this approach can be
-conceptualized as a form of matching that reduces the potential ommitted
-variable bias in our first approach, but may introduce selection bias
-(as some counties will be given low weights).
+employment may be correlated with swinging towards Trump for reasons
+other than manufacturing job losses. To account for this potential
+ommitted variable bias, we use a second approach that attempts to
+balance the covariates of the deindustrialization treatment. We use the
+same covariates as are used in controls above, as well as manufacturing
+as share of the population and total population. We apply the method of
+Covariate Balancing Propensity Scores, as developed by \cite{Imai14};
+this method generates weights to reduce the correlation between
+covariates and treatment, while addressing several of the issues with
+propensity score weights. We find significant imbalance in the data - in
+other words, it is relatively easy to predict the `treatment' of job
+loss given the covariates (see Figures \ref{balPlot} and
+\ref{balPlotWhite} for balance plots). Given covariate-balancing
+weights, we then conduct a single-stage weighted regression of change in
+Democratic vote share on manufacturing job loss, using the same controls
+as above. Essentially, this approach can be conceptualized as a form of
+matching that reduces the potential ommitted variable bias in our first
+approach, but may introduce selection bias (as some counties will be
+given low weights).
 
@@
 find the same effect when using covariate balancing, albeit of reduced
-size.
+size (we are investigating the difference in magnitude).
 

### 2021-12-13 Final Draft/Final Draft.Rmd
wording
tiny typo fix

@@
 Counter-intuitively, we find that counties that gained manufacturing jobs from 2012-2015 are more likely to have swung towards Trump.
-We believe this is due to an omitted variable - the job loss experienced from 2004 to 2012.
+We show this is due to an omitted variable - the job loss experienced from 2004 to 2012.
 Counties that experienced prior deindustrialization were more likely to exhibit increased support for Trump, as well as a slight manufacturing rebound in 2012-2015.
+We find that job losses from 2004 to 2015 are related to loss in Democratic vote share.
 Dis-aggregating this result by race shows that the Democratic vote share fell where job losses affected white populations, and rose where job losses affected nonwhites.
@@
 A potential weakness of our first approach is that manufacturing employment may be correlated with swinging towards Trump for reasons other than manufacturing job losses.
-To account for this potential ommitted variable bias, we use a second approach that attempts to balance the covariates of the deindustrialization treatment.
+To account for this potential omitted variable bias, we use a second approach that attempts to balance the covariates of the deindustrialization treatment.
 We use the same covariates as are used in controls above, as well as manufacturing as share of the population and total population.
@@
 Given covariate-balancing weights, we then conduct a single-stage weighted regression of change in Democratic vote share on manufacturing job loss, using the same controls as above.
-Essentially, this approach can be conceptualized as a form of matching that reduces the potential ommitted variable bias in our first approach, but may introduce selection bias (as some counties will be given low weights).
+Essentially, this approach can be conceptualized as a form of matching that reduces the potential omitted variable bias in our first approach, but may introduce selection bias (as some counties will be given low weights).
 

### 2021-12-13 Final Draft/Final Draft.Rmd
table 3 change

@@
 
-rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelOurs_2$fitted.values"] <-  "Job Losses"
+rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelOurs_3$fitted.values"] <-  "Job Losses"
+rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelOurs_5$fitted.values"] <-  "White Job Losses"
+rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelOurs_6$fitted.values"] <-  "White Job Losses"
 
 rownames(regResultList$secondStageModelWNetCA$coefficients 
-)[rownames(regResultList$secondStageModelWNetCA$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+)[rownames(regResultList$secondStageModelWNetCA$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
 rownames(regResultList$secondStageModelWNetC$coefficients
-)[rownames(regResultList$secondStageModelWNetC$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+)[rownames(regResultList$secondStageModelWNetC$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
 
-rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"
+rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelOurs_2$fitted.values"] <-  "Job Losses"
+rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelOurs_3$fitted.values"] <-  "Job Losses"
+rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelOurs_5$fitted.values"] <-  "White Job Losses"
+rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelOurs_6$fitted.values"] <-  "White Job Losses"
 
-rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
-rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
+rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
+rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
 
-names(regResultList$rseNetCA_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseNetC_2)[1] <- "Manufacturing Layoffs"
-names(regResultList$rseWNetCA_2)[1] <- "White Manufacturing Layoffs"
-names(regResultList$rseWNetC_2)[1] <- "White Manufacturing Layoffs"
+names(regResultList$rseNetCA_2)[1] <- "Job Losses"
+names(regResultList$rseNetC_2)[1] <- "Job Losses"
+names(regResultList$rseWNetCA_2)[1] <- "White Job Losses"
+names(regResultList$rseWNetC_2)[1] <- "White Job Losses"
 
-names(regResultList$rseWNetCA_2)[names(regResultList$rseWNetCA_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
-names(regResultList$rseWNetC_2)[names(regResultList$rseWNetC_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
+names(regResultList$rseWNetCA_2)[names(regResultList$rseWNetCA_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Job Losses"
+names(regResultList$rseWNetC_2)[names(regResultList$rseWNetC_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Job Losses"
 
@@
           omit.stat = c("rsq","ser"),
-          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
+          keep = c("Job Losses", "White Job Losses", "Nonwhite Job Losses"),
           add.lines = list(

### 2021-12-13 Final Draft/Final Draft.Rmd
final changes

--- 2021-12-13 Final Draft/Final Draft.Rmd
@@
 Counter-intuitively, we find that counties that gained manufacturing jobs from 2012-2015 are more likely to have swung towards Trump.
-We believe this is due to an omitted variable - the job loss experienced from 2004 to 2012.
+We show this is due to an omitted variable - the job loss experienced from 2004 to 2012.
 Counties that experienced prior deindustrialization were more likely to exhibit increased support for Trump, as well as a slight manufacturing rebound in 2012-2015.
+We find that manufacturing job losses from 2004 to 2015 are related to loss in Democratic vote share.
 Dis-aggregating this result by race shows that the Democratic vote share fell where job losses affected white populations, and rose where job losses affected nonwhites.
@@
 However, our results differ from \cite{Baccini21} in regards to the *timing* of the impact of manufacturing job losses on employment.
-In fact, using our preferred measure of deindustrialization - *net* change in manufacturing employment - we find that counties with manufacturing job *gains* from 2012-2015 tended to swing towards Donald Trump in 2016.
+In fact, using our preferred measure of deindustrialization - *net* manufacturing job losses - we find that counties with manufacturing job *gains* from 2012-2015 tended to swing towards Donald Trump in 2016.
 Given this counter-intuitive result, we extend the analysis to the 2004-2015 period in order to capture the long-term effects of deindustrialization on a region.
@@
 Electoral College votes are allocated.
-As an alternative perspective, we examined a range of counterfactual scenarios, in which counties manufacturing experienced job losses between the 1st and 99th percentiles across all counties.
+As an alternative perspective, we examined a range of counterfactual scenarios, in which we estimate counties' counterfactual voting outcomes assuming they had experienced manufacturing job losses between the 1st and 99th percentiles across all counties.
 
@@
 It is important to note that, in the counterfactual and simulation exercises shown in Figures \ref{counterfactual1}, \ref{counterfactual2}, and \ref{counterfactual3}, we estimate the change in Democratic vote share assuming various levels of white manufacturing job losses *holding all else equal, including non-white manufacturing job losses.* Given that white and non-white manufacturing job losses are weakly-to-moderately correlated across counties (r = .33), this is likely a poor assumption, because, in reality, a decline in white manufacturing job losses would likely correspond to a decline in non-white manufacturing job losses.
-Given that non-white manufacturing job losses were expected to *increase* Democratic vote share in 2016, this means that our simulation results may be overestimating effect sizes because it does not take into account this second-order impact.
+Given that non-white manufacturing job losses were expected to *increase* Democratic vote share in 2016, this means that our simulation results may be overestimating effect sizes because they do not take into account this second-order impact.
 
@@
 As discussed above, the 2012-2015 period can be broadly characterized as a slight rebound from the manufacturing job losses in the 2008 financial crisis.
-The counties that experience job losses from 2004-2012 are more likely to have job gains in 2012-2015 (see \ref{fig:vShapePlot1}).
-An apparent relationship between 2012-2015 job gains and loss of Democratic vote share in fact represents 2004-2012 job losses that may lead to both the later job gains and the loss of vote share.
+The counties that experience job losses from 2004-2012 are more likely to have job gains in 2012-2015 (see \ref{fig:vShapePlot1} and \ref{vShapePlot2}).
+An apparent relationship between 2012-2015 job gains and loss of Democratic vote share in fact represents 2004-2012 job losses that may lead to both the later job gains *and* the loss of vote share.
 These results can be seen in Table \ref{regResult12}.

### 2021-12-13 Final Draft/Final-Draft.tex
updates
final changes

@@
   Zagreb Mukerjee\thanks{
-  Darin: Harvard
-University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
-  Mukerjee: Harvard
-University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
+  Darin: Harvard University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
+  Mukerjee: Harvard University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
   Code available at https://github.com/zagrebmukerjee/ReplicationPaper;
@@
 that gained manufacturing jobs from 2012-2015 are more likely to have
-swung towards Trump. We believe this is due to an omitted variable - the
+swung towards Trump. We show this is due to an omitted variable - the
 job loss experienced from 2004 to 2012. Counties that experienced prior
 deindustrialization were more likely to exhibit increased support for
-Trump, as well as a slight manufacturing rebound in 2012-2015.
-Dis-aggregating this result by race shows that the Democratic vote share
-fell where job losses affected white populations, and rose where job
-losses affected nonwhites. This suggests a racial component to how
-voters process economic hardship.
+Trump, as well as a slight manufacturing rebound in 2012-2015. We find
+that manufacturing job losses from 2004 to 2015 are related to loss in
+Democratic vote share. Dis-aggregating this result by race shows that
+the Democratic vote share fell where job losses affected white
+populations, and rose where job losses affected nonwhites. This suggests
+a racial component to how voters process economic hardship.
 \end{abstract}
@@
 manufacturing job losses on employment. In fact, using our preferred
-measure of deindustrialization - \emph{net} change in manufacturing
-employment - we find that counties with manufacturing job \emph{gains}
-from 2012-2015 tended to swing towards Donald Trump in 2016. Given this
+measure of deindustrialization - \emph{net} manufacturing job losses -
+we find that counties with manufacturing job \emph{gains} from 2012-2015
+tended to swing towards Donald Trump in 2016. Given this
 counter-intuitive result, we extend the analysis to the 2004-2015 period
@@
 College votes are allocated. As an alternative perspective, we examined
-a range of counterfactual scenarios, in which counties manufacturing
-experienced job losses between the 1st and 99th percentiles across all
+a range of counterfactual scenarios, in which we estimate counties'
+counterfactual voting outcomes assuming they had experienced
+manufacturing job losses between the 1st and 99th percentiles across all
 counties.
@@
 2016, this means that our simulation results may be overestimating
-effect sizes because it does not take into account this second-order
+effect sizes because they do not take into account this second-order
 impact.
@@
 2004-2012 are more likely to have job gains in 2012-2015 (see
-\ref{fig:vShapePlot1}). An apparent relationship between 2012-2015 job
-gains and loss of Democratic vote share in fact represents 2004-2012 job
-losses that may lead to both the later job gains and the loss of vote
-share. These results can be seen in Table \ref{regResult12}.
-\FloatBarrier
+\ref{fig:vShapePlot1} and \ref{vShapePlot2}). An apparent relationship
+between 2012-2015 job gains and loss of Democratic vote share in fact
+represents 2004-2012 job losses that may lead to both the later job
+gains and the loss of vote share. These results can be seen in Table
+\ref{regResult12}. \FloatBarrier
 

### 2021-12-13 Final Draft/Final Draft.Rmd

--- 2021-12-13 Final Draft/Final Draft.Rmd
@@
 Counties that experienced prior deindustrialization were more likely to exhibit increased support for Trump, as well as a slight manufacturing rebound in 2012-2015.
-We find that job losses from 2004 to 2015 are related to loss in Democratic vote share.
+We find that manufacturing job losses from 2004 to 2015 are related to loss in Democratic vote share.
 Dis-aggregating this result by race shows that the Democratic vote share fell where job losses affected white populations, and rose where job losses affected nonwhites.
